---
--
title: "Toolik_gth89_Sila Flux Cleaning"
output:
html_document: default
df_print: paged
pdf_document: default
date: "2025-07-16"
---


```{r, warning=FALSE}
rm(list = ls())
Sys.setenv(TZ = "UTC")
knitr::opts_chunk$set(error = TRUE)
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = 'C:/Users/klynoe/Documents/toolik/raw_data') #use this to set your directory

library(data.table)
library(ggplot2)
library(cowplot)
library(openair)
library(plotrix)
library(signal)
library(svMisc)
library(zoo)
library(stringr)
library(plyr)
library(dplyr)



```

```{r, warning=FALSE}


#df = fread(input = "C:/Users/klynoe/Documents/toolik/raw_data/met/toolik-gth89-AllLogger.dat",skip=4, header = F , na.strings = c('-9999','NA','NaN','NAN','-7999'))

#h = fread("C:/Users/klynoe/Documents/toolik/raw_data/met/toolik-gth89-AllLogger.dat",skip=1, nrows = 0 , na.strings = c('-9999','NA','NaN','NAN','-7999'))

#df = fread(input = "C:/Users/klynoe/Documents/toolik/raw_data/met/toolik-gth89-AllBiomet.dat",skip=4, header = F , na.strings = c('-9999','NA','NaN','NAN','-7999'))

#h = fread("C:/Users/klynoe/Documents/toolik/raw_data/met/toolik-gth89-AllBiomet.dat",skip=1, nrows = 0 , na.strings = c('-9999','NA','NaN','NAN','-7999'))


#names(df) = names(h)

#df = rbind.fill(df,met)
#df = df[!duplicated(df$TIMESTAMP),]

df = read.csv('C:/Users/klynoe/Documents/toolik/R_outputs/gth89_biomet_1b.csv')


df$TIMESTAMP <- as.POSIXct(df$TIMESTAMP, format = "%Y-%m-%d %H:%M", tz = "UTC")

# Replace specific missing value indicators with NA
df[df == -9999] <- NA
df[df == -7999] <- NA


timestamp_cutoff <- as.POSIXct("2025-05-01 14:00", format = "%Y-%m-%d %H:%M", tz = "UTC")
df <- df %>%
  dplyr::filter(TIMESTAMP >= timestamp_cutoff)


# Create a complete sequence of timestamps at 30-minute intervals
tsdf <- data.frame(TIMESTAMP = seq(
  from = min(df$TIMESTAMP),
  to = max(df$TIMESTAMP),
  by = 60*30
))



df = merge(tsdf,df,by = 'TIMESTAMP',all.x = T)


names(df) <- gsub("^([A-Za-z]+)_(?:[0-9_]+_)?([0-9]+_[0-9]+_[0-9]+)$", "\\1_\\2", names(df))



```

```{r, warning=FALSE}
biomet_dates <- c('2025-05-01', '2025-10-01')
#biomet_dates <- c('2024-10-30', '2024-12-01')
```

# Air T 
```{r, warning=FALSE}
#First we need to just convert from Kelvin to degrees C
df$TA_1_1_1 = ifelse(df$TA_1_1_1 > 200,df$TA_1_1_1 - 273.15,df$TA_1_1_1)

ggplot(data = df)+
  geom_point(aes(TIMESTAMP, TA_1_1_1),col='black')+
  scale_y_continuous(limits = c(-40,40),
                     expression('Air Temperature ('*Celsius*')'))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates))



ggplot(data = df)+
  geom_point(aes(TIMESTAMP,TA_1_1_1),col='black')+
  scale_y_continuous(limits = c(-40,40),
                      expression('Air Temperature ('*Celsius*')'))+
   scale_x_datetime(limits = as.POSIXct(biomet_dates))
```


## Limits
```{r, warning=FALSE}
hist(df$TA_1_1_1,breaks=100)
plot(df$TIMESTAMP,df$TA_1_1_1,ylim = c(-50,50));abline(h=-50, col= 'red');abline(h=50, col='red')
TA_1_1_1.limits = replace(df$TA_1_1_1, df$TA_1_1_1 < -50 | df$TA_1_1_1 > 50,NA)
hist(TA_1_1_1.limits,breaks=100)
plot(TA_1_1_1.limits)

df$TA_1_1_1.c = TA_1_1_1.limits
```


#Relative Humidity

```{r,warning=FALSE}
ggplot(data = df)+
  geom_point(aes(TIMESTAMP,RH_1_1_1),col='black')+
  scale_y_continuous(#limits = c(20,100),
                     expression('Relative Humidity ('*percent*')'))+
 scale_x_datetime(limits = as.POSIXct(biomet_dates))
```


## Limits
```{r,warning=FALSE}
RH.limits = df$RH_1_1_1

#RH_1_1_1.limits = ifelse(df$RH_1_1_1 > 0 & df$TIMESTAMP <= '2022-9-23',NA, RH_1_1_1.limits)

df$RH.c = RH.limits

ggplot(data = df)+
  geom_point(aes(TIMESTAMP,RH.c),col='black')+
  scale_y_continuous(limits = c(5,105),
                     expression('Relative Humidity ('*percent*')'))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates))
```

# Barometric Pressure 

```{r,warning=FALSE}
ggplot(data = df)+
  geom_point(aes(TIMESTAMP,air_pressure),col='black')+
  scale_y_continuous(#limits = c(90000,110000),
                     expression ('Barometric Pressure ('*kPa*')'))
#  scale_x_datetime(limits = as.POSIXct(biomet_dates))

#df$air_pressure = ifelse(df$air_pressure > 97000,df$air_pressure/1000,df$air_pressure)
df$air_pressure = ifelse(df$air_pressure > 87000, df$air_pressure / 1000, df$air_pressure)

ggplot(data = df)+
  geom_point(aes(TIMESTAMP,air_pressure),col='black')+
  scale_y_continuous(limits = c(0,200),
                     expression ('Barometric Pressure ('*kPa*')'))


df$air_pressure = ifelse(df$air_pressure > 150,df$air_pressure/10,df$air_pressure)

ggplot(data = df)+
  geom_point(aes(TIMESTAMP,air_pressure),col='black')+
  scale_y_continuous(limits = c(80,110),
                     expression ('Barometric Pressure ('*kPa*')'))
```


```{r, warning=FALSE}
hist(df$air_pressure,breaks=100)

ggplot(data = df)+
  geom_point(aes(TIMESTAMP,air_pressure),col='black')+
  scale_y_continuous(limits = c(90,110),
                     expression ('Barometric Pressure ('*kPa*')'))

air_pressure.limits = ifelse(df$air_pressure > 110 | df$air_pressure < 97,NA, df$air_pressure)

ggplot(data = df)+
  geom_point(aes(TIMESTAMP,air_pressure.limits),col='black')+
  geom_hline(yintercept = 106,col = 'red')+
  geom_hline(yintercept = 97,col = 'red')+
  scale_y_continuous(limits = c(90,110),
                     expression ('Barometric Pressure ('*kPa*')'))
```
## Rolling MAD
```{r, warning=FALSE}
f = air_pressure.limits # first make a new flux vector to apply the above filters
# prepare the inputs for a zero-phase (forward and reverse) filter  
ind       = which(complete.cases(f))   # first save the index of all the NAs
b         = rep(1,8)/8                 # moving average coefficient
a         = 1                          # coefficient of the ARMA filter
mad_i    = filtfilt(b, a, na.omit(f)) #create a forward and reverse ARMA filter
mad_filt = f                          # make a copy of the full fluxes again
mad_filt[ind] = mad_i                # apply the filter where the real data exist

n = 7*48 # set the length of the rolling filter, 48 half hours in day * x days
roll.mad = rollapply(data = mad_filt,
                     width = n,
                     FUN = mad,
                     partial = TRUE,
                     na.rm = T,
                     fill = NA)  #create a rolling MAD or sd or other
roll.mad[is.na(mad_filt)] = NA  #make NA values where NAs exist in the real data


ggplot(df)+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,air_pressure.limits,col='Pressure'))+
  geom_line(aes(TIMESTAMP,mad_filt,col='Filter'))+
  geom_line(aes(TIMESTAMP,roll.mad,col='MAD'))+
  scale_y_continuous(limits = c(0,110))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))+
  scale_color_manual(values=c('yellow','red','black'))
```

```{r, warning=FALSE}
#adjust this value (N) to tweak how many MADs to be away from the norm
N = 4

#Add clean value to dataframe (_.c)

df$air_pressure.c = ifelse(abs(air_pressure.limits - mad_filt) > (N * roll.mad),NA,air_pressure.limits)

#Compare cleaned vs. uncleaned

ggplot(df)+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,air_pressure,col='Uncleaned'))+
  geom_point(aes(TIMESTAMP,air_pressure.c,col='Cleaned'))+
  scale_y_continuous(limits = c(90,110))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))+
  scale_color_manual(values=c('black','red'))
```

```{r, warning=FALSE}
ggplot(data = df)+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*6,ymin = mad_filt-roll.mad*6,fill='6'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*3,ymin = mad_filt-roll.mad*3,fill='3'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*2,ymin = mad_filt-roll.mad*2,fill='2'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*1,ymin = mad_filt-roll.mad*1,fill='1'))+
  geom_point(aes(TIMESTAMP,air_pressure.limits),col='red')+
  geom_point(aes(TIMESTAMP,air_pressure.c),col='black')+
  scale_y_continuous(limits = c(80,115))+
scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))
```


#Soil Heat Flux
```{r, warning=FALSE}
ggplot(data = df)+
  geom_point(aes(TIMESTAMP,SHF_1_1_1,col='SHF 1'))+
  geom_point(aes(TIMESTAMP,SHF_2_1_1,col='SHF 2'))+
 
  scale_y_continuous(limits = c(-80,190),
                     expression ('Soil Heat Flux ('*W/m^2*')'))+
  scale_color_manual(values = c('red','black','brown'))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates))
```

## SHF1
```{r, warning=FALSE}
hist(df$SHF_1_1_1,breaks=100)
plot(df$TIMESTAMP,df$SHF_1_1_1,ylim = c(-50,200));abline(h=-55, col= 'red');abline(h=190, col='red')
SHF_1_1_1.limits = replace(df$SHF_1_1_1, df$SHF_1_1_1 < -55 | df$SHF_1_1_1 > 190,NA)
hist(SHF_1_1_1.limits,breaks=100)
plot(SHF_1_1_1.limits)
df$SHF_1_1_1.c = SHF_1_1_1.limits
```

## SHF2
```{r, warning=FALSE}
hist(df$SHF_2_1_1,breaks=100)
plot(df$TIMESTAMP,df$SHF_2_1_1,ylim = c(-80,165));abline(h=-75, col= 'red');abline(h=150, col='red')
SHF_2_1_1.limits = replace(df$SHF_2_1_1, df$SHF_2_1_1 < -75 | df$SHF_2_1_1 > 150,NA)
hist(SHF_2_1_1.limits,breaks=100)
plot(SHF_2_1_1.limits)
df$SHF_2_1_1.c = SHF_2_1_1.limits
```




# PAR
```{r, warning=FALSE}
ggplot(data = df)+
  geom_point(aes(TIMESTAMP,PPFD_1_1_1),col='black')+
  scale_y_continuous(limits = c(-25,2000),
                     expression('PAR ('*mu*mol/m^2/s*')'))

ggplot(data = df)+
  geom_point(aes(TIMESTAMP,PPFD_1_1_1),col='black')+
  scale_y_continuous(limits = c(-25,2000),
                     expression('PAR ('*mu*mol/m^2/s*')'))+
  scale_x_datetime(limits =as.POSIXct(c( '2025-05-01', '2025-08-25'),format="%F"))
```

```{r, warning=FALSE}
summary(df$PPFD_1_1_1)
hist(df$PPFD_1_1_1,breaks=100)
plot(df$TIMESTAMP,df$PPFD_1_1_1,ylim = c(0,1850));abline(h=1750, col= 'red');abline(h=0, col='red')
PPFD_1_1_1.limits = replace(df$PPFD_1_1_1, df$PPFD_1_1_1 < 0 | df$PPFD_1_1_1 > 1750,NA)
hist(PPFD_1_1_1.limits,breaks=100)
plot(PPFD_1_1_1.limits)
```


### Rolling SD 
(Changed to SD because MAD was cutting good data)
```{r, warning=FALSE}
f = PPFD_1_1_1.limits # first make a new flux vector to apply the above filters
# prepare the inputs for a zero-phase (forward and reverse) filter  
ind       = which(complete.cases(f))   # first save the index of all the NAs
b         = rep(1,8)/8                 # moving average coefficient
a         = 1                          # coefficient of the ARMA filter
mad_i    = filtfilt(b, a, na.omit(f)) #create a forward and reverse ARMA filter
mad_filt = f                          # make a copy of the full fluxes again
mad_filt[ind] = mad_i                # apply the filter where the real data exist

n = 14*48 # set the length of the rolling filter, 48 half hours in day * x days
roll.mad = rollapply(data = mad_filt,
                     width = n,
                     FUN = sd,
                     partial = TRUE,
                     na.rm = T,
                     fill = NA)  #create a rolling MAD or sd or other
roll.mad[is.na(mad_filt)] = NA  #make NA values where NAs exist in the real data

ggplot(df)+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,PPFD_1_1_1.limits,col='PAR in'))+
  geom_line(aes(TIMESTAMP,mad_filt,col='Filter'))+
  geom_line(aes(TIMESTAMP,roll.mad,col='MAD'))+
  scale_y_continuous(limits = c(-15,1800))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))+
  scale_color_manual(values=c('yellow','red','black'))

```

```{r, warning=FALSE}
#adjust this value (N) to tweak how many MADs to be away from the norm
N = 3

#Add clean value to dataframe (_.c)

df$PPFD_1_1_1.c = ifelse(abs(PPFD_1_1_1.limits - mad_filt) > (N * roll.mad),NA,PPFD_1_1_1.limits)

#Compare cleaned vs. uncleaned

ggplot(df)+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,PPFD_1_1_1.limits,col='Uncleaned'))+
  geom_point(aes(TIMESTAMP,PPFD_1_1_1.c,col='Cleaned'))+
  scale_y_continuous(limits = c(0,2000))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))+
  scale_color_manual(values=c('black','red'))
```

```{r, warning=FALSE}
ggplot(data = df)+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*6,ymin = mad_filt-roll.mad*6,fill='6'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*3,ymin = mad_filt-roll.mad*3,fill='3'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*2,ymin = mad_filt-roll.mad*2,fill='2'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*1,ymin = mad_filt-roll.mad*1,fill='1'))+
  geom_point(aes(TIMESTAMP,PPFD_1_1_1.limits),col='red')+
  geom_point(aes(TIMESTAMP,PPFD_1_1_1.c),col='black')+
  scale_y_continuous(limits = c(-500,1300))
```



# Net Radiation 
```{r, warning=FALSE}
ggplot(data = df)+
  geom_point(aes(TIMESTAMP, RN_1_1_1),col='black')+
  scale_y_continuous(limits = c(-125,550),
                     expression('Net Radiation ('*W/m^2*')'))
```

```{r, warning=FALSE}
hist(df$RN_1_1_1,breaks=100)
plot(df$TIMESTAMP,df$RN_1_1_1,ylim = c(-400,850));abline(h=835,col= 'red');abline(h=-300, col='red')
RN_1_1_1.limits = replace(df$RN_1_1_1, df$RN_1_1_1 < -300 | df$RN_1_1_1 > 835,NA)
hist(RN_1_1_1.limits,breaks=100)
plot(df$TIMESTAMP,RN_1_1_1.limits)
```
## Rolling SD
```{r, warning=FALSE}
f = RN_1_1_1.limits # first make a new flux vector to apply the above filters
# prepare the inputs for a zero-phase (forward and reverse) filter  
ind       = which(complete.cases(f))   # first save the index of all the NAs
b         = rep(1,8)/8                 # moving average coefficient
a         = 1                          # coefficient of the ARMA filter
mad_i    = filtfilt(b, a, na.omit(f)) #create a forward and reverse ARMA filter
mad_filt = f                          # make a copy of the full fluxes again
mad_filt[ind] = mad_i                # apply the filter where the real data exist

n = 7*48 # set the length of the rolling filter, 48 half hours in day * x days
roll.mad = rollapply(data = mad_filt,
                     width = n,
                     FUN = sd,
                     partial = TRUE,
                     na.rm = T,
                     fill = NA)  #create a rolling MAD or sd or other
roll.mad[is.na(mad_filt)] = NA  #make NA values where NAs exist in the real data

ggplot(df)+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,RN_1_1_1.limits,col='Net Rad'))+
  geom_line(aes(TIMESTAMP,mad_filt,col='Filter'))+
  geom_line(aes(TIMESTAMP,roll.mad,col='MAD'))+
  scale_y_continuous(limits = c(-5,150))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))+
  scale_color_manual(values=c('yellow','red','black'))


```


```{r, warning=FALSE}

#adjust this value (N) to tweak how many MADs to be away from the norm
N = 3

#Add clean value to dataframe (_.c)

df$RN_1_1_1.c = ifelse(abs(RN_1_1_1.limits - mad_filt) > (N * roll.mad),NA,RN_1_1_1.limits)

#Compare cleaned vs. uncleaned

ggplot(df)+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,RN_1_1_1.limits,col='Uncleaned'))+
  geom_point(aes(TIMESTAMP,RN_1_1_1.c,col='Cleaned'))+
  scale_y_continuous(limits = c(-250,600))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))+
  scale_color_manual(values=c('black','red'))
```

```{r, warning=FALSE}
ggplot(data = df)+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*6,ymin = mad_filt-roll.mad*6,fill='6'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*3,ymin = mad_filt-roll.mad*3,fill='3'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*2,ymin = mad_filt-roll.mad*2,fill='2'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*1,ymin = mad_filt-roll.mad*1,fill='1'))+
  geom_point(aes(TIMESTAMP,RN_1_1_1.limits),col='red')+
  geom_point(aes(TIMESTAMP,RN_1_1_1.c),col='black')+
  scale_y_continuous(limits = c(-500,600))

```

# Shortwave in 
```{r, warning=FALSE}
ggplot(data = df)+
  geom_point(aes(TIMESTAMP,SWIN_1_1_1))+
  scale_y_continuous(#limits = c(-10,1000),
                     expression('Shortwave In ('*W/m^2*')'))
```

```{r, warning=FALSE}
hist(df$SWIN_1_1_1,breaks=100)
plot(df$TIMESTAMP,df$SWIN_1_1_1,ylim = c(0,1000));abline(h=900,col= 'red');abline(h=-1, col='red')
SWIN_1_1_1.limits <- df$SWIN_1_1_1
SWIN_1_1_1.limits[df$SWIN_1_1_1 < 0] <- 0
hist(SWIN_1_1_1.limits,breaks=100)
plot(df$TIMESTAMP,SWIN_1_1_1.limits)
```

## Rolling SD 
```{r, warning=FALSE}
f = SWIN_1_1_1.limits # first make a new flux vector to apply the above filters
# prepare the inputs for a zero-phase (forward and reverse) filter  
ind       = which(complete.cases(f))   # first save the index of all the NAs
b         = rep(1,8)/8                 # moving average coefficient
a         = 1                          # coefficient of the ARMA filter
mad_i    = filtfilt(b, a, na.omit(f)) #create a forward and reverse ARMA filter
mad_filt = f                          # make a copy of the full fluxes again
mad_filt[ind] = mad_i                # apply the filter where the real data exist

n = 7*48 # set the length of the rolling filter, 48 half hours in day * x days
roll.mad = rollapply(data = mad_filt,
                     width = n,
                     FUN = sd,
                     partial = TRUE,
                     na.rm = T,
                     fill = NA)  #create a rolling MAD or sd or other
roll.mad[is.na(mad_filt)] = NA  #make NA values where NAs exist in the real data


ggplot(df)+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,SWIN_1_1_1.limits,col='Shortwave in'))+
  geom_line(aes(TIMESTAMP,mad_filt,col='Filter'))+
  geom_line(aes(TIMESTAMP,roll.mad,col='MAD'))+
  scale_y_continuous(limits = c(-5,800))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))+
  scale_color_manual(values=c('yellow','red','black'))

```

```{r, warning=FALSE}
#adjust this value (N) to tweak how many MADs to be away from the norm
N = 4

#Add clean value to dataframe (_.c)

df$SWIN_1_1_1.c = ifelse(abs(SWIN_1_1_1.limits - mad_filt) > (N * roll.mad),NA,SWIN_1_1_1.limits)

#Compare cleaned vs. uncleaned

plot(df$TIMESTAMP,df$SWIN_1_1_1,col='red',ylim = c(-1,925));points(df$TIMESTAMP,df$SWIN_1_1_1.c)
```

```{r, warning=FALSE} 
ggplot(data = df)+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*6,ymin = mad_filt-roll.mad*6,fill='6'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*3,ymin = mad_filt-roll.mad*3,fill='3'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*2,ymin = mad_filt-roll.mad*2,fill='2'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*1,ymin = mad_filt-roll.mad*1,fill='1'))+
  geom_point(aes(TIMESTAMP,SWIN_1_1_1.limits),col='red')+
  geom_point(aes(TIMESTAMP,SWIN_1_1_1.c),col='black')+
  scale_y_continuous(limits = c(-300,700))
```


# Shortwave out 
```{r, warning=FALSE}
ggplot(data = df)+
  geom_point(aes(TIMESTAMP,SWOUT_1_1_1))+
  scale_y_continuous(limits = c(-10,150),
                     expression('Shortwave Out ('*W/m^2*')'))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates))
```

```{r, warning=FALSE}
hist(df$SWOUT_1_1_1,breaks=100)
plot(df$TIMESTAMP,df$SWOUT_1_1_1,ylim = c(0,800));abline(h=700,col= 'red');abline(h=-1, col='red')
SWOUT_1_1_1.limits <- df$SWOUT_1_1_1
SWOUT_1_1_1.limits[df$SWOUT_1_1_1 < 0] <- 0
hist(SWOUT_1_1_1.limits,breaks=100)
plot(df$TIMESTAMP,SWOUT_1_1_1.limits)
```


### Rolling MAD

```{r, warning=FALSE}
f = SWOUT_1_1_1.limits # first make a new flux vector to apply the above filters
# prepare the inputs for a zero-phase (forward and reverse) filter  
ind       = which(complete.cases(f))   # first save the index of all the NAs
b         = rep(1,8)/8                 # moving average coefficient
a         = 1                          # coefficient of the ARMA filter
mad_i    = filtfilt(b, a, na.omit(f)) #create a forward and reverse ARMA filter
mad_filt = f                          # make a copy of the full fluxes again
mad_filt[ind] = mad_i                # apply the filter where the real data exist

n = 7*48 # set the length of the rolling filter, 48 half hours in day * x days
roll.mad = rollapply(data = mad_filt,
                     width = n,
                     FUN = sd,
                     partial = TRUE,
                     na.rm = T,
                     fill = NA)  #create a rolling MAD or sd or other
roll.mad[is.na(mad_filt)] = NA  #make NA values where NAs exist in the real data

ggplot(df)+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,SWOUT_1_1_1.limits,col='Shortwave out'))+
  geom_line(aes(TIMESTAMP,mad_filt,col='Filter'))+
  geom_line(aes(TIMESTAMP,roll.mad,col='MAD'))+
  scale_y_continuous(limits = c(-5,100))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))+
  scale_color_manual(values=c('yellow','red','black'))


```

```{r, warning=FALSE}
#adjust this value (N) to tweak how many MADs to be away from the norm
N = 5

#Add clean value to dataframe (_.c)

df$SWOUT_1_1_1.c = ifelse(abs(SWOUT_1_1_1.limits - mad_filt) > (N * roll.mad),NA,SWOUT_1_1_1.limits)

#Compare cleaned vs. uncleaned

plot(df$TIMESTAMP,df$SWOUT_1_1_1,col='red',ylim = c(0,110));points(df$TIMESTAMP,df$SWOUT_1_1_1.c)
```

```{r, warning=FALSE}
ggplot(data = df)+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*6,ymin = mad_filt-roll.mad*6,fill='6'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*4,ymin = mad_filt-roll.mad*4,fill='4'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*3,ymin = mad_filt-roll.mad*3,fill='3'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*1,ymin = mad_filt-roll.mad*1,fill='1'))+
  geom_point(aes(TIMESTAMP,SWOUT_1_1_1.limits),col='red')+
  geom_point(aes(TIMESTAMP,SWOUT_1_1_1.c),col='black')+
  scale_y_continuous(limits = c(-200,300))
```


# Albedo 
```{r, warning=FALSE}
albedo = df$SWOUT_1_1_1.c / df$SWIN_1_1_1.c

ggplot(data = df)+
  geom_point(aes(TIMESTAMP,albedo))+
  scale_y_continuous(limits = c(-1,2),
                     expression('Albedo'))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates))

albedo.limits = replace(albedo, albedo < .05 | albedo > 1,NA)


ggplot(data = df)+
  geom_point(aes(TIMESTAMP,albedo.limits))+
  scale_y_continuous(limits = c(-.5,1.5),
                     expression('Albedo'))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates))


```

```{r, warning=FALSE}
f = albedo.limits # first make a new flux vector to apply the above filters
# prepare the inputs for a zero-phase (forward and reverse) filter  
ind       = which(complete.cases(f))   # first save the index of all the NAs
b         = rep(1,8)/8                 # moving average coefficient
a         = 1                          # coefficient of the ARMA filter
mad_i    = filtfilt(b, a, na.omit(f)) #create a forward and reverse ARMA filter
mad_filt = f                          # make a copy of the full fluxes again
mad_filt[ind] = mad_i                # apply the filter where the real data exist

n = 7*48 # set the length of the rolling filter, 48 half hours in day * x days
roll.mad = rollapply(data = mad_filt,
                     width = n,
                     FUN = mad,
                     partial = TRUE,
                     na.rm = T,
                     fill = NA)  #create a rolling MAD or sd or other
roll.mad[is.na(mad_filt)] = NA  #make NA values where NAs exist in the real data

ggplot(df)+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,albedo.limits,col='Albedo'))+
  geom_line(aes(TIMESTAMP,mad_filt,col='Filter'))+
  geom_line(aes(TIMESTAMP,roll.mad,col='MAD'))+
  scale_y_continuous(limits = c(0,1))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))+
  scale_color_manual(values=c('black','yellow','red'))
```


```{r, warning=FALSE}
#adjust this value (N) to tweak how many MADs to be away from the norm
N = 5

#Add clean value to dataframe (_.c)

df$ALB_1_1_1.c = ifelse(abs(albedo.limits - mad_filt) > (N * roll.mad),NA,albedo.limits)

#Compare cleaned vs. uncleaned


ggplot(df)+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,albedo.limits,col='Uncleaned'))+
  geom_point(aes(TIMESTAMP,df$ALB_1_1_1.c,col='Cleaned'))+
  scale_y_continuous(limits = c(0,1))+
  scale_color_manual(values=c('black','red'))   #scale_x_datetime(limits=as.POSIXct(c('2024-07-25','2024-12-01'),format="%F"))+
 


```

# Longwave In 
```{r, warning=FALSE}
ggplot(data = df)+
  geom_point(aes(TIMESTAMP,LWIN_1_1_1))+
  scale_y_continuous(limits = c(-250,550),
                     expression('Longwave In ('*W/m^2*')'))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates))

```

```{r, warning=FALSE}
hist(df$LWIN_1_1_1,breaks=100)
plot(df$TIMESTAMP,df$LWIN_1_1_1,ylim = c(80,750));abline(h=450, col= 'red');abline(h=90, col='red')
LWIN_1_1_1.limits = replace(df$LWIN_1_1_1, df$LWIN_1_1_1 < 80 | df$LWIN_1_1_1 > 450,NA)
hist(LWIN_1_1_1.limits,breaks=100)

ggplot(data = df)+
  geom_point(aes(TIMESTAMP,LWIN_1_1_1.limits))+
  scale_y_continuous(limits = c(-250,550),
                     expression('Longwave In ('*W/m^2*')'))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates))

df$LWIN_1_1_1.c = LWIN_1_1_1.limits
```


# Longwave out 
```{r, warning=FALSE}
ggplot(data = df)+
  geom_point(aes(TIMESTAMP,LWOUT_1_1_1))+
  scale_y_continuous(limits = c(-100,500),
                     expression('Longwave Out ('*W/m^2*')'))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates))
```

```{r, warning=FALSE}
hist(df$LWOUT_1_1_1,breaks=100)
plot(df$TIMESTAMP,df$LWOUT_1_1_1,ylim = c(80,750));abline(h=550, col= 'red');abline(h=85, col='red')
LWOUT_1_1_1.limits = replace(df$LWOUT_1_1_1, df$LWOUT_1_1_1 < 85 | df$LWOUT_1_1_1 > 550,NA)
hist(LWOUT_1_1_1.limits,breaks=100)
plot(LWOUT_1_1_1.limits)
df$LWOUT_1_1_1.c = LWOUT_1_1_1.limits
```


# Convert Soil Temps in Kelvin to Celcius
```{r, warning=FALSE}

ts_columns <- names(df)[grepl("TS", names(df))]

for (col in ts_columns) {
  df[[col]] <- ifelse(df[[col]] > 150, df[[col]] - 273.15, df[[col]])
}

```



# HERE ALL SOILTHERMS ARE AT 15 CM
# 15 cm
```{r, warning=FALSE}
ggplot(data = df)+ theme_bw()+ geom_hline(yintercept = 0)+
  geom_line(aes(TIMESTAMP, TS_1_1_1, col = '15 cm'))+
  geom_hline(yintercept = 0)+
  scale_y_continuous(limits = c(-8,15),
                     expression('Soil T ('*degree*C*')'))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates))
  #scale_x_datetime(limits = as.POSIXct(c('2024-09-01','2024-09-30'),format="%F"))
```



```{r, warning=FALSE}
ggplot(data = df)+ theme_bw()+ geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP, TS_1_1_1, col = '15 cm'))+
  scale_y_continuous(limits = c(-8,15),
                     expression('Therms Soil T ('*C*')'))
  
TS_1_1_1.limits = df$TS_1_1_1

df$TS_1_1_1.c = TS_1_1_1.limits

ggplot(data = df)+ theme_bw()+ geom_hline(yintercept = 0)+
  geom_line(aes(TIMESTAMP, TS_1_1_1.c, col = '15 cm'))

plot(df$TS_1_1_1.c)



```

## Rolling MAD 
```{r, warning=FALSE}
f = TS_1_1_1.limits # first make a new flux vector to apply the above filters
# prepare the inputs for a zero-phase (forward and reverse) filter  
ind       = which(complete.cases(f))   # first save the index of all the NAs
b         = rep(1,8)/8                 # moving average coefficient
a         = 1                          # coefficient of the ARMA filter
mad_i    = filtfilt(b, a, na.omit(f)) #create a forward and reverse ARMA filter
mad_filt = f                          # make a copy of the full fluxes again
mad_filt[ind] = mad_i                # apply the filter where the real data exist

n = 7*48 # set the length of the rolling filter, 48 half hours in day * x days
roll.mad = rollapply(data = mad_filt,
                     width = n,
                     FUN = mad,
                     partial = TRUE,
                     na.rm = T,
                     fill = NA)  #create a rolling MAD or sd or other
roll.mad[is.na(mad_filt)] = NA  #make NA values where NAs exist in the real data


ggplot(df)+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,TS_1_1_1.limits,col='Soil T'))+
  geom_line(aes(TIMESTAMP,mad_filt,col='Filter'))+
  geom_line(aes(TIMESTAMP,roll.mad,col='MAD'))+
  scale_y_continuous(limits = c(-8,15))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))+
  scale_color_manual(values=c('yellow','red','black'))
```

```{r, warning=FALSE}
#adjust this value (N) to tweak how many MADs to be away from the norm
N = 10

#Add clean value to dataframe (_.c)

df$TS_1_1_1.c = ifelse(abs(TS_1_1_1.limits - mad_filt) > (N * roll.mad),NA,TS_1_1_1.limits)

#Compare cleaned vs. uncleaned

ggplot(df)+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,TS_1_1_1.limits,col='Uncleaned'))+
  geom_point(aes(TIMESTAMP,df$TS_1_1_1.c,col='Cleaned'))+
  scale_y_continuous(limits = c(-10,15))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))+
  scale_color_manual(values=c('black','red'))

```

```{r, warning=FALSE}

ggplot(data = df)+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*6,ymin = mad_filt-roll.mad*6,fill='6'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*3,ymin = mad_filt-roll.mad*3,fill='3'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*2,ymin = mad_filt-roll.mad*2,fill='2'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*1,ymin = mad_filt-roll.mad*1,fill='1'))+
  geom_point(aes(TIMESTAMP,TS_1_1_1.limits),col='red')+
  geom_point(aes(TIMESTAMP,TS_1_1_1.c),col='black')+
  scale_y_continuous(limits = c(-15,30))
```


#15 Cm depth Therm

```{r, warning=FALSE}

ggplot(data = df)+ theme_bw()+ geom_hline(yintercept = 0)+
  geom_line(aes(TIMESTAMP, TS_2_1_1, col = '15 cm'))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates))

TS_2_1_1.limits = df$TS_2_1_1

df$TS_2_1_1.c = TS_2_1_1.limits

ggplot(data = df)+ theme_bw()+ geom_hline(yintercept = 0)+
  geom_line(aes(TIMESTAMP, TS_2_1_1.c, col = '15 cm'))
#+
 # scale_x_datetime(limits = as.POSIXct(c("2024-07-25",'2024-12-01')))

plot(df$TS_2_1_1.c)
```
## Rolling MAD

```{r, warning=FALSE}
f = TS_2_1_1.limits # first make a new flux vector to apply the above filters
# prepare the inputs for a zero-phase (forward and reverse) filter  
ind       = which(complete.cases(f))   # first save the index of all the NAs
b         = rep(1,8)/8                 # moving average coefficient
a         = 1                          # coefficient of the ARMA filter
mad_i    = filtfilt(b, a, na.omit(f)) #create a forward and reverse ARMA filter
mad_filt = f                          # make a copy of the full fluxes again
mad_filt[ind] = mad_i                # apply the filter where the real data exist

n = 7*48 # set the length of the rolling filter, 48 half hours in day * x days
roll.mad = rollapply(data = mad_filt,
                     width = n,
                     FUN = mad,
                     partial = TRUE,
                     na.rm = T,
                     fill = NA)  #create a rolling MAD or sd or other
roll.mad[is.na(mad_filt)] = NA  #make NA values where NAs exist in the real data


ggplot(df)+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,TS_2_1_1.limits,col='Soil T'))+
  geom_line(aes(TIMESTAMP,mad_filt,col='Filter'))+
  geom_line(aes(TIMESTAMP,roll.mad,col='MAD'))+
  scale_y_continuous(limits = c(-5,15))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))+
  scale_color_manual(values=c('yellow','red','black'))
```


```{r, warning=FALSE}
#adjust this value (N) to tweak how many MADs to be away from the norm
N = 10

#Add clean value to dataframe (_.c)

df$TS_2_1_1.c = ifelse(abs(TS_2_1_1.limits - mad_filt) > (N * roll.mad),NA,TS_2_1_1.limits)

#Compare cleaned vs. uncleaned

ggplot(df)+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,TS_2_1_1.limits,col='Uncleaned'))+
  geom_point(aes(TIMESTAMP,df$TS_2_1_1.c,col='Cleaned'))+
  scale_y_continuous(limits = c(-10,15))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))+
  scale_color_manual(values=c('black','red'))

```


```{r, warning=FALSE}

ggplot(data = df)+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*6,ymin = mad_filt-roll.mad*6,fill='6'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*3,ymin = mad_filt-roll.mad*3,fill='3'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*2,ymin = mad_filt-roll.mad*2,fill='2'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*1,ymin = mad_filt-roll.mad*1,fill='1'))+
  geom_point(aes(TIMESTAMP,TS_2_1_1.limits),col='red')+
  geom_point(aes(TIMESTAMP,TS_2_1_1.c),col='black')+
  scale_y_continuous(limits = c(-15,30))
```

#15 Cm depth Therm

```{r, warning=FALSE}

ggplot(data = df)+ theme_bw()+ geom_hline(yintercept = 0)+
  geom_line(aes(TIMESTAMP, TS_2_2_1, col = '15 cm'))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates))

TS_2_2_1.limits = df$TS_2_2_1

df$TS_2_2_1.c = TS_2_2_1.limits

ggplot(data = df)+ theme_bw()+ geom_hline(yintercept = 0)+
  geom_line(aes(TIMESTAMP, TS_2_2_1.c, col = '15 cm'))
#+
 # scale_x_datetime(limits = as.POSIXct(c("2024-07-25",'2024-12-01')))

plot(df$TS_2_2_1.c)
```
## Rolling MAD

```{r, warning=FALSE}
f = TS_2_2_1.limits # first make a new flux vector to apply the above filters
# prepare the inputs for a zero-phase (forward and reverse) filter  
ind       = which(complete.cases(f))   # first save the index of all the NAs
b         = rep(1,8)/8                 # moving average coefficient
a         = 1                          # coefficient of the ARMA filter
mad_i    = filtfilt(b, a, na.omit(f)) #create a forward and reverse ARMA filter
mad_filt = f                          # make a copy of the full fluxes again
mad_filt[ind] = mad_i                # apply the filter where the real data exist

n = 7*48 # set the length of the rolling filter, 48 half hours in day * x days
roll.mad = rollapply(data = mad_filt,
                     width = n,
                     FUN = mad,
                     partial = TRUE,
                     na.rm = T,
                     fill = NA)  #create a rolling MAD or sd or other
roll.mad[is.na(mad_filt)] = NA  #make NA values where NAs exist in the real data


ggplot(df)+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,TS_2_2_1.limits,col='Soil T'))+
  geom_line(aes(TIMESTAMP,mad_filt,col='Filter'))+
  geom_line(aes(TIMESTAMP,roll.mad,col='MAD'))+
  scale_y_continuous(limits = c(-5,15))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))+
  scale_color_manual(values=c('yellow','red','black'))
```


```{r, warning=FALSE}
#adjust this value (N) to tweak how many MADs to be away from the norm
N = 10

#Add clean value to dataframe (_.c)

df$TS_2_2_1.c = ifelse(abs(TS_2_2_1.limits - mad_filt) > (N * roll.mad),NA,TS_2_2_1.limits)

#Compare cleaned vs. uncleaned

ggplot(df)+geom_hline(yintercept = 0)+
  geom_point(aes(TIMESTAMP,TS_2_2_1.limits,col='Uncleaned'))+
  geom_point(aes(TIMESTAMP,df$TS_2_2_1.c,col='Cleaned'))+
  scale_y_continuous(limits = c(-10,15))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates,format="%F"))+
  scale_color_manual(values=c('black','red'))

```


```{r, warning=FALSE}

ggplot(data = df)+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*6,ymin = mad_filt-roll.mad*6,fill='6'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*3,ymin = mad_filt-roll.mad*3,fill='3'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*2,ymin = mad_filt-roll.mad*2,fill='2'))+
  geom_ribbon(aes(x = TIMESTAMP,ymax = mad_filt+roll.mad*1,ymin = mad_filt-roll.mad*1,fill='1'))+
  geom_point(aes(TIMESTAMP,TS_2_2_1.limits),col='red')+
  geom_point(aes(TIMESTAMP,TS_2_2_1.c),col='black')+
  scale_y_continuous(limits = c(-15,30))
```


# All soil therms
```{r, warning=FALSE}
ggplot(data = df)+ theme_bw()+
  geom_hline(yintercept = 0)+
  geom_line(aes(TIMESTAMP,TS_1_1_1.c,color='15_1 cm'))+
  geom_line(aes(TIMESTAMP,TS_2_1_1.c,color='15_2 cm'))+
  geom_line(aes(TIMESTAMP,TS_2_2_1.c,color='15_3 cm'))
  
 # scale_x_datetime(biomet_dates)
```




# Volumetric Water Content
```{r, warning=FALSE}
ggplot(data = df)+
  geom_point(aes(TIMESTAMP, SWC_1_1_1*100,col='SWC 1'))+
  geom_point(aes(TIMESTAMP, SWC_2_1_1*100,col='SWC 2'))+
  geom_point(aes(TIMESTAMP, SWC_2_2_1*100,col='SWC 3'))+
  scale_y_continuous(limits = c(0,100),
                     expression('% VWC'))+
  scale_x_datetime(limits = as.POSIXct(biomet_dates))
```

# Save

```{r, warning=FALSE}
write.csv(x = df,file = 'C:/Users/klynoe/Documents/toolik/R_outputs/met/biomet_clean',row.names = F,quote = T)

```

# Save as individual month

```{r, warning = F}

base_path = "C:/Users/klynoe/Documents/toolik/R_outputs/met/"


met <- met %>%
  mutate(
  TIMESTAMP_fixed = sub("(\\d{4}-\\d{2}-\\d{2}) (\\d{2})(\\d{2})", "\\1 \\2:\\3", TIMESTAMP),
   TIMESTAMP = as.POSIXct(TIMESTAMP_fixed, format = "%Y-%m-%d %H:%M", tz = "UTC")
 )

data_nested = met %>%
  mutate(TIMESTAMP = as.POSIXct(TIMESTAMP, format = "%Y-%m-%d %H:%M:%S")) %>%
  mutate(year_month = format(TIMESTAMP, "%Y%m")) %>%
  group_by(year_month) %>%
  nest() %>%
  ungroup() %>%  # Important to prevent errors with grouped data
  mutate(file_path = paste0(base_path, "toolik_gth89_biomet_", year_month, ".csv"))

walk2(
  .x = data_nested$data, 
  .y = data_nested$file_path, 
  ~ {
    # Ensure the nested data frame has the same column names and types as units_row
    .x[] = lapply(.x, as.character)  # Convert all columns to character
    
    # Write to CSV
    write.csv(.x, .y, row.names = FALSE)
  }
)



#knitr::opts_chunk$set(echo = TRUE)
```





