---
title: "Data Quality Check"
author: "Dani Trangmoe"
date: "`r Sys.Date()`"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(error =  TRUE)
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = 'C:/Users/klynoe/Documents/toolik/R_outputs/flux_met_c/') #use this to set your directory
```


This file generates plots for the monthly data check meetings


```{r, include=FALSE}
# Load packages, cleaned data 

rm(list = ls())

library(data.table)
library(ggplot2)
library(cowplot)
library(openair)
library(plotrix)
library(signal)
library(svMisc)
library(zoo)
library(stringr)
library(plyr)
library(dplyr)
library(patchwork) # formats plots
library(bigleaf) # for radiation check
library(scales)
library(lubridate)
library(tidyr)
library(openair)
```


```{r, include = FALSE}

df <- fread('./toolik_flux_c_met_c_202505_202512.csv')

#df$ts <- df$ts-9*3600 #adjust timezone from UTC to CST
#df$TIMESTAMP <- df$TIMESTAMP-9*3600 #adjust timezone from UTC to CST

df_month <- subset(df, df$TIMESTAMP >= as.POSIXct("2025-11-01 0000", tz = "UTC"))


# data formatting for flag plots
# Ensure flags are character first
df$co2_flux.flag <- as.character(df$co2_flux.flag)
df$ch4_flux.flag <- as.character(df$ch4_flux.flag)

# Then assign factor with explicit levels
df$co2_flux.flag <- factor(df$co2_flux.flag, levels = c("0","1","2","3","4","5"))
df$ch4_flux.flag <- factor(df$ch4_flux.flag, levels = c("0","1","2","3","4","5"))

#df$co2_flux.flag <- as.factor(df$co2_flux.flag)
#df$ch4_flux.flag <- as.factor(df$ch4_flux.flag)

color_map = c("0" = "yellow3", "1" = "darkblue" , "2" =  "red4", "3" = "orange", "4" = "green4", "5" = "purple")

```



# Timeseries Plots

Flag = 0, 1, 2 : EP Flag
Flag = 3 : Absolute Limits Filter
Flag = 4 : Rolling MAD Filter
Flag = 5 : Diagnostic filter


## CO2

CO2 is cleaned with absolute limits of 8 & -15, and a limit of 3 MADs away from the mean over a 7 day window

#### Year-to-Date CO2
```{r, warning=FALSE, echo=FALSE}

# Flag = 0, 1, 2 : EP Flag
# Flag = 3 : Absolute Limits Filter
# Flag = 4 : Rolling MAD Filter
# Flag = 5 : Diagnostic filter

nee_plot_ytd = ggplot(data = df)+geom_hline(yintercept = 0)+
  geom_point(data = subset(df, !is.na(co2_flux.flag)),
    aes(TIMESTAMP,co2_flux,color = co2_flux.flag))+
  geom_point(aes(TIMESTAMP,co2_flux.c),col='black')+
  scale_y_continuous(limits=c(-12,8))+
  scale_x_datetime(limits = as.POSIXct(c("2025-05-01", "2025-12-16")))+
  labs(
    x = NULL,
    y = expression(paste( ~CO[2], ~"Flux (umol m",""^"-2","s",""^"-1",")"))
  ) +
scale_color_manual(values = color_map, name = "Cleaning Flag")
nee_plot_ytd
```
```{r, warning=FALSE}
# Flag = 0, 1, 2 : EP Flag
# Flag = 3 : Absolute Limits Filter
# Flag = 4 : Rolling MAD Filter
# Flag = 5 : Diagnostic filter

nee_plot_ytd = ggplot(data = df)+geom_hline(yintercept = 0)+
  geom_point(data = subset(df, !is.na(co2_flux.flag)),
    aes(TIMESTAMP,co2_flux,color = co2_flux.flag))+
  geom_point(aes(TIMESTAMP,co2_flux.c),col='black')+
  scale_y_continuous(limits=c(-30,30))+
  scale_x_datetime(limits = as.POSIXct(c("2025-05-01", "2025-12-16")))+
  labs(
    x = NULL,
    y = expression(paste( ~CO[2], ~"Flux (umol m",""^"-2","s",""^"-1",")"))
  ) +
scale_color_manual(values = color_map, name = "Cleaning Flag")
nee_plot_ytd

```

## Previous Month CO2
```{r, warning=FALSE, echo=FALSE}

# Flag = 0, 1, 2 : EP Flag
# Flag = 3 : Absolute Limits Filter
# Flag = 4 : Rolling MAD Filter
# Flag = 5 : Diagnostic filter

nee_plot_month = ggplot(data = df)+geom_hline(yintercept = 0)+
  geom_point(data = subset(df, !is.na(co2_flux.flag)),
    aes(TIMESTAMP,co2_flux,color = co2_flux.flag))+
  geom_point(aes(TIMESTAMP,co2_flux.c),col='black')+
  scale_y_continuous(limits=c(-12,8))+
    labs(
    x = NULL,
    y = expression(paste( ~CO[2], ~"Flux (umol m",""^"-2","s",""^"-1",")"))
  ) +
  scale_x_datetime(limits = as.POSIXct(c("2025-11-01", "2025-11-30")))+
scale_color_manual(values = color_map, name = "QC CO2 Flux")
nee_plot_month

```


## Week zoom-in CO2
```{r, warning=FALSE, echo=FALSE}

# Flag = 0, 1, 2 : EP Flag
# Flag = 3 : Absolute Limits Filter
# Flag = 4 : Rolling MAD Filter
# Flag = 5 : Diagnostic filter

nee_plot_week = ggplot(data = df)+geom_hline(yintercept = 0)+
  geom_point(data = subset(df, !is.na(co2_flux.flag)),
    aes(TIMESTAMP,co2_flux,color = co2_flux.flag))+
  geom_point(aes(TIMESTAMP,co2_flux.c),col='black')+
  scale_y_continuous(limits=c(-12,8))+
    labs(
    x = NULL,
    y = expression(paste( ~CO[2], ~"Flux (umol m",""^"-2","s",""^"-1",")"))
  ) +
  scale_x_datetime(limits = as.POSIXct(c("2025-11-02", "2025-11-08")))+
scale_color_manual(values = color_map, name = "QC CO2 Flux")
nee_plot_week

```


## Methane

Methane is cleaned with absolute limits of -0.15 & 0.28, and a limit of 8 MADs away from the mean over a 7 day window

#### Year-to-Date Methane
```{r, warning=FALSE, echo=FALSE}

# Flag = 0, 1, 2 : EP Flag
# Flag = 3 : Absolute Limits Filter
# Flag = 4 : Rolling MAD Filter
# Flag = 5 : Diagnostic filter

ch4_plot_year = ggplot(data = df)+geom_hline(yintercept = 0)+
  geom_point(data = subset(df, !is.na(ch4_flux.flag)),
    aes(TIMESTAMP,ch4_flux,color = ch4_flux.flag))+
  geom_point(aes(TIMESTAMP,ch4_flux.c),col='black')+
  scale_y_continuous(limits=c(-0.1,0.33))+
  labs(
    x = NULL,
    y = expression(paste( ~CH[4], ~"Flux (umol m",""^"-2","s",""^"-1",")"))
  ) +
  scale_x_datetime(limits = as.POSIXct(c("2025-05-01", "2025-12-16")))+
scale_color_manual(values = color_map, name = "QC CH4 Flux")
ch4_plot_year

```

```{r, warning=FALSE}
# Flag = 0, 1, 2 : EP Flag
# Flag = 3 : Absolute Limits Filter
# Flag = 4 : Rolling MAD Filter
# Flag = 5 : Diagnostic filter

ch4_plot_year = ggplot(data = df)+geom_hline(yintercept = 0)+
  geom_point(data = subset(df, !is.na(ch4_flux.flag)),
    aes(TIMESTAMP,ch4_flux,color = ch4_flux.flag))+
  geom_point(aes(TIMESTAMP,ch4_flux.c),col='black')+
  scale_y_continuous(limits=c(-1,1))+
  labs(
    x = NULL,
    y = expression(paste( ~CH[4], ~"Flux (umol m",""^"-2","s",""^"-1",")"))
  ) +
  scale_x_datetime(limits = as.POSIXct(c("2025-05-01", "2025-12-16")))+
scale_color_manual(values = color_map, name = "QC CH4 Flux")
ch4_plot_year

```

#### Previous Month Methane
```{r, warning=FALSE, echo=FALSE}

# Flag = 0, 1, 2 : EP Flag
# Flag = 3 : Absolute Limits Filter
# Flag = 4 : Rolling MAD Filter
# Flag = 5 : Diagnostic filter
ch4_plot_month = ggplot(data = df)+geom_hline(yintercept = 0)+
  geom_point(data = subset(df, !is.na(ch4_flux.flag)),
    aes(TIMESTAMP,ch4_flux,color = ch4_flux.flag))+
  geom_point(aes(TIMESTAMP,ch4_flux.c),col='black')+
  scale_y_continuous(limits=c(-0.08,0.08))+  
  labs(
    x = NULL,
    y = expression(paste( ~CH[4], ~"Flux (umol m",""^"-2","s",""^"-1",")"))
  ) +
  scale_x_datetime(limits = as.POSIXct(c("2025-10-01", "2025-10-31")))+
scale_color_manual(values = color_map, name = "QC CH4 Flux")
ch4_plot_month


ch4_plot_month = ggplot(data = df)+geom_hline(yintercept = 0)+
  geom_point(data = subset(df, !is.na(ch4_flux.flag)),
    aes(TIMESTAMP,ch4_flux,color = ch4_flux.flag))+
  geom_point(aes(TIMESTAMP,ch4_flux.c),col='black')+
  scale_y_continuous(limits=c(-0.05,0.051))+  
  labs(
    x = NULL,
    y = expression(paste( ~CH[4], ~"Flux (umol m",""^"-2","s",""^"-1",")"))
  ) +
  scale_x_datetime(limits = as.POSIXct(c("2025-11-01", "2025-11-30")))+
scale_color_manual(values = color_map, name = "QC CH4 Flux")
ch4_plot_month



```


#### Week zoom-in Methane
```{r, warning=FALSE, echo=FALSE}

# Flag = 0, 1, 2 : EP Flag
# Flag = 3 : Absolute Limits Filter
# Flag = 4 : Rolling MAD Filter
# Flag = 5 : Diagnostic filter

ch4_plot_week = ggplot(data = df)+geom_hline(yintercept = 0)+
  geom_point(data = subset(df, !is.na(ch4_flux.flag)),
    aes(TIMESTAMP,ch4_flux,color = ch4_flux.flag))+
  geom_point(aes(TIMESTAMP,ch4_flux.c),col='black')+
  scale_y_continuous(limits=c(-0.1,0.0833))+
  labs(
    x = NULL,
    y = expression(paste( ~CH[4], ~"Flux (umol m",""^"-2","s",""^"-1",")"))
  ) +
  scale_x_datetime(limits = as.POSIXct(c("2025-10-18", "2025-10-26")))+
scale_color_manual(values = color_map, name = "QC CH4 Flux")
ch4_plot_week

ch4_plot_week = ggplot(data = df)+geom_hline(yintercept = 0)+
  geom_point(data = subset(df, !is.na(ch4_flux.flag)),
    aes(TIMESTAMP,ch4_flux,color = ch4_flux.flag))+
  geom_point(aes(TIMESTAMP,ch4_flux.c),col='black')+
  scale_y_continuous(limits=c(-0.1,0.0833))+
  labs(
    x = NULL,
    y = expression(paste( ~CH[4], ~"Flux (umol m",""^"-2","s",""^"-1",")"))
  ) +
  scale_x_datetime(limits = as.POSIXct(c("2025-11-18", "2025-11-20")))+
scale_color_manual(values = color_map, name = "QC CH4 Flux")
ch4_plot_week

```



# Energy Balance Plots

#### Full Year-to-date
```{r, warning=FALSE, echo=FALSE}

df$met = ((df$LWIN_6_14_1_1_1.c + df$SWIN_6_10_1_1_1.c) -
         (df$LWOUT_6_15_1_1_1.c + df$SWOUT_6_11_1_1_1.c)) -
        ((df$SHF_6_37_1_1_1.c + df$SHF_6_37_2_1_1.c)/2)
df$flux = df$H.c + df$LE.c

# Fit linear model
mod = lm(flux ~ met, data = df)
summary_mod = summary(mod)

# Extract slope and R²
slope = coef(mod)["met"]
r2 = summary_mod$r.squared
cat("Slope:", slope, "\nR²:", r2, "\n")

# Define axis limits
x_lim = c(-200,500)
y_lim = c(-200,500)


# Plot
eb_ytd <- ggplot(df, aes(x = met, y = flux)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", color = "blue", se = FALSE) +
  geom_abline(slope = 1, intercept = 0,
               linetype = "dashed", color = "red") +
  geom_hline(yintercept = 0, linetype = "solid", color = "black") +
  geom_vline(xintercept = 0, linetype = "solid", color = "black") +
  coord_fixed(ratio = 1, xlim = x_lim, ylim = y_lim) +
  labs(
    x = expression("Rn - G  (Wm"^-2*")"),
    y = expression("H + LE  (Wm"^-2*")"),
    title = expression("Full Year EB")
  ) +
  annotate(
    "text",
    x = Inf, y = -Inf,
    label = paste0("Slope = ", round(slope, 3), "\nR² = ", round(r2, 3)),
    hjust = 1.1, vjust = -0.5, size = 4
  ) +
  theme_bw()
eb_ytd
```



#### Previous Month
```{r, warning=FALSE, echo=FALSE}

df_month$met = ((df_month$LWIN_6_14_1_1_1.c + df_month$SWIN_6_10_1_1_1.c) -
         (df_month$LWOUT_6_15_1_1_1.c + df_month$SWOUT_6_11_1_1_1.c)) -
        ((df_month$SHF_6_37_1_1_1.c + df_month$SHF_6_37_2_1_1.c)/2)
df_month$flux = df_month$H.c + df_month$LE.c

# Fit linear model
mod = lm(flux ~ met, data = df_month)
summary_mod = summary(mod)

# Extract slope and R²
slope = coef(mod)["met"]
r2 = summary_mod$r.squared
cat("Slope:", slope, "\nR²:", r2, "\n")

# Define axis limits
x_lim = c(-200,500)
y_lim = c(-200,500)

# Plot
eb_month <- ggplot(df_month, aes(x = met, y = flux)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", color = "blue", se = FALSE) +
  geom_abline(slope = 1, intercept = 0,
               linetype = "dashed", color = "red") +
  geom_hline(yintercept = 0, linetype = "solid", color = "black") +
  geom_vline(xintercept = 0, linetype = "solid", color = "black") +
  coord_fixed(ratio = 1, xlim = x_lim, ylim = y_lim) +
  labs(
    x = expression("Rn - G  (Wm"^-2*")"),
    y = expression("H + LE  (Wm"^-2*")"),
    title = expression("Previous Month EB")
  ) +
  annotate(
    "text",
    x = Inf, y = -Inf,
    label = paste0("Slope = ", round(slope, 3), "\nR² = ", round(r2, 3)),
    hjust = 1.1, vjust = -0.5, size = 4
  ) +
  theme_bw()
eb_month

```
```{r, warning=FALSE}
p_H <- ggplot(data = df) +
  theme_bw() +
  geom_hline(yintercept = 0, linetype = "dashed", color = "black") +
  geom_line(aes(x = TIMESTAMP, y = H.c), linewidth = 1.2, color = "firebrick") +
  labs(
    x = "Time",
    y = "H (W/m²)",
    title = "Sensible Heat Flux (H)"
  )
p_LE <- ggplot(data = df) +
  theme_bw() +
  geom_hline(yintercept = 0, linetype = "dashed", color = "black") +
  geom_line(aes(x = TIMESTAMP, y = LE.c), linewidth = 1.2, color = "dodgerblue") +
  labs(
    x = "Time",
    y = "LE (W/m²)",
    title = "Latent Heat Flux (LE)"
  )
p_H/p_LE


```
```{r, warning=FALSE}

p_flux <- ggplot(data = df) +
  theme_bw() +
  geom_hline(yintercept = 0, linetype = "dashed", color = "black") +
  geom_line(aes(x = TIMESTAMP, y = H.c, color = "H"), linewidth = 1) +
  geom_line(aes(x = TIMESTAMP, y = LE.c, color = "LE"), linewidth = 1) +
  scale_color_manual(
    name = "Flux",
    values = c("H" = "firebrick", "LE" = "dodgerblue")
  ) +
  labs(
    x = "Time",
    y = "Flux (W/m²)",
    title = "H & LE"
  )

df$EB <- df$H.c + df$LE.c

p_eb <- ggplot(data = df) +
  theme_bw() +
  geom_hline(yintercept = 0, linetype = "dashed", color = "purple3") +
  geom_line(aes(x = TIMESTAMP, y = EB), linewidth = 1) +
  labs(
    x = "Time",
    y = "EB (W/m²)",
    title = "Energy Balance (H + LE)"
  )
p_flux / p_eb

```
```{r, warning=FALSE}
start_date <- as.POSIXct("2025-10-08", tz = "UTC")
end_date   <- as.POSIXct("2025-10-14", tz = "UTC")

df2 <- subset(df, TIMESTAMP >= start_date & TIMESTAMP <= end_date)
p_flux <- ggplot(data = df2) +
  theme_bw() +
  geom_hline(yintercept = 0, linetype = "dashed", color = "black") +
  geom_line(aes(x = TIMESTAMP, y = H.c, color = "H"), linewidth = 1.2) +
  geom_line(aes(x = TIMESTAMP, y = LE.c, color = "LE"), linewidth = 1.2) +
  scale_color_manual(
    name = "Flux",
    values = c("H" = "firebrick", "LE" = "dodgerblue")
  ) +
  labs(
    x = "Time",
    y = "Flux (W/m²)",
    title = "H & LE"
  )
df2$EB <- df2$H.c + df2$LE.c

p_eb <- ggplot(data = df2) +
  theme_bw() +
  geom_hline(yintercept = 0, linetype = "dashed", color = "purple3") +
  geom_line(aes(x = TIMESTAMP, y = EB), linewidth = 1.2, color = "black") +
  labs(
    x = "Time",
    y = "EB (W/m²)",
    title = "Energy Balance (H + LE)"
  )
p_flux / p_eb


```


```{r, warning=FALSE}
start_date <- as.POSIXct("2025-07-01", tz = "UTC")
end_date   <- as.POSIXct("2025-07-10", tz = "UTC")

df2 <- subset(df, TIMESTAMP >= start_date & TIMESTAMP <= end_date)
p_flux <- ggplot(data = df2) +
  theme_bw() +
  geom_hline(yintercept = 0, linetype = "dashed", color = "black") +
  geom_line(aes(x = TIMESTAMP, y = H.c, color = "H"), linewidth = 1.2) +
  geom_line(aes(x = TIMESTAMP, y = LE.c, color = "LE"), linewidth = 1.2) +
  scale_color_manual(
    name = "Flux",
    values = c("H" = "firebrick", "LE" = "dodgerblue")
  ) +
  labs(
    x = "Time",
    y = "Flux (W/m²)",
    title = "H & LE Heat Flux"
  )

df2$EB <- df2$H.c + df2$LE.c

p_eb <- ggplot(data = df2) +
  theme_bw() +
  geom_hline(yintercept = 0, linetype = "dashed", color = "purple3") +
  geom_line(aes(x = TIMESTAMP, y = EB), linewidth = 1.2) +
  labs(
    x = "Time",
    y = "EB (W/m²)",
    title = "Energy Balance (H + LE)"
  )
p_flux / p_eb

```
```{r, warning=FALSE}



```

```{r,warning=FALSE}
df_wind_openair <- df %>%
  filter(!is.na(wind_dir) & !is.na(WS_16_33_1_1_1)) %>%
  rename(
    wd = wind_dir,
    ws = WS_16_33_1_1_1
  )

windRose(df_wind_openair,
         ws = "ws",
         wd = "wd",
         paddle = FALSE,
         key = TRUE,
         main = "Wind Rose")
```

```{r, warning=FALSE}





```




```{r, warning=FALSE}




```


```{r, warning=F}




```


### rpot vs swin
```{r}


```

```{r, warning=FALSE}

ggplot(df, aes(x = TIMESTAMP)) +
  geom_line(aes(y = rpot), color = "blue") +                        # RPOT line
  geom_point(aes(y = SWIN_6_10_1_1_1), color = "black") +          # all SWIN points
  geom_point(data = subset(df, SWIN_6_10_1_1_1.c > rpot),            # only misaligned
             aes(y = SWIN_6_10_1_1_1.c), color = "red", size = .5) +
  theme_minimal() +
  coord_cartesian(xlim = as.POSIXct(c("2025-10-01 00:00", "2025-10-30 23:59")))


```

```{r, warning=FALSE}


ggplot(df, aes(x = TIMESTAMP)) +
  geom_line(aes(y = rpot), color = "blue") +                        # RPOT line
  geom_point(aes(y = SWIN_6_10_1_1_1), color = "black") +          # all SWIN points
  geom_point(data = subset(df, SWIN_6_10_1_1_1.c > rpot),            # only misaligned
             aes(y = SWIN_6_10_1_1_1.c), color = "red", size = .5) +
  theme_minimal() +
  coord_cartesian(xlim = as.POSIXct(c("2025-10-01 00:00", "2025-10-14 23:59")))



```

#### Full Year-to-Date
```{r, warning=FALSE, echo=FALSE}


```


#### Previous Month
```{r, warning=FALSE, echo=FALSE}


```

```{r}





```

```{r, warning=FALSE}

```

```{r, warning=FALSE}

```

# Diurnal Fluxes

```{r, warning=FALSE, echo=FALSE}
# set hour and month vectors to be able to take the averages

df <- dplyr::filter(df, !df$TIMESTAMP < as.POSIXct("2025-05-01 00:00:00"))

df$hour = as.numeric(format(df$ts,'%H'))
df$month = as.numeric(format(df$ts,'%m'))

diel = df %>%
  group_by(hour,month) %>%
  select(co2_flux.c,ch4_flux.c,LE.c,H.c, RN_6_5_1_1_1.c, u., TKE, hour,month) %>%
  summarise_all(.funs = c(median,sd),na.rm=T)

diel = subset(diel,!is.na(diel$month))
```

#### NEE

```{r, warning=FALSE, echo=FALSE}
diurnal_nee <- ggplot(data = diel)+geom_hline(yintercept = 0)+
  geom_line(aes(hour,co2_flux.c_fn1),lty=2)+
  geom_ribbon(aes(x = hour,y = co2_flux.c_fn1,
                  ymax = co2_flux.c_fn1 + co2_flux.c_fn2,
                  ymin = co2_flux.c_fn1 - co2_flux.c_fn2),
              alpha= 0.5)+
  facet_wrap(~month)
diurnal_nee
```

#### CH4

```{r, warning=FALSE, echo=FALSE}
diurnal_ch4 <- ggplot(data = diel)+geom_hline(yintercept = 0)+
  geom_line(aes(hour,ch4_flux.c_fn1),lty=2)+
  geom_ribbon(aes(x = hour,y = ch4_flux.c_fn1,
                  ymax = ch4_flux.c_fn1 + ch4_flux.c_fn2,
                  ymin = ch4_flux.c_fn1 - ch4_flux.c_fn2),
              alpha= 0.5)+
  facet_wrap(~month)
diurnal_ch4

```

#temps
```{r, warning=FALSE}

p_soil <- ggplot(data = df) +
  theme_bw() +
  geom_hline(yintercept = 0, linetype = "dashed", color = "black") +
  geom_line(aes(x = TIMESTAMP, y = TS_2_38_1_1_1.c, color = "8 cm")) +
  geom_line(aes(x = TIMESTAMP, y = TS_2_38_2_1_1.c, color = "18 cm")) +
  geom_line(aes(x = TIMESTAMP, y = TS_2_38_23_1_1.c, color = "28 cm")) +
  scale_color_manual(
    name = "Sensor Depth",
    values = c("8 cm" = "blue", "18 cm" = "green", "28 cm" = "gold3")
  ) +
  labs(x = "Time",
       y = "Soil Temperature (°C)",
       title = "Soil Temperature by Depth")

p_air <- ggplot(data = df) +
  theme_bw() +
  geom_hline(yintercept = 0, linetype = "dashed", color = "black") +
  geom_line(aes(x = TIMESTAMP, y = TA_2_1_1_1_1.c), color = "red") +
  labs(x = "Time",
       y = "Air Temperature (°C)",
       title = "Air Temperature")

p_soil/p_air



```


```{r, warning=FALSE}
t1 <- as.POSIXct("2025-10-10 00:00:00", tz="UTC")
t2 <- as.POSIXct("2025-10-20 00:00:00", tz="UTC")

df_sub <- subset(df, TIMESTAMP >= t1 & TIMESTAMP <= t2)

p_soil <- ggplot(data = df_sub) +
  theme_bw() +
  geom_hline(yintercept = 0, linetype = "dashed", color = "black") +
  geom_line(aes(x = TIMESTAMP, y = TS_2_38_1_1_1.c, color = "8 cm"), linewidth = 1.2) +
  geom_line(aes(x = TIMESTAMP, y = TS_2_38_2_1_1.c, color = "18 cm"), linewidth = 1.2) +
  geom_line(aes(x = TIMESTAMP, y = TS_2_38_23_1_1.c, color = "28 cm"), linewidth = 1.2) +
  scale_color_manual(
    name = "Sensor Depth",
    values = c("8 cm" = "blue", "18 cm" = "green", "28 cm" = "gold3")
  ) +
  labs(x = "Time",
       y = "Soil Temperature (°C)",
       title = "Soil Temperature")

p_air <- ggplot(data = df_sub) +
  theme_bw() +
  geom_hline(yintercept = 0, linetype = "dashed", color = "black") +
  geom_line(aes(x = TIMESTAMP, y = TA_2_1_1_1_1.c), color = "red", linewidth = 1.2) +
  labs(x = "Time",
       y = "Air Temperature (°C)",
       title = "Air Temperature")

p_soil / p_air

```
```{r, warning=FALSE}
# define date range


```

#soil T and groud heat flux (G)

```{r, warning=FALSE}
# Compute G
df$G <- (df$SHF_6_37_1_1_1.c + df$SHF_6_37_2_1_1.c) / 2

# Surface temp variable
df$TS <- df$TS_2_38_1_1_1.c

# Define date window
t1 <- as.POSIXct("2025-07-10 00:00:00", tz = "UTC")
t2 <- as.POSIXct("2025-11-20 00:00:00", tz = "UTC")

# Subset
df_sub <- subset(df, TIMESTAMP >= t1 & TIMESTAMP <= t2)


# ---- TIME SERIES (fixed dual-axis) ----

# Scaling factor
sf <- max(df_sub$TS, na.rm = TRUE) / max(df_sub$G, na.rm = TRUE)

ggplot(df_sub, aes(x = TIMESTAMP)) +
  geom_line(aes(y = TS, color = "TS (°C)"), linewidth = 0.7) +
  geom_line(aes(y = G * sf, color = "G (W/m²)"), linewidth = 0.7) +
  scale_y_continuous(
    name = "Temperature -8 cm (°C)",
    sec.axis = sec_axis(~ . / sf, name = "Soil Heat Flux (W/m²)")
  ) +
  scale_color_manual(values = c("TS (°C)" = "red", "G (W/m²)" = "blue")) +
  labs(
    x = "Time",
    color = "Variable",
    title = ""
  ) +
  theme_minimal() +
  theme(
    axis.title.y.left = element_text(color = "red"),
    axis.title.y.right = element_text(color = "blue"),
    legend.position = "top"
  )



```

#soil T and groud heat flux (G)
# close up
```{r,warning=FALSE}
# Compute G
df$G <- (df$SHF_6_37_1_1_1.c + df$SHF_6_37_2_1_1.c) / 2

# Surface temp variable
df$TS <- df$TS_2_38_1_1_1.c

# Define date window
t1 <- as.POSIXct("2025-10-26 00:00:00", tz = "UTC")
t2 <- as.POSIXct("2025-11-03 00:00:00", tz = "UTC")

# Subset
df_sub <- subset(df, TIMESTAMP >= t1 & TIMESTAMP <= t2)


# ---- TIME SERIES (fixed dual-axis) ----

# Scaling factor
sf <- max(df_sub$TS, na.rm = TRUE) / max(df_sub$G, na.rm = TRUE)

ggplot(df_sub, aes(x = TIMESTAMP)) +
  geom_line(aes(y = TS, color = "TS (°C)"), linewidth = 0.7) +
  geom_line(aes(y = G * sf, color = "G (W/m²)"), linewidth = 0.7) +
  scale_y_continuous(
    name = "Temperature -8 cm (°C)",
    sec.axis = sec_axis(~ . / sf, name = "Soil Heat Flux (W/m²)")
  ) +
  scale_color_manual(values = c("TS (°C)" = "red", "G (W/m²)" = "blue")) +
  labs(
    x = "Time",
    color = "Variable",
    title = ""
  ) +
  theme_minimal() +
  theme(
    axis.title.y.left = element_text(color = "red"),
    axis.title.y.right = element_text(color = "blue"),
    legend.position = "top"
  )





```
# T air vs Sonic

```{r, warning=FALSE}
# Add month column
df <- df %>%
  mutate(month = as.numeric(format(TIMESTAMP, "%m")))

# List unique months in order
months <- sort(unique(df$month))

# List to store plots
plots <- list()

for (m in months) {
  df_month <- df %>% filter(month == m)
  
  p <- ggplot(df_month, aes(x = TIMESTAMP)) +
    geom_line(aes(y = TA_2_1_1_1_1.c, color = "Air Temp"), linewidth = 0.8) +
    geom_line(aes(y = sonic_temperature - 273.15, color = "Sonic Temp"), linewidth = 0.8) +
    geom_hline(yintercept = 0, linetype = "dashed", color = "black") +
    scale_color_manual(values = c("Air Temp" = "red", "Sonic Temp" = "blue")) +
    labs(
      x = "Time",
      y = "Temperature (°C)",
      color = "Sensor",
      title = paste("Month:", m)
    ) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1))
  
  plots[[paste0("temp_month_", m)]] <- p
}

# Print all plots (auto)
for (name in names(plots)) {
  print(plots[[name]])
}




```


```{r, warning=FALSE}


# Add month column
df <- df %>%
  mutate(month = as.numeric(format(TIMESTAMP, "%m")))

# List of unique months
months <- sort(unique(df$month))

# Loop to generate separate plots per month
plots <- list()

for (m in months) {
  df_month <- df %>% filter(month == m)
  
  p <- ggplot(df_month, aes(x = TIMESTAMP)) +
    geom_line(aes(y = TA_2_1_1_1_1.c, color = "Air Temp"), size = 0.8) +
    geom_line(aes(y = sonic_temperature - 273.15, color = "Sonic Temp"), size = 0.8) +
    geom_hline(yintercept = 0, linetype = "dashed", color = "black") +
    scale_color_manual(values = c("Air Temp" = "red", "Sonic Temp" = "blue")) +
    labs(
      x = "Time",
      y = "Temperature (°C)",
      color = "Sensor",
      title = paste("Month:", m)
    ) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1))
  
  plots[[paste0("temp_month_", m)]] <- p
}

# Example: print January (month 1)
plots$temp_month_1

# To view all plots sequentially
for (name in names(plots)) {
  print(plots[[name]])
  readline(prompt = paste("Displaying:", name, "- Press [Enter] for next plot."))
}

```



