---
title: "Data Quality Check"
author: "Dani Trangmoe"
date: "`r Sys.Date()`"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(error =  TRUE)
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = 'C:/Users/klynoe/Documents/toolik/R_outputs/flux_met_c/') #use this to set your directory
```


This file generates plots for the monthly data check meetings


```{r, include=FALSE}
# Load packages, cleaned data 

rm(list = ls())

library(data.table)
library(ggplot2)
library(cowplot)
library(openair)
library(plotrix)
library(signal)
library(svMisc)
library(zoo)
library(stringr)
library(plyr)
library(dplyr)
library(patchwork) # formats plots
library(bigleaf) # for radiation check
library(scales)
library(lubridate)
library(tidyr)
```


```{r, include = FALSE}

df <- fread('./toolik_flux_c_met_c_202505_202512.csv')

#df$ts <- df$ts-9*3600 #adjust timezone from UTC to CST
#df$TIMESTAMP <- df$TIMESTAMP-9*3600 #adjust timezone from UTC to CST

df_month <- subset(df, df$TIMESTAMP >= as.POSIXct("2025-11-01 0000", tz = "UTC"))


# data formatting for flag plots
# Ensure flags are character first
df$co2_flux.flag <- as.character(df$co2_flux.flag)
df$ch4_flux.flag <- as.character(df$ch4_flux.flag)

# Then assign factor with explicit levels
df$co2_flux.flag <- factor(df$co2_flux.flag, levels = c("0","1","2","3","4","5"))
df$ch4_flux.flag <- factor(df$ch4_flux.flag, levels = c("0","1","2","3","4","5"))

#df$co2_flux.flag <- as.factor(df$co2_flux.flag)
#df$ch4_flux.flag <- as.factor(df$ch4_flux.flag)

color_map = c("0" = "yellow3", "1" = "darkblue" , "2" =  "red4", "3" = "orange", "4" = "green4", "5" = "purple")

```



# Timeseries Plots

Flag = 0, 1, 2 : EP Flag
Flag = 3 : Absolute Limits Filter
Flag = 4 : Rolling MAD Filter
Flag = 5 : Diagnostic filter


## CO2

CO2 is cleaned with absolute limits of 8 & -15, and a limit of 3 MADs away from the mean over a 7 day window

#### Year-to-Date CO2
```{r, warning=FALSE, echo=FALSE}

# Flag = 0, 1, 2 : EP Flag
# Flag = 3 : Absolute Limits Filter
# Flag = 4 : Rolling MAD Filter
# Flag = 5 : Diagnostic filter

nee_plot_ytd = ggplot(data = df)+geom_hline(yintercept = 0)+
  geom_point(data = subset(df, !is.na(co2_flux.flag)),
    aes(TIMESTAMP,co2_flux,color = co2_flux.flag))+
  geom_point(aes(TIMESTAMP,co2_flux.c),col='black')+
  scale_y_continuous(limits=c(-12,8))+
  scale_x_datetime(limits = as.POSIXct(c("2025-05-01", "2025-12-16")))+
  labs(
    x = NULL,
    y = expression(paste( ~CO[2], ~"Flux (umol m",""^"-2","s",""^"-1",")"))
  ) +
scale_color_manual(values = color_map, name = "Cleaning Flag")
nee_plot_ytd
```


## Previous Month CO2
```{r, warning=FALSE, echo=FALSE}

# Flag = 0, 1, 2 : EP Flag
# Flag = 3 : Absolute Limits Filter
# Flag = 4 : Rolling MAD Filter
# Flag = 5 : Diagnostic filter

nee_plot_month = ggplot(data = df)+geom_hline(yintercept = 0)+
  geom_point(data = subset(df, !is.na(co2_flux.flag)),
    aes(TIMESTAMP,co2_flux,color = co2_flux.flag))+
  geom_point(aes(TIMESTAMP,co2_flux.c),col='black')+
  scale_y_continuous(limits=c(-12,8))+
    labs(
    x = NULL,
    y = expression(paste( ~CO[2], ~"Flux (umol m",""^"-2","s",""^"-1",")"))
  ) +
  scale_x_datetime(limits = as.POSIXct(c("2025-11-01", "2025-11-30")))+
scale_color_manual(values = color_map, name = "QC CO2 Flux")
nee_plot_month

```


## Week zoom-in CO2
```{r, warning=FALSE, echo=FALSE}

# Flag = 0, 1, 2 : EP Flag
# Flag = 3 : Absolute Limits Filter
# Flag = 4 : Rolling MAD Filter
# Flag = 5 : Diagnostic filter

nee_plot_week = ggplot(data = df)+geom_hline(yintercept = 0)+
  geom_point(data = subset(df, !is.na(co2_flux.flag)),
    aes(TIMESTAMP,co2_flux,color = co2_flux.flag))+
  geom_point(aes(TIMESTAMP,co2_flux.c),col='black')+
  scale_y_continuous(limits=c(-12,8))+
    labs(
    x = NULL,
    y = expression(paste( ~CO[2], ~"Flux (umol m",""^"-2","s",""^"-1",")"))
  ) +
  scale_x_datetime(limits = as.POSIXct(c("2025-11-02", "2025-11-08")))+
scale_color_manual(values = color_map, name = "QC CO2 Flux")
nee_plot_week

```


## Methane

Methane is cleaned with absolute limits of -0.15 & 0.28, and a limit of 8 MADs away from the mean over a 7 day window

#### Year-to-Date Methane
```{r, warning=FALSE, echo=FALSE}

# Flag = 0, 1, 2 : EP Flag
# Flag = 3 : Absolute Limits Filter
# Flag = 4 : Rolling MAD Filter
# Flag = 5 : Diagnostic filter

ch4_plot_year = ggplot(data = df)+geom_hline(yintercept = 0)+
  geom_point(data = subset(df, !is.na(ch4_flux.flag)),
    aes(TIMESTAMP,ch4_flux,color = ch4_flux.flag))+
  geom_point(aes(TIMESTAMP,ch4_flux.c),col='black')+
  scale_y_continuous(limits=c(-0.1,0.33))+
  labs(
    x = NULL,
    y = expression(paste( ~CH[4], ~"Flux (umol m",""^"-2","s",""^"-1",")"))
  ) +
  scale_x_datetime(limits = as.POSIXct(c("2025-05-01", "2025-12-16")))+
scale_color_manual(values = color_map, name = "QC CH4 Flux")
ch4_plot_year

```


#### Previous Month Methane
```{r, warning=FALSE, echo=FALSE}

# Flag = 0, 1, 2 : EP Flag
# Flag = 3 : Absolute Limits Filter
# Flag = 4 : Rolling MAD Filter
# Flag = 5 : Diagnostic filter
ch4_plot_month = ggplot(data = df)+geom_hline(yintercept = 0)+
  geom_point(data = subset(df, !is.na(ch4_flux.flag)),
    aes(TIMESTAMP,ch4_flux,color = ch4_flux.flag))+
  geom_point(aes(TIMESTAMP,ch4_flux.c),col='black')+
  scale_y_continuous(limits=c(-0.08,0.08))+  
  labs(
    x = NULL,
    y = expression(paste( ~CH[4], ~"Flux (umol m",""^"-2","s",""^"-1",")"))
  ) +
  scale_x_datetime(limits = as.POSIXct(c("2025-10-01", "2025-10-31")))+
scale_color_manual(values = color_map, name = "QC CH4 Flux")
ch4_plot_month


ch4_plot_month = ggplot(data = df)+geom_hline(yintercept = 0)+
  geom_point(data = subset(df, !is.na(ch4_flux.flag)),
    aes(TIMESTAMP,ch4_flux,color = ch4_flux.flag))+
  geom_point(aes(TIMESTAMP,ch4_flux.c),col='black')+
  scale_y_continuous(limits=c(-0.05,0.051))+  
  labs(
    x = NULL,
    y = expression(paste( ~CH[4], ~"Flux (umol m",""^"-2","s",""^"-1",")"))
  ) +
  scale_x_datetime(limits = as.POSIXct(c("2025-11-01", "2025-11-30")))+
scale_color_manual(values = color_map, name = "QC CH4 Flux")
ch4_plot_month



```


#### Week zoom-in Methane
```{r, warning=FALSE, echo=FALSE}

# Flag = 0, 1, 2 : EP Flag
# Flag = 3 : Absolute Limits Filter
# Flag = 4 : Rolling MAD Filter
# Flag = 5 : Diagnostic filter

ch4_plot_week = ggplot(data = df)+geom_hline(yintercept = 0)+
  geom_point(data = subset(df, !is.na(ch4_flux.flag)),
    aes(TIMESTAMP,ch4_flux,color = ch4_flux.flag))+
  geom_point(aes(TIMESTAMP,ch4_flux.c),col='black')+
  scale_y_continuous(limits=c(-0.1,0.0833))+
  labs(
    x = NULL,
    y = expression(paste( ~CH[4], ~"Flux (umol m",""^"-2","s",""^"-1",")"))
  ) +
  scale_x_datetime(limits = as.POSIXct(c("2025-10-18", "2025-10-26")))+
scale_color_manual(values = color_map, name = "QC CH4 Flux")
ch4_plot_week

ch4_plot_week = ggplot(data = df)+geom_hline(yintercept = 0)+
  geom_point(data = subset(df, !is.na(ch4_flux.flag)),
    aes(TIMESTAMP,ch4_flux,color = ch4_flux.flag))+
  geom_point(aes(TIMESTAMP,ch4_flux.c),col='black')+
  scale_y_continuous(limits=c(-0.1,0.0833))+
  labs(
    x = NULL,
    y = expression(paste( ~CH[4], ~"Flux (umol m",""^"-2","s",""^"-1",")"))
  ) +
  scale_x_datetime(limits = as.POSIXct(c("2025-11-18", "2025-11-20")))+
scale_color_manual(values = color_map, name = "QC CH4 Flux")
ch4_plot_week

```



# Energy Balance Plots

#### Full Year-to-date
```{r, warning=FALSE, echo=FALSE}

df$met = ((df$LWIN_6_14_1_1_1.c + df$SWIN_6_10_1_1_1.c) -
         (df$LWOUT_6_15_1_1_1.c + df$SWOUT_6_11_1_1_1.c)) -
        ((df$SHF_6_37_1_1_1.c + df$SHF_6_37_2_1_1.c)/2)
df$flux = df$H.c + df$LE.c

# Fit linear model
mod = lm(flux ~ met, data = df)
summary_mod = summary(mod)

# Extract slope and R²
slope = coef(mod)["met"]
r2 = summary_mod$r.squared
cat("Slope:", slope, "\nR²:", r2, "\n")

# Define axis limits
x_lim = c(-200,500)
y_lim = c(-200,500)


# Plot
eb_ytd <- ggplot(df, aes(x = met, y = flux)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", color = "blue", se = FALSE) +
  geom_abline(slope = 1, intercept = 0,
               linetype = "dashed", color = "red") +
  geom_hline(yintercept = 0, linetype = "solid", color = "black") +
  geom_vline(xintercept = 0, linetype = "solid", color = "black") +
  coord_fixed(ratio = 1, xlim = x_lim, ylim = y_lim) +
  labs(
    x = expression("Rn - G  (Wm"^-2*")"),
    y = expression("H + LE  (Wm"^-2*")"),
    title = expression("Full Year EB")
  ) +
  annotate(
    "text",
    x = Inf, y = -Inf,
    label = paste0("Slope = ", round(slope, 3), "\nR² = ", round(r2, 3)),
    hjust = 1.1, vjust = -0.5, size = 4
  ) +
  theme_bw()
eb_ytd
```



#### Previous Month
```{r, warning=FALSE, echo=FALSE}

df_month$met = ((df_month$LWIN_6_14_1_1_1.c + df_month$SWIN_6_10_1_1_1.c) -
         (df_month$LWOUT_6_15_1_1_1.c + df_month$SWOUT_6_11_1_1_1.c)) -
        ((df_month$SHF_6_37_1_1_1.c + df_month$SHF_6_37_2_1_1.c)/2)
df_month$flux = df_month$H.c + df_month$LE.c

# Fit linear model
mod = lm(flux ~ met, data = df_month)
summary_mod = summary(mod)

# Extract slope and R²
slope = coef(mod)["met"]
r2 = summary_mod$r.squared
cat("Slope:", slope, "\nR²:", r2, "\n")

# Define axis limits
x_lim = c(-200,500)
y_lim = c(-200,500)

# Plot
eb_month <- ggplot(df_month, aes(x = met, y = flux)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", color = "blue", se = FALSE) +
  geom_abline(slope = 1, intercept = 0,
               linetype = "dashed", color = "red") +
  geom_hline(yintercept = 0, linetype = "solid", color = "black") +
  geom_vline(xintercept = 0, linetype = "solid", color = "black") +
  coord_fixed(ratio = 1, xlim = x_lim, ylim = y_lim) +
  labs(
    x = expression("Rn - G  (Wm"^-2*")"),
    y = expression("H + LE  (Wm"^-2*")"),
    title = expression("Previous Month EB")
  ) +
  annotate(
    "text",
    x = Inf, y = -Inf,
    label = paste0("Slope = ", round(slope, 3), "\nR² = ", round(r2, 3)),
    hjust = 1.1, vjust = -0.5, size = 4
  ) +
  theme_bw()
eb_month

```
```{r, warning=FALSE}
# Scatter: CO2 vs TA
ggplot(subset(df, !is.na(co2_flux.c) & !is.na(TA_2_1_1_1_1.c)),
       aes(x = TA_2_1_1_1_1.c, y = co2_flux.c, color = TA_2_1_1_1_1.c)) +
  geom_point(alpha = 0.7) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "black") +   # vertical line at TA = 0
  geom_hline(yintercept = 0, linetype = "dashed", color = "black") +   # horizontal line at flux = 0
  scale_color_viridis_c(option = "plasma", name = "Temp (°C)") +
  labs(
    x = "Air Temperature (°C)",
    y = expression(CO[2]~"Flux (µmol/m²/s)")
  ) +
  theme_bw()


# Scatter: CH4 vs TA
ggplot(subset(df, !is.na(ch4_flux.c) & !is.na(TA_2_1_1_1_1.c)),
       aes(x = TA_2_1_1_1_1.c, y = ch4_flux.c, color = TA_2_1_1_1_1.c)) +
  geom_point(alpha = 0.7) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "black") +   # vertical line at TA = 0
  geom_hline(yintercept = 0, linetype = "dashed", color = "black") +   # horizontal line at flux = 0
  scale_color_viridis_c(option = "plasma", name = "Temp (°C)") +
  labs(
    x = "Air Temperature (°C)",
    y = expression(CH[4]~"Flux (µmol/m²/s)")
  ) +
  theme_bw()


```
```{r, warning=FALSE}
ggplot(subset(df, !is.na(co2_flux.c) & !is.na(TA_2_1_1_1_1.c)),
       aes(x = TIMESTAMP, y = co2_flux.c, color = TA_2_1_1_1_1.c)) +
  geom_point(alpha = 0.7, size = 1.5) +
  scale_color_viridis_c(option = "plasma", name = "Temp (°C)") +
  geom_hline(yintercept = 0, linetype = "dashed", color = "black") +
  labs(x = "Time", y = expression(CO[2]~"Flux (µmol/m²/s)")) +
  theme_bw() +
  scale_x_datetime(date_labels = "%b %d", date_breaks = "7 days")

ggplot(subset(df, !is.na(ch4_flux.c) & !is.na(TA_2_1_1_1_1.c)),
       aes(x = TIMESTAMP, y = ch4_flux.c, color = TA_2_1_1_1_1.c)) +
  geom_point(alpha = 0.7, size = 1.5) +
  scale_color_viridis_c(option = "plasma", name = "Temp (°C)") +
  geom_hline(yintercept = 0, linetype = "dashed", color = "black") +
  labs(x = "Time", y = expression(CH[4]~"Flux (µmol/m²/s)")) +
  theme_bw() +
  scale_x_datetime(date_labels = "%b %d", date_breaks = "7 days")

```
```{r, warning=FALSE}

# Bin directions (every 30°)
df_wind_hour <- df %>%
  filter(!is.na(wind_dir) & !is.na(WS_16_33_1_1_1)) %>%
  mutate(
    hour = hour(TIMESTAMP),
    wind_dir_bin = cut(wind_dir, breaks = seq(0, 360, by = 30), include.lowest = TRUE)
  )

# Summarize: average wind speed by hour and direction
df_summary <- df_wind_hour %>%
  group_by(hour, wind_dir_bin) %>%
  summarise(mean_ws = mean(WS_16_33_1_1_1), .groups = "drop")

# Convert bin to mid-angle for plotting
df_summary <- df_summary %>%
  mutate(
    wind_rad = as.numeric(sub("\\((.+),.*", "\\1", wind_dir_bin)) * pi / 180
  )

ggplot(df_wind_hour, aes(x = hour, y = wind_dir, color = WS_16_33_1_1_1)) +
  geom_point(alpha = 0.7, size = 1.5) +
  scale_y_continuous(breaks = seq(0, 360, by = 45)) +
  scale_color_viridis_c(name = "Wind Speed (m/s)") +
  labs(x = "Hour of Day", y = "Wind Direction (°)") +
  theme_minimal()

```


```{r, warning=FALSE}



# Wind data
df_wind <- df %>%
  filter(!is.na(wind_dir) & !is.na(WS_16_33_1_1_1)) %>%
  mutate(wind_bin = cut(wind_dir, breaks = seq(0,360,22.5), include.lowest=TRUE, right=FALSE)) %>%
  group_by(wind_bin) %>%
  summarise(WS_mean = mean(WS_16_33_1_1_1, na.rm=TRUE))

ggplot(df_wind, aes(x = wind_bin, y = WS_mean)) +
  geom_col(fill="grey70", color="black", width=1) +
  coord_polar() +
  scale_x_discrete(labels = seq(0,337.5,22.5)) +
  labs(title="Wind", x="", y="") +
  theme_minimal() +
  theme(axis.text.y = element_blank())

# CO₂ data
df_co2_wr <- df %>%
  filter(!is.na(wind_dir) & !is.na(co2_flux.c)) %>%
  mutate(wind_bin = cut(wind_dir, breaks = seq(0,360,22.5), include.lowest=TRUE, right=FALSE)) %>%
  group_by(wind_bin) %>%
  summarise(
    count = n(),
    flux_mean = mean(co2_flux.c, na.rm=TRUE)
  )

ggplot(df_co2_wr, aes(x = wind_bin, y = count, fill = flux_mean)) +
  geom_col(color="black", width=1) +
  coord_polar() +
  scale_fill_gradient(low="blue", high="green", name=expression(CO[2]~"Flux")) +
  scale_x_discrete(labels = seq(0,337.5,22.5)) +
  labs(title="Carbon dioxide Flux Windrose", x="", y="") +
  theme_minimal() +
  theme(axis.text.y = element_blank())

# CH₄ data
df_ch4_wr <- df %>%
  filter(!is.na(wind_dir) & !is.na(ch4_flux.c)) %>%
  mutate(wind_bin = cut(wind_dir, breaks = seq(0,360,22.5), include.lowest=TRUE, right=FALSE)) %>%
  group_by(wind_bin) %>%
  summarise(
    count = n(),
    flux_mean = mean(ch4_flux.c, na.rm=TRUE)
  )

ggplot(df_ch4_wr, aes(x = wind_bin, y = count, fill = flux_mean)) +
  geom_col(color="black", width=1) +
  coord_polar() +
  scale_fill_gradient(low="blue", high="green", name=expression(CH[4]~"Flux")) +
  scale_x_discrete(labels = seq(0,337.5,22.5)) +
  labs(title="methane Flux Windrose", x="", y="") +
  theme_minimal() +
  theme(axis.text.y = element_blank())



```




```{r, warning=FALSE}

Uthreshold <- 0.065 # import the set U* threshold for specific site

# Fit linear model
mod_utke <- lm(TKE ~ u., data = df)
summary_mod_utke <- summary(mod_utke)

# Extract slope and R²
slope_utke <- coef(mod_utke)["u."]
r2_utke <- summary_mod_utke$r.squared

cat("Slope:", slope_utke, "\nR²:", r2_utke, "\n")

df_clean <- subset(df, !is.na(u.) & !is.na(TKE))
df_clean$thresh <- df_clean$u. < Uthreshold  # TRUE = red

# Optional fixed axis limits
x_lim_utke <- c(0, 1)
y_lim_utke <- c(0, 10)

scatter_utke <- ggplot(df_clean, aes(x = u., y = TKE)) +
  geom_point(aes(color = thresh), alpha = 0.5, size = 1.8) +
  scale_color_manual(values = c("FALSE" = "darkblue", "TRUE" = "red"),
                  
                     name = paste0("u* <", Uthreshold)) +
  geom_smooth(method = "lm", color = "black", se = FALSE, linewidth = 0.8) +
  geom_vline(xintercept = Uthreshold, linetype = "dashed", color = "red") +
  geom_hline(yintercept = 0, color = "black") +
  geom_vline(xintercept = 0, color = "black") +
  scale_x_continuous(limits = x_lim_utke) +
  scale_y_continuous(limits = y_lim_utke) +
  labs(
    x = expression(u["*"] ~ "(m/s)"),
    y = expression("TKE (m"^2*"/s"^2*")"),
    title = "u* vs TKE"
  ) +
  annotate("text", x = Inf, y = Inf,
           label = paste0("Slope = ", round(slope_utke, 3),
                          "\nR² = ", round(r2_utke, 3)),
           hjust = 1.1, vjust = 1.1, size = 4) +
  theme_bw(base_size = 12) +
  theme(
    plot.title = element_text(face = "bold"),
    panel.grid.minor = element_blank()
  )

scatter_utke


```


```{r, warning=F}

# Standardize variables (z-score)
df$u_std  <- (df$u.  - median(df$u.,  na.rm=TRUE)) / sd(df$u.,  na.rm=TRUE)
df$TKE_std <- (df$TKE - median(df$TKE, na.rm=TRUE)) / sd(df$TKE, na.rm=TRUE)

# Extract hour and month
df$hour  <- as.numeric(format(df$TIMESTAMP, "%H"))
df$month <- as.numeric(format(df$TIMESTAMP, "%m"))

# Compute diurnal median and SD
diel_utke <- df %>%
  group_by(hour, month) %>%
  summarise(
    u_fn1   = median(u_std, na.rm=TRUE),
    u_fn2   = sd(u_std, na.rm=TRUE),
    TKE_fn1 = median(TKE_std, na.rm=TRUE),
    TKE_fn2 = sd(TKE_std, na.rm=TRUE)
  ) %>%
  ungroup() %>%
  subset(!is.na(month))

# Diurnal plot
diurnal_utke_plot <- ggplot(diel_utke, aes(x=hour)) +
  geom_line(aes(y=u_fn1, color="u*"), linewidth=1) +
  geom_ribbon(aes(ymin=u_fn1-u_fn2, ymax=u_fn1+u_fn2, fill="u*"), alpha=0.2) +
  geom_line(aes(y=TKE_fn1, color="TKE"), linewidth=1) +
  geom_ribbon(aes(ymin=TKE_fn1-TKE_fn2, ymax=TKE_fn1+TKE_fn2, fill="TKE"), alpha=0.2) +
  facet_wrap(~month) +
  scale_color_manual(values=c("u*"="blue", "TKE"="red")) +
  scale_fill_manual(values=c("u*"="blue", "TKE"="red")) +
  labs(x="Hour", y="Standardized value (z-score)", title="Diurnal u* and TKE") +
  theme_bw()

diurnal_utke_plot


```


### rpot vs swin
```{r}
# Flag misalignment: SWIN outside RPOT
misaligned <- df$SWIN_6_10_1_1_1 > df$rpot | df$SWIN_6_10_1_1_1 < 0  # or just > RPOT if negative not possible

ggplot(df, aes(x = TIMESTAMP)) +
  geom_line(aes(y = rpot), color = "blue", size = 0.8) +
  geom_point(
    data = subset(df, !is.na(SWIN_6_10_1_1_1)),          # exclude NAs
    aes(
      y = SWIN_6_10_1_1_1,
      color = SWIN_6_10_1_1_1 > rpot                     # TRUE = misaligned
    ),
    alpha = 0.8,
    size = 1.2
  ) +
  scale_color_manual(
    values = c("TRUE" = "red", "FALSE" = "black"),
    labels = c("TRUE" = "Misaligned", "FALSE" = "OK")
  ) +
  labs(
    x = "Time",
    y = "Radiation (W/m²)",
    color = ""
  ) +
 scale_x_datetime(
    date_breaks = "1 month",
    date_labels = "%b"
  ) +
  theme_minimal()


```
```{r, warning=FALSE}

ggplot(df, aes(x = TIMESTAMP)) +
  geom_line(aes(y = rpot), color = "blue") +                        # RPOT line
  geom_point(aes(y = SWIN_6_10_1_1_1), color = "black") +          # all SWIN points
  geom_point(data = subset(df, SWIN_6_10_1_1_1.c > rpot),            # only misaligned
             aes(y = SWIN_6_10_1_1_1.c), color = "red", size = .5) +
  theme_minimal() +
  coord_cartesian(xlim = as.POSIXct(c("2025-10-01 00:00", "2025-10-30 23:59")))


```

```{r, warning=FALSE}


ggplot(df, aes(x = TIMESTAMP)) +
  geom_line(aes(y = rpot), color = "blue") +                        # RPOT line
  geom_point(aes(y = SWIN_6_10_1_1_1), color = "black") +          # all SWIN points
  geom_point(data = subset(df, SWIN_6_10_1_1_1.c > rpot),            # only misaligned
             aes(y = SWIN_6_10_1_1_1.c), color = "red", size = .5) +
  theme_minimal() +
  coord_cartesian(xlim = as.POSIXct(c("2025-10-01 00:00", "2025-10-14 23:59")))



```

#### Full Year-to-Date
```{r, warning=FALSE, echo=FALSE}
ggplot(data = df)+
  geom_point(aes(x = rpot, y = SWIN_6_10_1_1_1, color = radflag))+
  geom_abline(yint = 0, slope = 1, color = "red")+
  scale_x_continuous(limits = c(0, 1000))+
  scale_y_continuous(limits = c(0, 1000))

```


#### Previous Month
```{r, warning=FALSE, echo=FALSE}
# CO2 vs SWIN
ggplot(subset(df, !is.na(co2_flux.c) & !is.na(SWIN_6_10_1_1_1.c)),
       aes(x = SWIN_6_10_1_1_1.c, y = co2_flux.c, color = SWIN_6_10_1_1_1.c)) +
  geom_point(alpha = 0.7) +
  geom_vline(xintercept = 0, linetype="dashed", color="black") +
  geom_hline(yintercept = 0, linetype="dashed", color="black") +
  scale_color_viridis_c(option="plasma", name="SWIN") +
  labs(x="SWIN", y=expression(CO[2]~"Flux (µmol/m²/s)"), title="CO2 Flux vs SWIN") +
  theme_bw()

# CO2 vs SWOUT
ggplot(subset(df, !is.na(co2_flux.c) & !is.na(SWOUT_6_11_1_1_1.c)),
       aes(x = SWOUT_6_11_1_1_1.c, y = co2_flux.c, color = SWOUT_6_11_1_1_1.c)) +
  geom_point(alpha = 0.7) +
  geom_vline(xintercept = 0, linetype="dashed", color="black") +
  geom_hline(yintercept = 0, linetype="dashed", color="black") +
  scale_color_viridis_c(option="plasma", name="SWOUT") +
  labs(x="SWOUT", y=expression(CO[2]~"Flux (µmol/m²/s)"), title="CO2 Flux vs SWOUT") +
  theme_bw()

# CO2 vs LWIN
ggplot(subset(df, !is.na(co2_flux.c) & !is.na(LWIN_6_14_1_1_1.c)),
       aes(x = LWIN_6_14_1_1_1.c, y = co2_flux.c, color = LWIN_6_14_1_1_1.c)) +
  geom_point(alpha = 0.7) +
  geom_vline(xintercept = 0, linetype="dashed", color="black") +
  geom_hline(yintercept = 0, linetype="dashed", color="black") +
  scale_color_viridis_c(option="plasma", name="LWIN") +
  labs(x="LWIN", y=expression(CO[2]~"Flux (µmol/m²/s)"), title="CO2 Flux vs LWIN") +
  theme_bw()

# CO2 vs LWOUT
ggplot(subset(df, !is.na(co2_flux.c) & !is.na(LWOUT_6_15_1_1_1.c)),
       aes(x = LWOUT_6_15_1_1_1.c, y = co2_flux.c, color = LWOUT_6_15_1_1_1.c)) +
  geom_point(alpha = 0.7) +
  geom_vline(xintercept = 0, linetype="dashed", color="black") +
  geom_hline(yintercept = 0, linetype="dashed", color="black") +
  scale_color_viridis_c(option="plasma", name="LWOUT") +
  labs(x="LWOUT", y=expression(CO[2]~"Flux (µmol/m²/s)"), title="CO2 Flux vs LWOUT") +
  theme_bw()

# CO2 vs SHF1
ggplot(subset(df, !is.na(co2_flux.c) & !is.na(SHF_6_37_1_1_1.c)),
       aes(x = SHF_6_37_1_1_1.c, y = co2_flux.c, color = SHF_6_37_1_1_1.c)) +
  geom_point(alpha = 0.7) +
  geom_vline(xintercept = 0, linetype="dashed", color="black") +
  geom_hline(yintercept = 0, linetype="dashed", color="black") +
  scale_color_viridis_c(option="plasma", name="SHF1") +
  labs(x="SHF1", y=expression(CO[2]~"Flux (µmol/m²/s)"), title="CO2 Flux vs SHF1") +
  theme_bw()

# CO2 vs SHF2
ggplot(subset(df, !is.na(co2_flux.c) & !is.na(SHF_6_37_2_1_1_1.c)),
       aes(x = SHF_6_37_2_1_1_1.c, y = co2_flux.c, color = SHF_6_37_2_1_1_1.c)) +
  geom_point(alpha = 0.7) +
  geom_vline(xintercept = 0, linetype="dashed", color="black") +
  geom_hline(yintercept = 0, linetype="dashed", color="black") +
  scale_color_viridis_c(option="plasma", name="SHF2") +
  labs(x="SHF2", y=expression(CO[2]~"Flux (µmol/m²/s)"), title="CO2 Flux vs SHF2") +
  theme_bw()


```

```{r}


# CH4 vs SWIN
ggplot(subset(df, !is.na(ch4_flux.c) & !is.na(SWIN_6_10_1_1_1.c)),
       aes(x = SWIN_6_10_1_1_1.c, y = ch4_flux.c, color = SWIN_6_10_1_1_1.c)) +
  geom_point(alpha = 0.7) +
  geom_vline(xintercept = 0, linetype="dashed", color="black") +
  geom_hline(yintercept = 0, linetype="dashed", color="black") +
  scale_color_viridis_c(option="plasma", name="SWIN") +
  labs(x="SWIN", y=expression(CH[4]~"Flux (µmol/m²/s)"), title="CH4 Flux vs SWIN") +
  theme_bw()

# CH4 vs SWOUT
ggplot(subset(df, !is.na(ch4_flux.c) & !is.na(SWOUT_6_11_1_1_1.c)),
       aes(x = SWOUT_6_11_1_1_1.c, y = ch4_flux.c, color = SWOUT_6_11_1_1_1.c)) +
  geom_point(alpha = 0.7) +
  geom_vline(xintercept = 0, linetype="dashed", color="black") +
  geom_hline(yintercept = 0, linetype="dashed", color="black") +
  scale_color_viridis_c(option="plasma", name="SWOUT") +
  labs(x="SWOUT", y=expression(CH[4]~"Flux (µmol/m²/s)"), title="CH4 Flux vs SWOUT") +
  theme_bw()

# CH4 vs LWIN
ggplot(subset(df, !is.na(ch4_flux.c) & !is.na(LWIN_6_14_1_1_1.c)),
       aes(x = LWIN_6_14_1_1_1.c, y = ch4_flux.c, color = LWIN_6_14_1_1_1.c)) +
  geom_point(alpha = 0.7) +
  geom_vline(xintercept = 0, linetype="dashed", color="black") +
  geom_hline(yintercept = 0, linetype="dashed", color="black") +
  scale_color_viridis_c(option="plasma", name="LWIN") +
  labs(x="LWIN", y=expression(CH[4]~"Flux (µmol/m²/s)"), title="CH4 Flux vs LWIN") +
  theme_bw()

# CH4 vs LWOUT
ggplot(subset(df, !is.na(ch4_flux.c) & !is.na(LWOUT_6_15_1_1_1.c)),
       aes(x = LWOUT_6_15_1_1_1.c, y = ch4_flux.c, color = LWOUT_6_15_1_1_1.c)) +
  geom_point(alpha = 0.7) +
  geom_vline(xintercept = 0, linetype="dashed", color="black") +
  geom_hline(yintercept = 0, linetype="dashed", color="black") +
  scale_color_viridis_c(option="plasma", name="LWOUT") +
  labs(x="LWOUT", y=expression(CH[4]~"Flux (µmol/m²/s)"), title="CH4 Flux vs LWOUT") +
  theme_bw()

# CH4 vs SHF1
ggplot(subset(df, !is.na(ch4_flux.c) & !is.na(SHF_6_37_1_1_1.c)),
       aes(x = SHF_6_37_1_1_1.c, y = ch4_flux.c, color = SHF_6_37_1_1_1.c)) +
  geom_point(alpha = 0.7) +
  geom_vline(xintercept = 0, linetype="dashed", color="black") +
  geom_hline(yintercept = 0, linetype="dashed", color="black") +
  scale_color_viridis_c(option="plasma", name="SHF1") +
  labs(x="SHF1", y=expression(CH[4]~"Flux (µmol/m²/s)"), title="CH4 Flux vs SHF1") +
  theme_bw()

# CH4 vs SHF2
ggplot(subset(df, !is.na(ch4_flux.c) & !is.na(SHF_6_37_2_1_1_1.c)),
       aes(x = SHF_6_37_2_1_1_1.c, y = ch4_flux.c, color = SHF_6_37_2_1_1_1.c)) +
  geom_point(alpha = 0.7) +
  geom_vline(xintercept = 0, linetype="dashed", color="black") +
  geom_hline(yintercept = 0, linetype="dashed", color="black") +
  scale_color_viridis_c(option="plasma", name="SHF2") +
  labs(x="SHF2", y=expression(CH[4]~"Flux (µmol/m²/s)"), title="CH4 Flux vs SHF2") +
  theme_bw()


```
```{r, warning=FALSE}
# SWIN
ggplot(subset(df, !is.na(co2_flux.c) & !is.na(SWIN_6_10_1_1_1.c)),
       aes(x = TIMESTAMP, y = co2_flux.c, color = SWIN_6_10_1_1_1.c)) +
  geom_point(alpha = 0.7, size = 1.5) +
  scale_color_viridis_c(option = "plasma", name = "SWIN") +
  geom_hline(yintercept = 0, linetype="dashed", color="black") +
  labs(x="Time", y=expression(CO[2]~"Flux (µmol/m²/s)"), title="CO2 Flux vs SWIN") +
  theme_bw() +
  scale_x_datetime(date_labels="%b %d", date_breaks="7 days")

# SWOUT
ggplot(subset(df, !is.na(co2_flux.c) & !is.na(SWOUT_6_11_1_1_1.c)),
       aes(x = TIMESTAMP, y = co2_flux.c, color = SWOUT_6_11_1_1_1.c)) +
  geom_point(alpha = 0.7, size = 1.5) +
  scale_color_viridis_c(option = "plasma", name = "SWOUT") +
  geom_hline(yintercept = 0, linetype="dashed", color="black") +
  labs(x="Time", y=expression(CO[2]~"Flux (µmol/m²/s)"), title="CO2 Flux vs SWOUT") +
  theme_bw() +
  scale_x_datetime(date_labels="%b %d", date_breaks="7 days")

# LWIN
ggplot(subset(df, !is.na(co2_flux.c) & !is.na(LWIN_6_14_1_1_1.c)),
       aes(x = TIMESTAMP, y = co2_flux.c, color = LWIN_6_14_1_1_1.c)) +
  geom_point(alpha = 0.7, size = 1.5) +
  scale_color_viridis_c(option = "plasma", name = "LWIN") +
  geom_hline(yintercept = 0, linetype="dashed", color="black") +
  labs(x="Time", y=expression(CO[2]~"Flux (µmol/m²/s)"), title="CO2 Flux vs LWIN") +
  theme_bw() +
  scale_x_datetime(date_labels="%b %d", date_breaks="7 days")

# LWOUT
ggplot(subset(df, !is.na(co2_flux.c) & !is.na(LWOUT_6_15_1_1_1.c)),
       aes(x = TIMESTAMP, y = co2_flux.c, color = LWOUT_6_15_1_1_1.c)) +
  geom_point(alpha = 0.7, size = 1.5) +
  scale_color_viridis_c(option = "plasma", name = "LWOUT") +
  geom_hline(yintercept = 0, linetype="dashed", color="black") +
  labs(x="Time", y=expression(CO[2]~"Flux (µmol/m²/s)"), title="CO2 Flux vs LWOUT") +
  theme_bw() +
  scale_x_datetime(date_labels="%b %d", date_breaks="7 days")

# SHF1
ggplot(subset(df, !is.na(co2_flux.c) & !is.na(SHF_6_37_1_1_1.c)),
       aes(x = TIMESTAMP, y = co2_flux.c, color = SHF_6_37_1_1_1.c)) +
  geom_point(alpha = 0.7, size = 1.5) +
  scale_color_viridis_c(option = "plasma", name = "SHF1") +
  geom_hline(yintercept = 0, linetype="dashed", color="black") +
  labs(x="Time", y=expression(CO[2]~"Flux (µmol/m²/s)"), title="CO2 Flux vs SHF1") +
  theme_bw() +
  scale_x_datetime(date_labels="%b %d", date_breaks="7 days")

# SHF2
ggplot(subset(df, !is.na(co2_flux.c) & !is.na(SHF_6_37_2_1_1_1.c)),
       aes(x = TIMESTAMP, y = co2_flux.c, color = SHF_6_37_2_1_1_1.c)) +
  geom_point(alpha = 0.7, size = 1.5) +
  scale_color_viridis_c(option = "plasma", name = "SHF2") +
  geom_hline(yintercept = 0, linetype="dashed", color="black") +
  labs(x="Time", y=expression(CO[2]~"Flux (µmol/m²/s)"), title="CO2 Flux vs SHF2") +
  theme_bw() +
  scale_x_datetime(date_labels="%b %d", date_breaks="7 days")

```

```{r, warning=FALSE}
# CH4 vs SWIN
ggplot(subset(df, !is.na(ch4_flux.c) & !is.na(SWIN_6_10_1_1_1.c)),
       aes(x = TIMESTAMP, y = ch4_flux.c, color = SWIN_6_10_1_1_1.c)) +
  geom_point(alpha = 0.7, size = 1.5) +
  scale_color_viridis_c(option = "plasma", name = "SWIN") +
  geom_hline(yintercept = 0, linetype = "dashed", color = "black") +
  labs(x = "Time", y = expression(CH[4]~"Flux (µmol/m²/s)"), title = "CH4 Flux vs SWIN") +
  theme_bw() +
  scale_x_datetime(date_labels = "%b %d", date_breaks = "7 days")

# CH4 vs SWOUT
ggplot(subset(df, !is.na(ch4_flux.c) & !is.na(SWOUT_6_11_1_1_1.c)),
       aes(x = TIMESTAMP, y = ch4_flux.c, color = SWOUT_6_11_1_1_1.c)) +
  geom_point(alpha = 0.7, size = 1.5) +
  scale_color_viridis_c(option = "plasma", name = "SWOUT") +
  geom_hline(yintercept = 0, linetype = "dashed", color = "black") +
  labs(x = "Time", y = expression(CH[4]~"Flux (µmol/m²/s)"), title = "CH4 Flux vs SWOUT") +
  theme_bw() +
  scale_x_datetime(date_labels = "%b %d", date_breaks = "7 days")
# CH4 vs LWIN
ggplot(subset(df, !is.na(ch4_flux.c) & !is.na(LWIN_6_14_1_1_1.c)),
       aes(x = TIMESTAMP, y = ch4_flux.c, color = LWIN_6_14_1_1_1.c)) +
  geom_point(alpha = 0.7, size = 1.5) +
  scale_color_viridis_c(option = "plasma", name = "LWIN") +
  geom_hline(yintercept = 0, linetype = "dashed", color = "black") +
  labs(x = "Time", y = expression(CH[4]~"Flux (µmol/m²/s)"), title = "CH4 Flux vs LWIN") +
  theme_bw() +
  scale_x_datetime(date_labels = "%b %d", date_breaks = "7 days")

# CH4 vs LWOUT
ggplot(subset(df, !is.na(ch4_flux.c) & !is.na(LWOUT_6_15_1_1_1.c)),
       aes(x = TIMESTAMP, y = ch4_flux.c, color = LWOUT_6_15_1_1_1.c)) +
  geom_point(alpha = 0.7, size = 1.5) +
  scale_color_viridis_c(option = "plasma", name = "LWOUT") +
  geom_hline(yintercept = 0, linetype = "dashed", color = "black") +
  labs(x = "Time", y = expression(CH[4]~"Flux (µmol/m²/s)"), title = "CH4 Flux vs LWOUT") +
  theme_bw() +
  scale_x_datetime(date_labels = "%b %d", date_breaks = "7 days")
# CH4 vs SHF1
ggplot(subset(df, !is.na(ch4_flux.c) & !is.na(SHF_6_37_1_1_1.c)),
       aes(x = TIMESTAMP, y = ch4_flux.c, color = SHF_6_37_1_1_1.c)) +
  geom_point(alpha = 0.7, size = 1.5) +
  scale_color_viridis_c(option = "plasma", name = "SHF1") +
  geom_hline(yintercept = 0, linetype = "dashed", color = "black") +
  labs(x = "Time", y = expression(CH[4]~"Flux (µmol/m²/s)"), title = "CH4 Flux vs SHF1") +
  theme_bw() +
  scale_x_datetime(date_labels = "%b %d", date_breaks = "7 days")

# CH4 vs SHF2
ggplot(subset(df, !is.na(ch4_flux.c) & !is.na(SHF_6_37_2_1_1_1.c)),
       aes(x = TIMESTAMP, y = ch4_flux.c, color = SHF_6_37_2_1_1_1.c)) +
  geom_point(alpha = 0.7, size = 1.5) +
  scale_color_viridis_c(option = "plasma", name = "SHF2") +
  geom_hline(yintercept = 0, linetype = "dashed", color = "black") +
  labs(x = "Time", y = expression(CH[4]~"Flux (µmol/m²/s)"), title = "CH4 Flux vs SHF2") +
  theme_bw() +
  scale_x_datetime(date_labels = "%b %d", date_breaks = "7 days")

```

# Diurnal Fluxes

```{r, warning=FALSE, echo=FALSE}
# set hour and month vectors to be able to take the averages

df <- dplyr::filter(df, !df$TIMESTAMP < as.POSIXct("2025-05-01 00:00:00"))

df$hour = as.numeric(format(df$ts,'%H'))
df$month = as.numeric(format(df$ts,'%m'))

diel = df %>%
  group_by(hour,month) %>%
  select(co2_flux.c,ch4_flux.c,LE.c,H.c, RN_6_5_1_1_1.c, u., TKE, hour,month) %>%
  summarise_all(.funs = c(median,sd),na.rm=T)

diel = subset(diel,!is.na(diel$month))
```

#### NEE

```{r, warning=FALSE, echo=FALSE}
diurnal_nee <- ggplot(data = diel)+geom_hline(yintercept = 0)+
  geom_line(aes(hour,co2_flux.c_fn1),lty=2)+
  geom_ribbon(aes(x = hour,y = co2_flux.c_fn1,
                  ymax = co2_flux.c_fn1 + co2_flux.c_fn2,
                  ymin = co2_flux.c_fn1 - co2_flux.c_fn2),
              alpha= 0.5)+
  facet_wrap(~month)
diurnal_nee
```

#### CH4

```{r, warning=FALSE, echo=FALSE}
diurnal_ch4 <- ggplot(data = diel)+geom_hline(yintercept = 0)+
  geom_line(aes(hour,ch4_flux.c_fn1),lty=2)+
  geom_ribbon(aes(x = hour,y = ch4_flux.c_fn1,
                  ymax = ch4_flux.c_fn1 + ch4_flux.c_fn2,
                  ymin = ch4_flux.c_fn1 - ch4_flux.c_fn2),
              alpha= 0.5)+
  facet_wrap(~month)
diurnal_ch4

```


```{r, warning=FALSE}

ggplot(data = df) + 
  theme_bw() +
  geom_hline(yintercept = 0, linetype = "dashed", color = "black") +
  geom_line(aes(x = TIMESTAMP, y = TS_2_38_1_1_1.c, color = "8 cm")) +
  geom_line(aes(x = TIMESTAMP, y = TS_2_38_2_1_1.c, color = "18 cm")) +
  geom_line(aes(x = TIMESTAMP, y = TS_2_38_23_1_1.c, color = "28 cm")) +
  geom_line(aes(x = TIMESTAMP, y = TA_2_1_1_1_1.c, color = "Air")) +  # map inside aes()
  scale_color_manual(
    name = "Sensor Depth",
    values = c("8 cm" = "blue", "18 cm" = "green", "28 cm" = "gold3", "Air" = "red")
  ) +
  labs(
    x = "Time",
    y = "Temperature (°C)"
  )





```

```{r, warning=FALSE}


# Add month column
df <- df %>%
  mutate(month = as.numeric(format(TIMESTAMP, "%m")))

# List of unique months
months <- sort(unique(df$month))

# Loop to generate separate plots per month
plots <- list()

for (m in months) {
  df_month <- df %>% filter(month == m)
  
  p <- ggplot(df_month, aes(x = TIMESTAMP)) +
    geom_line(aes(y = TA_2_1_1_1_1.c, color = "Air Temp"), size = 0.8) +
    geom_line(aes(y = sonic_temperature - 273.15, color = "Sonic Temp"), size = 0.8) +
    geom_hline(yintercept = 0, linetype = "dashed", color = "black") +
    scale_color_manual(values = c("Air Temp" = "red", "Sonic Temp" = "blue")) +
    labs(
      x = "Time",
      y = "Temperature (°C)",
      color = "Sensor",
      title = paste("Month:", m)
    ) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1))
  
  plots[[paste0("temp_month_", m)]] <- p
}

# Example: print January (month 1)
plots$temp_month_1

# To view all plots sequentially
for (name in names(plots)) {
  print(plots[[name]])
  readline(prompt = paste("Displaying:", name, "- Press [Enter] for next plot."))
}

```



