---
title: "Data Quality Check"
author: "Dani Trangmoe"
date: "`r Sys.Date()`"
output:
  html_document: default
  pdf_document: default
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(error =  TRUE)
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = 'C:/Users/klynoe/Documents/toolik/R_outputs/flux_met_c/') #use this to set your directory
```


This file generates plots for the monthly data check meetings


```{r, include=FALSE}
# Load packages, cleaned data 

rm(list = ls())
Sys.setlocale("LC_CTYPE", "en_US.UTF-8")
library(data.table)
library(ggplot2)
library(cowplot)
library(openair)
library(plotrix)
library(signal)
library(svMisc)
library(zoo)
library(stringr)
library(plyr)
library(dplyr)
library(patchwork) # formats plots
library(bigleaf) # for radiation check
library(scales)
library(lubridate)
library(tidyr)
library(openair)

```


```{r, include = FALSE}

setwd('C:/Users/klynoe/Documents/toolik/R_outputs/flux_met_c/')

df <- fread('./toolik_flux_c_met_c_202505_202512.csv')

df$TIMESTAMP <- as.POSIXct( paste(df$TIMESTAMP, "00:00"), format = "%Y-%m-%d %H:%M", tz = "UTC")

full_time <- data.frame(
  TIMESTAMP = seq(min(df$TIMESTAMP),
                  max(df$TIMESTAMP),
                  by = "30 mins")
)

df <- merge(full_time, df, by = "TIMESTAMP", all.x = TRUE)


# data formatting for flag plots
# Ensure flags are character first
df$co2_flux.flag <- as.character(df$co2_flux.flag)
df$ch4_flux.flag <- as.character(df$ch4_flux.flag)
df$H.flag <- as.character(df$H.flag)
df$LE.flag <- as.character(df$LE.flag)


# Then assign factor with explicit levels
df$co2_flux.flag <- factor(df$co2_flux.flag, levels = c("0","1","2","3","4","5"))
df$ch4_flux.flag <- factor(df$ch4_flux.flag, levels = c("0","1","2","3","4","5"))

df$H.flag <- factor(df$H.flag, levels = c("0","1","2","3","4","5"))
df$LE.flag <- factor(df$LE.flag, levels = c("0","1","2","3","4","5"))

#df$co2_flux.flag <- as.factor(df$co2_flux.flag)
#df$ch4_flux.flag <- as.factor(df$ch4_flux.flag)

color_map = c("0" = "yellow3", "1" = "darkblue" , "2" =  "red4", "3" = "orange", "4" = "green4", "5" = "purple")

```

# Add any calculations that you want to keep throughout (make sure to adjust accordingly to site)
```{r, warning=FALSE, echo=FALSE}

##NOTE! NEVER USE filter(!is.na) - it'll break timeseries potentially - use ifelse

df$G = (df$SHF_6_37_1_1_1.c + df$SHF_6_37_2_1_1.c)/2  # SOIL HEAT FLUX

df <- df %>% mutate(SD_cm = ifelse(is.na(SD_10_99_1_1_1),NA,
      (SD_10_99_1_1_1 - (-2.06)) * 10 ))  # adjust and convert to cm - SNOW DEPTH
    
df <- df %>% mutate(sonic_c = sonic_temperature - 273.15) # - SONIC TEMP

df <- df %>% mutate(air_pressure_kpa = ifelse( is.na(air_pressure), NA, #- SONIC PRESSURE
      air_pressure / 1000))

df$Rn <- df$LWIN_6_14_1_1_1.c + df$SWIN_6_10_1_1_1.c -      # Compute net radiation 
         df$LWOUT_6_15_1_1_1.c - df$SWOUT_6_11_1_1_1.c

df$shf_avg = rowMeans(
  df[, c("SHF_6_37_1_1_1.c", "SHF_6_37_2_1_1.c")],     # Compute SHF safely with fallback 
  na.rm = TRUE
)

df <- df %>%
  mutate(across(c(SWC_12_36_1_1_1.c, SWC_12_36_2_1_1.c, SWC_12_36_3_1_1.c), ~ .x * 100)) # convert to %

```

# SUBSET MONTH AND WEEKS

```{r, warning=FALSE, echo=FALSE}


make_week_index <- function(df, time_col = "TIMESTAMP") {

  start_month <- as.POSIXct(
    format(min(df[[time_col]]), "%Y-%m-01 00:00"),
    tz = "UTC"
  )

  df$week_in_month <- floor(
    as.numeric(difftime(df[[time_col]], start_month, units = "days")) / 7
  ) + 1

  df
}

df_month <- subset(df,
  df$TIMESTAMP >= as.POSIXct("2025-11-01 00:00", tz = "UTC")
)

df_month <- make_week_index(df_month)


```

#BUILD A PLOTTING FUNCTION FOR CO2 AND CH4

```{r, warning=FALSE, echo=FALSE}

plot_flux <- function(df, flux_base,
                      ylims, y_label,
                      title = NULL) {

  flux      <- flux_base
  flux_c    <- paste0(flux_base, ".c")
  flux_flag <- paste0(flux_base, ".flag")

  df$.__flux__      <- df[[flux]]
  df$.__flux_c__    <- df[[flux_c]]
  df$.__flux_flag__ <- df[[flux_flag]]

  ggplot(df) +
    geom_hline(yintercept = 0) +
    geom_point(
      aes(TIMESTAMP, .__flux__, color = .__flux_flag__),
      na.rm = TRUE
    ) +
    geom_point(aes(TIMESTAMP, .__flux_c__), color = "black") +
    scale_y_continuous(limits = ylims) +
    labs(
      title = title,
      x = NULL,
      y = y_label
    ) +
    scale_color_manual(
      values = color_map,
      name = "Cleaning Flag",
      na.translate = FALSE
    ) +
    theme_bw()
}

```

# MAKE FUNCTION TO PLOT WEEKS OF CURRENT MONTH

```{r, warning=FALSE, echo=FALSE}

plot_week_flux <- function(df, week_num,
                           flux_base,
                           ylims, y_label) {

  dfw <- subset(df, week_in_month == week_num)

  plot_flux(
    dfw,
    flux_base,
    ylims,
    y_label,
    title = paste("Week", week_num)
  )
}

```

# Timeseries Plots

Flag = 0, 1, 2 : EP Flag
Flag = 3 : Absolute Limits Filter
Flag = 4 : Rolling MAD Filter
Flag = 5 : Diagnostic filter


## CO2

CO2 is cleaned with absolute limits of 8 & -15, and a limit of 3 MADs away from the mean over a 7 day window

#### Year-to-Date CO2 - wide range plot

```{r, warning=FALSE}

nee_plot_ytd <- plot_flux(
  df,
  "co2_flux",
  c(-30, 30),
  expression(paste( ~CO[2], ~"Flux (umol m",""^"-2","s",""^"-1",")"))
)

nee_plot_ytd

```

#### Year-to-Date CO2 - limit range plot

```{r, warning=FALSE}
# Flag = 0, 1, 2 : EP Flag
# Flag = 3 : Absolute Limits Filter
# Flag = 4 : Rolling MAD Filter
# Flag = 5 : Diagnostic filter

nee_plot_ytd <- plot_flux(
  df,
  "co2_flux",
  c(-12, 8),
  expression(paste( ~CO[2], ~"Flux (umol m",""^"-2","s",""^"-1",")"))
)

nee_plot_ytd

```

# PREVIOUS MONTH CO2

```{r, warning=FALSE}

nee_plot_month <- plot_flux(
  df_month,
  "co2_flux", 
  c(-12, 8),
  expression(paste( ~CO[2], ~"Flux (umol m",""^"-2","s",""^"-1",")"))
)

nee_plot_month

```


# WEEKLY CO2

```{r, warning=FALSE, message=FALSE, echo=FALSE, fig.show='hold'}

for (w in sort(unique(df_month$week_in_month))) {

  p <- plot_week_flux(
    df_month, w,
    "co2_flux", 
    c(-12, 8),
    expression(paste( ~CO[2], ~"Flux (umol m",""^"-2","s",""^"-1",")"))
  )

  plot(p)
}

```

## Methane

Methane is cleaned with absolute limits of -0.15 & 0.28, and a limit of 8 MADs away from the mean over a 7 day window

# YEAR TO DATE CH4

```{r, warning=FALSE}

ch4_plot_ytd <- plot_flux(
  df,
  "ch4_flux", 
  c(-0.1, 0.33),
  expression(paste( ~CH[4], ~"Flux (umol m",""^"-2","s",""^"-1",")"))
)

ch4_plot_ytd

```

# MONTHLY CH4

```{r, warning=FALSE}

ch4_plot_month <- plot_flux(
  df_month,
  "ch4_flux", 
  c(-0.1, 0.2),
  expression(paste( ~CH[4], ~"Flux (umol m",""^"-2","s",""^"-1",")"))
)

ch4_plot_month

```

#WEEKLY CH4

```{r, warning=FALSE, message=FALSE, echo=FALSE, fig.show='hold'}

for (w in sort(unique(df_month$week_in_month))) {

  p <- plot_week_flux(
    df_month, w,
    "ch4_flux",      
    c(-0.1, 0.2),    
    expression(paste( ~CH[4], ~"Flux (umol m",""^"-2","s",""^"-1",")"))
  )

  print(p)
}

```
#### ENERGY FLUXES WITH CLEANING FLAGS

# Year to Date H
```{r, warning=FALSE, echo=FALSE}
H_plot_ytd <- plot_flux(
  df,
  "H", 
  c(-400, 400),
    expression(paste("H (W/m"^2*")"))
)

H_plot_ytd

```

#### H Month
```{r, warning=FALSE, echo=FALSE}
H_plot_ytd <- plot_flux(
  df_month,
  "H", 
  c(-400, 400),
  expression(paste("H (W/m"^2*")"))
)

H_plot_ytd

```

#### H week
```{r, warning=FALSE, message=FALSE, echo=FALSE, fig.show='hold'}

for (w in sort(unique(df_month$week_in_month))) {

p <- plot_week_flux(
  df_month,w,
  "H", 
  c(-400, 400),
  expression(paste("H (W/m"^2*")"))
)

print(p)
}

```

#### Year to Date LE
```{r, warning=FALSE, echo=FALSE}
LE_plot_ytd <- plot_flux(
  df,
  "LE", 
  c(-100, 300),
  expression(paste("LE (W/m"^2*")"))
)

LE_plot_ytd

```
#### LE month
```{r, warning=FALSE, echo=FALSE}

LE_plot_month<- plot_flux(
  df_month,
  "LE", 
  c(-100, 300),
  expression(paste("LE (W/m"^2*")"))
)

LE_plot_month

```

#### Weekly LE

```{r, warning=FALSE, message=FALSE, echo=FALSE, fig.show='hold'}

for (w in sort(unique(df_month$week_in_month))) {

p <- plot_week_flux(
  df_month,w,
  "LE", 
  c(-100, 300),
  expression(paste("LE (W/m"^2*")"))
)

print(p)
}

```

# Diurnal Fluxes

```{r, warning=FALSE, echo=FALSE}
# set hour and month vectors to be able to take the averages

df$hour = as.numeric(format(df$ts,'%H'))
df$month = as.numeric(format(df$ts,'%m'))

diel = df %>%
  group_by(hour,month) %>%
  select(co2_flux.c,ch4_flux.c,LE.c,H.c, RN_6_5_1_1_1.c, u., TKE, hour,month) %>%
  summarise_all(.funs = c(median,sd),na.rm=T)

diel = subset(diel,!is.na(diel$month))
```

#### NEE

```{r, warning=FALSE, echo=FALSE}
diurnal_nee <- ggplot(data = diel)+geom_hline(yintercept = 0)+
  geom_line(aes(hour,co2_flux.c_fn1),lty=2)+
  geom_ribbon(aes(x = hour,y = co2_flux.c_fn1,
                  ymax = co2_flux.c_fn1 + co2_flux.c_fn2,
                  ymin = co2_flux.c_fn1 - co2_flux.c_fn2),
              alpha= 0.5)+
  facet_wrap(~month)
diurnal_nee
```

#### CH4

```{r, warning=FALSE, echo=FALSE}
diurnal_ch4 <- ggplot(data = diel)+geom_hline(yintercept = 0)+
  geom_line(aes(hour,ch4_flux.c_fn1),lty=2)+
  geom_ribbon(aes(x = hour,y = ch4_flux.c_fn1,
                  ymax = ch4_flux.c_fn1 + ch4_flux.c_fn2,
                  ymin = ch4_flux.c_fn1 - ch4_flux.c_fn2),
              alpha= 0.5)+
  facet_wrap(~month)
diurnal_ch4

```

## LE

```{r, warning=FALSE, echo=FALSE}
diurnal_le <- ggplot(data = diel)+geom_hline(yintercept = 0)+
  geom_line(aes(hour,LE.c_fn1),lty=2)+
  geom_ribbon(aes(x = hour,y = LE.c_fn1,
                  ymax = LE.c_fn1 + LE.c_fn2,
                  ymin = LE.c_fn1 - LE.c_fn2),
              alpha= 0.5)+
  facet_wrap(~month)
diurnal_le

```

# H

```{r, warning=FALSE, echo=FALSE}
diurnal_H <- ggplot(data = diel)+geom_hline(yintercept = 0)+
  geom_line(aes(hour,H.c_fn1),lty=2)+
  geom_ribbon(aes(x = hour,y = H.c_fn1,
                  ymax = H.c_fn1 + H.c_fn2,
                  ymin = H.c_fn1 - H.c_fn2),
              alpha= 0.5)+
  facet_wrap(~month)
diurnal_H

```

#RN

```{r, warning=FALSE, echo=FALSE}
diurnal_RN <- ggplot(data = diel)+geom_hline(yintercept = 0)+
  geom_line(aes(hour,RN_6_5_1_1_1.c_fn1),lty=2)+
  geom_ribbon(aes(x = hour,y = RN_6_5_1_1_1.c_fn1,
                  ymax = RN_6_5_1_1_1.c_fn1 + RN_6_5_1_1_1.c_fn2,
                  ymin = RN_6_5_1_1_1.c_fn1 - RN_6_5_1_1_1.c_fn2),
              alpha= 0.5)+
  facet_wrap(~month)
diurnal_RN

```

# U*

```{r, warning=FALSE, echo=FALSE}
diurnal_u. <- ggplot(data = diel)+geom_hline(yintercept = 0)+
  geom_line(aes(hour,u._fn1),lty=2)+
  geom_ribbon(aes(x = hour,y = u._fn1,
                  ymax = u._fn1 + u._fn2,
                  ymin = u._fn1 - u._fn2),
              alpha= 0.5)+
  facet_wrap(~month)
diurnal_u.

```

# Energy Balance Plots

#### Full Year-to-date COLOR CODED

```{r, warning=FALSE, echo=FALSE}

# Replace rows where both SHF were missing
both_missing <- is.na(df$SHF_6_37_1_1_1.c) & is.na(df$SHF_6_37_2_1_1.c)
df$shf_avg[both_missing] = 0  

# -------------------------------
# Compute energy balance
# -------------------------------
df$met <- df$Rn - df$shf_avg
df$flux <- df$H.c + df$LE.c

# Fit linear model
mod = lm(flux ~ met, data = df)
summary_mod = summary(mod)

# Extract slope and R²
slope = coef(mod)["met"]
r2 = summary_mod$r.squared
cat("Slope:", slope, "\nR²:", r2, "\n")

# Define axis limits
x_lim = c(-200,500)
y_lim = c(-200,500)

# Plot with month coloring
eb_ytd_month <- ggplot(df, aes(x = met, y = flux, color = factor(month))) +
  geom_point(alpha = 0.7) +
  geom_smooth(method = "lm", color = "blue", se = FALSE) +
  geom_abline(slope = 1, intercept = 0, linetype = "dashed", color = "red") +
  geom_hline(yintercept = 0, linetype = "solid", color = "black") +
  geom_vline(xintercept = 0, linetype = "solid", color = "black") +
  coord_fixed(ratio = 1, xlim = x_lim, ylim = y_lim) +
  scale_color_viridis_d(name = "Month") +
  labs(
    x = expression("Rn - G  (W m"^-2*")"),
    y = expression("H + LE  (W m"^-2*")"),
    title = "Toolik Full Year Energy Balance"
  ) +
  annotate(
    "text",
    x = max(x_lim), y = min(y_lim),
    label = paste0("Slope = ", round(slope, 3), "\nR² = ", round(r2, 3)),
    hjust = 1.1, vjust = -0.5, size = 4
  ) +
  theme_bw()

# Print
eb_ytd_month

```

#### Previous Month EB
```{r, warning=FALSE, echo=FALSE}

# Plot
eb_month <- ggplot(df_month, aes(x = met, y = flux)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", color = "blue", se = FALSE) +
  geom_abline(slope = 1, intercept = 0,
               linetype = "dashed", color = "red") +
  geom_hline(yintercept = 0, linetype = "solid", color = "black") +
  geom_vline(xintercept = 0, linetype = "solid", color = "black") +
  coord_fixed(ratio = 1, xlim = x_lim, ylim = y_lim) +
  labs(
    x = expression("Rn - G  (Wm"^-2*")"),
    y = expression("H + LE  (Wm"^-2*")"),
    title = expression("Previous Month EB")
  ) +
  annotate(
    "text",
    x = Inf, y = -Inf,
    label = paste0("Slope = ", round(slope, 3), "\nR² = ", round(r2, 3)),
    hjust = 1.1, vjust = -0.5, size = 4
  ) +
  theme_bw()
eb_month

```
##### Plot Builder Functions

```{r, warning=FALSE, echo=FALSE}

break_gaps <- function(df, ts_col, value_col, max_gap_minutes = 90) {

  df <- df[order(df[[ts_col]]), ]

  dt <- as.numeric(difftime(df[[ts_col]],
                            dplyr::lag(df[[ts_col]]),
                            units = "mins"))

  gap <- dt > max_gap_minutes
  gap[is.na(gap)] <- FALSE   # fix first NA safely

  df[[value_col]][gap] <- NA

  df
}


roll_vars <- c(                         # ADD VARIABLE THAT YOU WANT TO HAVE ROOLING AVERAGE 
  "H.c",
  "LE.c",
  "G",
  "LWIN_6_14_1_1_1.c",
  "LWOUT_6_15_1_1_1.c",
  "SWIN_6_10_1_1_1.c",
  "SWOUT_6_11_1_1_1.c",
  "PPFD_7_21_1_1_1.c",
  "PPFDR_7_23_1_1_1.c"
)

roll_smooth <- function(df, ts_col, value_col,
                        k = NULL,
                        base_resolution_min = NULL,
                        min_obs = NULL) {

  df <- as.data.frame(df)
  df <- df[order(df[[ts_col]]), ]

  # --- detect timestep automatically ---
  if (is.null(base_resolution_min)) {
    dt <- median(diff(as.numeric(df[[ts_col]])) / 60, na.rm = TRUE)
    base_resolution_min <- dt
  }

  pts_per_day <- 1440 / base_resolution_min

  # --- adaptive window ---
  if (is.null(k)) {
    n_days <- as.numeric(difftime(max(df[[ts_col]]),
                                 min(df[[ts_col]]),
                                 units = "days"))

    k_days <- dplyr::case_when(
      n_days <= 30    ~ 1,
      n_days <= 120   ~ 3,
      n_days <= 365   ~ 7,
      n_days <= 2*365 ~ 14,
      n_days <= 5*365 ~ 30,
      TRUE            ~ 45
    )

    k <- round(k_days * pts_per_day)
  }

  # --- adaptive min_obs (AFTER k is known!) ---
  if (is.null(min_obs)) {
    min_obs <- max(5, round(k * 0.2))
  }

  # -------------------------------
# -------------------------------
# SEGMENT BASED ON TIME GAPS ONLY
# -------------------------------
dt <- c(0, diff(as.numeric(df[[ts_col]])) / 60)
gap_flag <- dt > 90   # SAME as break_gaps()

segment_id <- cumsum(gap_flag)

  df$roll <- NA_real_

  # -------------------------------
  # APPLY ROLLING PER SEGMENT
  # -------------------------------
  for (seg in unique(segment_id)) {

  idx <- which(segment_id == seg)

  # ONLY smooth valid segments
  if (length(idx) == 0) next

  if (length(idx) < k) next

  sm <- zoo::rollapply(
    df[[value_col]][idx],
    width = k,
    align = "center",
    fill = NA,
    partial = TRUE,
    FUN = function(x) {

      if (sum(!is.na(x)) < min_obs) {
        return(NA_real_)
      }

      mean(x, na.rm = TRUE)
    }
  )

  df$roll[idx] <- sm
}
  return(df)
}


# ------------------------------- # Single-variable flux/energy plot # ------------------------------- 

plot_flux_single <- function(df, ts_col = "TIMESTAMP", flux_col,
                             y_label, title, color = "blue", 
                             date_breaks = "1 month", date_labels = "%b",
                             smooth = FALSE,
                             y_limits = NULL,
                             clip_smooth = NULL){

  # --- split data for line vs smooth ---
  df_line   <- break_gaps(df, ts_col, flux_col)  # for geom_line
  df_smooth <- df[order(df[[ts_col]]), ]# clean data for loess

  p <- ggplot(df_line, aes(x = .data[[ts_col]])) +
    geom_hline(yintercept = 0, linetype = "dashed", color = "black") +
    geom_line(aes(x = .data[[ts_col]], y = .data[[flux_col]]),
    #geom_line(aes(y = .data[[flux_col]]),
              linewidth = 0.8, alpha = 0.6, color = color) + 
    labs(x = "", y = y_label, title = title) + 
    scale_y_continuous(
      limits = y_limits,
      expand = expansion(mult = 0.05),
      breaks = scales::pretty_breaks(n = 8)
    ) +
    scale_x_datetime(date_breaks = date_breaks, 
                     date_labels = date_labels) +
    theme_minimal() + 
    theme(axis.text.x = element_text(angle = 45, hjust = 1))
  
  


  if (smooth) {

    # --- choose smoothing method based on variable ---
    if (flux_col %in% roll_vars) {

      df_roll <- roll_smooth(df_smooth, ts_col, flux_col)

      p <- p + geom_line(
        data = df_roll,
        aes(x = .data[[ts_col]], y = .data[["roll"]]),
        #aes(x = .data[[ts_col]], y = roll),
        color = "black",
        linewidth = 0.9
      )

    } else {

      # LOESS for bounded / slow variables
      n <- nrow(df_smooth)
      span_auto <- max(min((48*2) / n, 0.2), 0.01)

      p <- p + geom_smooth(
        data = df_smooth,
       # aes(x = .data[[ts_col]], y = .data[[flux_col]]),
        aes(x = .data[[ts_col]], y = .data[[flux_col]]),
        method = "loess",
        span = span_auto,
        color = "black",
        linewidth = 0.7,
        se = FALSE
      )

      if (!is.null(clip_smooth)) {
        p <- p + coord_cartesian(ylim = clip_smooth)
      }
    }
  }

  return(p)
}

# ------------------------------- # Long-format paired-variable flux/energy plot # -------------------------------

plot_flux_long <- function(df, ts_col = "TIMESTAMP", 
                           cols, labels, colors, 
                           y_label, title, 
                           date_breaks = "1 month",
                           date_labels = "%b", 
                           smooth = FALSE) {
  
  # -------------------------------
  # RAW LINES WITH GAP BREAKS
  # -------------------------------
  raw_list <- lapply(cols, function(v) {
    
    dfv <- df[, c(ts_col, v), drop = FALSE]
    names(dfv) <- c(ts_col, "value")
    dfv$variable <- v
    
    dfv <- break_gaps(dfv, ts_col, "value")
    dfv
  })
  
  df_long <- do.call(rbind, raw_list)
  df_long$variable <- factor(df_long$variable, levels = cols)
  
  p <- ggplot(df_long, aes(x = .data[[ts_col]], y = value, color = variable)) +
    geom_line(alpha = 0.6, linewidth = 0.8) + 
    scale_color_manual(values = colors, labels = labels, name = NULL) + 
    scale_y_continuous(expand = expansion(mult = 0.05), 
                       breaks = scales::pretty_breaks(n = 8),
                       name = y_label) + 
    scale_x_datetime(date_breaks = date_breaks, 
                     date_labels = date_labels) + 
    labs(title = title, x = "") +
    theme_minimal() + 
    theme(axis.text.x = element_text(angle = 45, hjust = 1), 
          legend.position = "top") 
  
  # -------------------------------
  # SMART SMOOTHING
  # -------------------------------
  if (smooth) {
    
    smooth_list <- lapply(cols, function(v) {
      
      dfv <- df[, c(ts_col, v), drop = FALSE]
      names(dfv) <- c(ts_col, "value")
      dfv$variable <- v
      
      if (v %in% roll_vars) {
        dfv <- break_gaps(dfv, ts_col, "value")
        dfv <- roll_smooth(dfv, ts_col, "value")
        dfv$smooth_value <- dfv$roll
      } else {
        n <- nrow(dfv)
        span_auto <- max(min((48*2) / n, 0.2), 0.01)
        
        lo <- loess(value ~ as.numeric(dfv[[ts_col]]),
                    data = dfv,
                    span = span_auto,
                    na.action = na.exclude)
        
        dfv$smooth_value <- predict(lo)
      }
      
      dfv
    })
    
    df_smooth <- do.call(rbind, smooth_list)
    df_smooth$variable <- factor(df_smooth$variable, levels = cols)
    
    p <- p + geom_line(
      data = df_smooth,
      aes(x = .data[[ts_col]], y = smooth_value, color = variable),
      linewidth = 0.9
    )
  }
  
  return(p)
}



```

# Year to Date H and LE
```{r, warning=FALSE}
# Sensible and latent heat fluxes stacked
p_H <- plot_flux_single(df, flux_col = "H.c",
                        y_label = "H (W/m²)",
                        title = "Sensible Heat Flux (H)",
                        color = "firebrick",
                        smooth = T)
                  
        

p_LE <- plot_flux_single(df, flux_col = "LE.c",
                         y_label = "LE (W/m²)",
                         title = "Latent Heat Flux (LE)",
                         color = "dodgerblue",
                         smooth = T)
                        
         

p_H / p_LE  # stack using patchwork

```
# Monthly H and LE
```{r, warning=FALSE}
p_H_mo <- plot_flux_single(df_month, flux_col = "H.c",
                           y_label = "H (W/m²)",
                           title = "Sensible Heat Flux (H)",
                           color = "firebrick",
                           date_breaks = "2 days",
                           date_labels = "%b %d")

p_LE_mo <- plot_flux_single(df_month, flux_col = "LE.c",
                            y_label = "LE (W/m²)",
                            title = "Latent Heat Flux (LE)",
                            color = "dodgerblue",
                            date_breaks = "2 days",
                            date_labels = "%b %d")

p_H_mo / p_LE_mo

```

#Year to Date Longwave Radiation
```{r, warning=FALSE}
p_lw <- plot_flux_long(df,
                       cols = c("LWIN_6_14_1_1_1.c", "LWOUT_6_15_1_1_1.c"),
                       labels = c("Incoming LW", "Outgoing LW"),
                       colors = c("firebrick", "dodgerblue"),
                       y_label = expression(Longwave~Radiation~(W/m^2)),
                       title = "Longwave Radiation In/Out",
                       date_breaks = "1 month",
                       date_labels = "%b",
                       smooth = T)
p_lw

```

# Monthly Longwave Radiation
```{r, warning=FALSE}
p_lw <- plot_flux_long(df_month,
                       cols = c("LWIN_6_14_1_1_1.c", "LWOUT_6_15_1_1_1.c"),
                       labels = c("Incoming LW", "Outgoing LW"),
                       colors = c("firebrick", "dodgerblue"),
                       y_label = expression(Longwave~Radiation~(W/m^2)),
                       title = "Longwave Radiation In/Out",
                       date_breaks = "2 days",
                       date_labels = "%b %d")
p_lw

```

# Year to Date Shortwave Radiation
```{r, warning=FALSE}
p_sw <- plot_flux_long(df,
                       cols = c("SWIN_6_10_1_1_1.c", "SWOUT_6_11_1_1_1.c"),
                       labels = c("Incoming SW", "Outgoing SW"),
                       colors = c("pink4", "dodgerblue4"),
                       y_label = expression(Shortwave~Radiation~(W/m^2)),
                       title = "Shortwave Radiation In/Out",
                       date_breaks = "1 month",
                       date_labels = "%b",
                       smooth = T)

p_sw

```
# Monthly Shortwave 

```{r, warning=FALSE}
p_sw <- plot_flux_long(df_month,
                       cols = c("SWIN_6_10_1_1_1.c", "SWOUT_6_11_1_1_1.c"),
                       labels = c("Incoming SW", "Outgoing SW"),
                       colors = c("pink4", "dodgerblue4"),
                       y_label = expression(Shortwave~Radiation~(W/m^2)),
                       title = "Shortwave Radiation In/Out",
                       date_breaks = "2 days",
                       date_labels = "%b %d")

p_sw

```
# Year to Date PAR
```{r, warning=FALSE}

p_par_IN <- plot_flux_single(df, flux_col = "PPFD_7_21_1_1_1.c",
                             y_label = expression(PAR~"(µmol m"^-2~" s"^-1*")"),
                             title = "PAR — In",
                             color = "forestgreen",
                             date_breaks = "1 month",
                             date_labels = "%b",
                             smooth = T)

p_par_OUT <- plot_flux_single(df, flux_col = "PPFDR_7_23_1_1_1.c",
                              y_label = expression(PAR~"(µmol m"^-2~" s"^-1*")"),
                              title = "PAR — Out",
                              color = "forestgreen",
                              date_breaks = "1 month",
                              date_labels = "%b",
                              smooth = T)

p_par_IN / p_par_OUT

```

# Monthly PAR
```{r, warning=FALSE}

p_par_IN <- plot_flux_single(df_month, flux_col = "PPFD_7_21_1_1_1.c",
                             y_label = expression(PAR~"(µmol m"^-2~" s"^-1*")"),
                             title = "PAR — In",
                             color = "forestgreen",
                             date_breaks = "2 days",
                             date_labels = "%b %d")

p_par_OUT <- plot_flux_single(df_month, flux_col = "PPFDR_7_23_1_1_1.c",
                              y_label = expression(PAR~"(µmol m"^-2~" s"^-1*")"),
                              title = "PAR — Out",
                              color = "forestgreen",
                              date_breaks = "2 days",
                              date_labels = "%b %d")

p_par_IN / p_par_OUT

```
## Albedo
```{r, warning=FALSE}
p_albedo <- plot_flux_single(df, flux_col = "ALB_1_1_1.c",
                             y_label = "Albedo",
                             title = "Albedo",
                             color = "cyan4",
                             date_breaks = "1 month",
                             date_labels = "%b",
                             smooth = T,
                             y_limits =c(0,1),
                             clip_smooth = c(0,1)
                             )

p_albedo 
```

```{r, warning=FALSE}

```
## Year to Date Heat Flux (G)
```{r, warning=FALSE}
p_G <- plot_flux_single(df, flux_col = "G",
                        y_label = expression(Soil~Heat~Flux~(W/m^2)),
                        title = "Soil Heat Flux",
                        color = "blue",
                        date_breaks = "1 month",
                        date_labels = "%b",
                        smooth = T)
p_G
```
## Monthly Heat Flux (G)
```{r, warning=FALSE}
p_G <- plot_flux_single(df_month, flux_col = "G",
                        y_label = expression(Soil~Heat~Flux~(W/m^2)),
                        title = "Soil Heat Flux",
                        color = "blue",
                        date_breaks = "2 days",
                        date_labels = "%b %d")#,
                        #smooth = FALSE)
p_G
```

#### Year to Date Soil Moisture
```{r, warning=FALSE, echo=FALSE}

P_soilM <- plot_flux_long(
  df,
  cols = c("SWC_12_36_1_1_1.c",
           "SWC_12_36_2_1_1.c",
           "SWC_12_36_3_1_1.c"),
  labels = c("8 cm", "18 cm", "28 cm"),
  colors = c("blue", "green", "gold3"),
  y_label = "Soil Moisture (%)",
  title = "Soil Moisture by Depth")
P_soilM

```

#### Monthly Soil Moisture
```{r, warning=FALSE, echo=FALSE}
P_soilM <- plot_flux_long(
  df_month,
  cols = c("SWC_12_36_1_1_1.c",
           "SWC_12_36_2_1_1.c",
           "SWC_12_36_3_1_1.c"),
  labels = c("8 cm", "18 cm", "28 cm"),
  colors = c("blue", "green", "gold3"),
  y_label = "Soil Moisture (%)",
  title = "Soil Moisture by Depth",
  date_breaks = "2 days",
  date_labels = "%b %d")

P_soilM

```

#### Year to Date Soil Temperatures
```{r, warning=FALSE, echo=FALSE}

P_soilT <- plot_flux_long(
  df,
  cols = c("TS_2_38_1_1_1.c",
           "TS_2_38_2_1_1.c",
           "TS_2_38_23_1_1.c"),
  labels = c("8 cm", "18 cm", "28 cm"),
  colors = c("blue", "green", "gold3"),
  y_label = "Soil Temperature (°C)",
  title = "Soil Temperature by Depth"
)
P_soilT

```

#### Monthly Soil Temperatures
```{r, warning=FALSE, echo=FALSE}
P_soilT <- plot_flux_long(
  df_month,
  cols = c("TS_2_38_1_1_1.c",
           "TS_2_38_2_1_1.c",
           "TS_2_38_23_1_1.c"),
  labels = c("8 cm", "18 cm", "28 cm"),
  colors = c("blue", "green", "gold3"),
  y_label = "Soil Temperature (°C)",
  title = "Soil Temperature by Depth",
  date_breaks = "2 days",
  date_labels = "%b %d")

P_soilT

```

#Year to Date Air Temperature
```{r, warning=FALSE}
p_air <- plot_flux_single(
  df,
  flux_col = "TA_2_1_1_1_1.c",
  y_label  = "Air Temperature (°C)",
  title    = "Air Temperature",
  color    = "red",
  date_breaks = "1 month",
  date_labels = "%b"
)

p_air
```
# Monthly Air Temperature
```{r, warning=FALSE}
p_air <- plot_flux_single(
  df_month,
  flux_col = "TA_2_1_1_1_1.c",
  y_label  = "Air Temperature (°C)",
  title    = "Air Temperature",
  color    = "red",
  date_breaks = "2 days",
  date_labels = "%b %d"
)
p_air
```
# SONIC PRESSURE

```{r, warning=FALSE}
p_pres <- plot_flux_single(
  df,
  flux_col = "air_pressure_kpa",
  y_label  = "Air Pressure (kpa)",
  title    = "Air Pressure",
  color    = "black",
  date_breaks = "1 month",
  date_labels = "%b",
  y_limits = c(80,100)
)

p_pres
 
```

# RELATIVE HUMIDITY

```{r, warning=FALSE}
p_rh <- plot_flux_single(
  df,
  flux_col = "RH.c",
  y_label  = "Relative Humidity (%)",
  title    = "Relative Humidity ",
  color    = "lightblue4",
  date_breaks = "1 month",
  date_labels = "%b",
  smooth = T,
  y_limits = c(0,100),
  clip_smooth = c (0,100)
)

p_rh
 
```

#### T air vs T sonic - full
```{r, warning=FALSE, echo=FALSE}

full_temp_plot <- plot_flux_long(
  df,
  cols   = c("TA_2_1_1_1_1.c", "sonic_c"),
  labels = c("Air Temp", "Sonic Temp"),
  colors = c("red", "blue"),
  y_label = "Temperature (°C)",
  title   = "Air vs Sonic Temperature — Full Timeseries",
  smooth  = FALSE,           # only once!
  date_breaks = "1 month",
  date_labels = "%b"
)


full_temp_plot 
```

#### T air vs T sonic - month
```{r, warning=FALSE, echo=FALSE}

month_temp_plot <- plot_flux_long(
  df_month,
  cols   = c("TA_2_1_1_1_1.c", "sonic_c"),
  labels = c("Air Temp", "Sonic Temp"),
  colors = c("red", "blue"),
  y_label = "Temperature (°C)",
  title   = "Air vs Sonic Temperature — Month View",
  smooth  = FALSE,
  date_breaks = "1 week",
  date_labels = "%b %d"
)

month_temp_plot
```

#### T air vs T sonic - weeks
```{r, warning=FALSE, echo=FALSE}

week_temp_plots <- lapply(
  sort(unique(df_month$week_in_month)),
  function(w) {
    plot_flux_long(
      subset(df_month, week_in_month == w),
      cols   = c("TA_2_1_1_1_1.c", "sonic_c"),
      labels = c("Air Temp", "Sonic Temp"),
      colors = c("red", "blue"),
      y_label = "Temperature (°C)",
      title   = paste("Air vs Sonic Temperature — Week", w),
      smooth  = FALSE,
      date_breaks = "1 day",
      date_labels = "%b %d"
    )
  }
)
names(week_temp_plots) <- paste0("Week_", sort(unique(df_month$week_in_month)))

week_temp_plots

```

#### SNOW DEPTH
```{r, warning=FALSE, echo=FALSE}
p_sd <- plot_flux_single(df, flux_col = "SD_cm",
                             y_label = "Snow Depth (cm)",
                             title = "Snow Depth",
                             color = "turquoise2",
                             date_breaks = "1 month",
                             date_labels = "%b",
                             smooth = TRUE)

p_sd
```
# PRECIP (RAIN) -to be added 2026
```{r, warning=FALSE, echo=FALSE}


```

# Year to Date Wind
```{r,warning=FALSE}  

df_wind_openair <- df %>%
  filter(!is.na(wind_dir) & !is.na(WS_16_33_1_1_1)) %>%
  rename(
    wd = wind_dir,
    ws = WS_16_33_1_1_1
  )

windRose(df_wind_openair,
         ws = "ws",
         wd = "wd",
         paddle = FALSE,
         key = TRUE,
         main = "Wind Rose")
```

# Monthly Wind
```{r, warning=FALSE} 

df_wind_openair <- df_month %>%
  filter(!is.na(wind_dir) & !is.na(WS_16_33_1_1_1)) %>%
  rename(
    wd = wind_dir,
    ws = WS_16_33_1_1_1
  )

windRose(df_wind_openair,
         ws = "ws",
         wd = "wd",
         paddle = FALSE,
         key = TRUE,
         main = "Wind Rose")

```


#POTENTIAL RADIATION VS SWIN - TIME ALIGNMENT CHECK
#making monthly diel graphs
```{r, warning=F, echo=FALSE}

df$TIMESTAMP <- as.POSIXct(df$TIMESTAMP, tz = "UTC")

df$year  <- as.numeric(format(df$TIMESTAMP, "%Y"))
df$month <- as.numeric(format(df$TIMESTAMP, "%m"))
df$hour  <- as.numeric(format(df$TIMESTAMP, "%H"))

diel_rad <- df %>%
  group_by(year, month, hour) %>%
  summarise(
    rad_mean  = mean(SWIN_6_10_1_1_1, na.rm = TRUE),
    rad_sd    = sd(SWIN_6_10_1_1_1, na.rm = TRUE),
    rpot_mean = mean(rpot, na.rm = TRUE),
    .groups = "drop"
  )

month_list <- diel_rad %>%
  distinct(year, month) %>%
  arrange(year, month)

for(i in 1:nrow(month_list)) {
  
  y <- month_list$year[i]
  m <- month_list$month[i]
  
  dfm <- diel_rad %>%
    filter(year == y, month == m)
  
  p <- ggplot(dfm) +
    
    # rpot line (like original blue line)
    geom_line(aes(hour, rpot_mean),
              color = "blue",
              linewidth = 0.8) +
    
    # measured radiation mean
    geom_line(aes(hour, rad_mean),
              linetype = 2) +
    
    # variability ribbon
    geom_ribbon(aes(
      x = hour,
      ymin = rad_mean - rad_sd,
      ymax = rad_mean + rad_sd
    ),
    alpha = 0.3) +
    
    scale_x_continuous(breaks = seq(0, 23, by = 3)) +
    
    labs(
      title = format(as.Date(paste(y, m, 1, sep = "-")), "%B %Y"),
      x = "Hour of Day",
      y = "Radiation (W m⁻²)"
    ) +
    
    theme_minimal()
  
  print(p)
}


```

#POTENTIAL RADIATION VS SWIN - TIME ALIGNMENT CHECK

```{r, warning=FALSE, echo=FALSE}

generate_rad_plots <- function(df,
                               timestamp_col,
                               value_col,
                               mode = "biweekly",
                               month_start = NULL) {
  
  # --- Time handling ---
  df[[timestamp_col]] <- as.POSIXct(df[[timestamp_col]], tz = "UTC")
  
  # Keep a FULL copy for rpot 
  df_full <- df
  
  # Filter ONLY for points/legend cleanliness
  df <- df[!is.na(df$radflag), ]
  df$radflag <- factor(df$radflag, levels = c(0, 1))
  
  # ----- Base plot (no data attached yet) -----
  base_plot <- ggplot() +
    
    # rpot from FULL continuous dataset
    geom_line(
      data = df_full,
      aes(x = .data[[timestamp_col]], y = rpot),
      color = "blue",
      linewidth = 0.6,
      na.rm = TRUE
    ) +
    
    # measured radiation from filtered dataset
    geom_point(
      data = df,
      aes(x = .data[[timestamp_col]],
          y = .data[[value_col]],
          color = radflag),
      alpha = 0.7
    ) +
    
    labs(x = "", y = value_col, color = "Rad Flag") +
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          legend.position = "top") +
    scale_color_manual(
      values = c("0" = "black", "1" = "red"),
      breaks = c("0", "1"),
      drop = TRUE
    )
  
  # =========================================================
  # MODE 1 — BIWEEKLY
  # =========================================================
  if (mode == "biweekly") {
    
    start_datetime <- min(df_full[[timestamp_col]], na.rm = TRUE)
    end_datetime   <- max(df_full[[timestamp_col]], na.rm = TRUE)
    interval <- 14 * 24 * 3600
    
    current_start <- start_datetime
    plot_count <- 1
    
    while (current_start < end_datetime) {
      
      current_end <- min(current_start + interval, end_datetime)
      
      p <- base_plot +
        ggtitle(paste0(
          "Biweekly: ",
          format(current_start, "%Y-%m-%d"),
          " to ",
          format(current_end, "%Y-%m-%d")
        )) +
        scale_x_datetime(
          limits = c(current_start, current_end),
          date_breaks = "2 day",
          date_labels = "%b %d"
        )
      
      print(p)
      assign(paste0("rad_biweek_", plot_count), p, envir = .GlobalEnv)
      
      current_start <- current_end
      plot_count <- plot_count + 1
    }
  }
  
  # =========================================================
  # MODE 2 — WEEKLY INSIDE A MONTH
  # =========================================================
  if (mode == "weekly_month") {
    
    if (is.null(month_start)) {
      stop("You must provide month_start for weekly_month mode")
    }
    
    month_start <- as.POSIXct(month_start, tz = "UTC")
    month_end <- seq(month_start, length = 2, by = "1 month")[2]
    
    df_month_full <- df_full[df_full[[timestamp_col]] >= month_start &
                               df_full[[timestamp_col]] < month_end, ]
    
    df_month <- df[df[[timestamp_col]] >= month_start &
                     df[[timestamp_col]] < month_end, ]
    
    df_month <- make_week_index(df_month, timestamp_col)
    
    weeks <- sort(unique(df_month$week_in_month))
    plot_count <- 1
    
    for (w in weeks) {
      
      dfw <- df_month[df_month$week_in_month == w, ]
      start_w <- min(dfw[[timestamp_col]])
      end_w   <- max(dfw[[timestamp_col]])
      
      p <- ggplot() +
        
        # rpot still from FULL month data
        geom_line(
          data = df_month_full,
          aes(x = .data[[timestamp_col]], y = rpot),
          color = "blue",
          linewidth = 0.6,
          na.rm = TRUE
        ) +
        
        geom_point(
          data = dfw,
          aes(x = .data[[timestamp_col]],
              y = .data[[value_col]],
              color = radflag),
          alpha = 0.7
        ) +
        
        labs(x = "", y = value_col, color = "Rad Flag") +
        theme_minimal() +
        theme(axis.text.x = element_text(angle = 45, hjust = 1),
              legend.position = "top") +
        scale_color_manual(
          values = c("0" = "black", "1" = "red"),
          breaks = c("0", "1"),
          drop = TRUE
        ) +
        ggtitle(paste0(
          "Week ", w, ": ",
          format(start_w, "%b %d"),
          " to ",
          format(end_w, "%b %d, %Y")
        )) +
        scale_x_datetime(
          limits = c(start_w, end_w),
          date_breaks = "1 day",
          date_labels = "%b %d"
        )
      
      print(p)
      assign(paste0("rad_week_", plot_count), p, envir = .GlobalEnv)
      plot_count <- plot_count + 1
    }
  }
}



```


#### Previous Month Radiation Plots
```{r, warning=FALSE, echo=FALSE}
generate_rad_plots(df,
                   "TIMESTAMP",
                   "SWIN_6_10_1_1_1",
                   mode = "weekly_month",
                   month_start = "2025-11-01")

```






