---
title: "Toolik annual qc check"
author: "Kaj"
date: "2026-01-26"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(error =  TRUE)
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = 'C:/Users/klynoe/Documents/toolik/R_outputs/flux_met_c/') #use this to set your directory
```


This file generates plots for the annual data checks


```{r, include=FALSE}
# Load packages, cleaned data 

rm(list = ls())

library(data.table)
library(ggplot2)
library(cowplot)
library(openair)
library(plotrix)
library(signal)
library(svMisc)
library(zoo)
library(stringr)
library(plyr)
library(dplyr)
library(patchwork) # formats plots
library(bigleaf) # for radiation check
library(scales)
library(lubridate)
library(tidyr)

```

#DATA LOADER AND FLAGS
```{r, include = FALSE}

df <- fread('./toolik_flux_c_met_c_202505_202512.csv')

#df$ts <- df$ts-9*3600 #adjust timezone from UTC to CST
#df$TIMESTAMP <- df$TIMESTAMP-9*3600 #adjust timezone from UTC to CST

df$TIMESTAMP <- as.POSIXct( paste(df$TIMESTAMP, "00:00"), format = "%Y-%m-%d %H:%M", tz = "UTC")


# data formatting for flag plots
# Ensure flags are character first
df$co2_flux.flag <- as.character(df$co2_flux.flag)
df$ch4_flux.flag <- as.character(df$ch4_flux.flag)

# Then assign factor with explicit levels
df$co2_flux.flag <- factor(df$co2_flux.flag, levels = c("0","1","2","3","4","5"))
df$ch4_flux.flag <- factor(df$ch4_flux.flag, levels = c("0","1","2","3","4","5"))

#df$co2_flux.flag <- as.factor(df$co2_flux.flag)
#df$ch4_flux.flag <- as.factor(df$ch4_flux.flag)

color_map = c("0" = "yellow3", "1" = "darkblue" , "2" =  "red4", "3" = "orange", "4" = "green4", "5" = "purple")

```


# Timeseries Plots

Flag = 0, 1, 2 : EP Flag
Flag = 3 : Absolute Limits Filter
Flag = 4 : Rolling MAD Filter
Flag = 5 : Diagnostic filter

# ANNUAL PLOT CO2
```{r, warning=FALSE}
# Flag = 0, 1, 2 : EP Flag
# Flag = 3 : Absolute Limits Filter
# Flag = 4 : Rolling MAD Filter
# Flag = 5 : Diagnostic filter

# -------------------------------
# NEE Plot with Monthly Ticks
# -------------------------------
nee_plot_ytd <- ggplot(data = df) +
  geom_hline(yintercept = 0) +
  geom_point(
    data = subset(df, !is.na(co2_flux.flag)),
    aes(TIMESTAMP, co2_flux, color = co2_flux.flag)
  ) +
  geom_point(aes(TIMESTAMP, co2_flux.c), col = 'black') +
  scale_y_continuous(limits = c(-30, 30)) +
  scale_x_datetime(
    date_breaks = "1 month",
    date_labels = "%b"
  ) +
  labs(
    title = "Toolik",
    x = "Month",
    y = bquote(CO[2]~"Flux ("*mu*"mol m"^-2~"s"^-1*")")
  ) +
  scale_color_manual(values = color_map, name = "Cleaning Flag") +
  theme_bw() +
  theme(
    plot.title = element_text(hjust = 0.5),
    axis.text.x = element_text(angle = 45, hjust = 1)
  )

nee_plot_ytd


```
# MONTHLY CO2

```{r}

# Add month column
df <- df %>%
  mutate(month = as.numeric(format(TIMESTAMP, "%m")))

# Sort unique months
months <- sort(unique(df$month))

# Loop: print separate plot for each month
for (m in months) {
  
  df_month <- df %>% filter(month == m)
  
  p <- ggplot(data = df_month) +
    geom_hline(yintercept = 0) +
    geom_point(
      data = subset(df_month, !is.na(co2_flux.flag)),
      aes(TIMESTAMP, co2_flux, color = co2_flux.flag),
      alpha = 0.7
    ) +
    geom_point(
      aes(TIMESTAMP, co2_flux.c),
      color = 'black',
      alpha = 0.7
    ) +
    scale_y_continuous(limits = c(-30, 30)) +
    scale_color_manual(values = color_map, name = "Cleaning Flag") +
    labs(
     title = bquote(CO[2]~"Flux — Month"~~.(m)),
      x = "Time",
      y = expression(paste(CO[2], " Flux (µmol m"^-2," s"^-1,")"))
    ) +
    theme_bw() +
    theme(
      axis.text.x = element_text(angle = 45, hjust = 1)
    )
  
  print(p)
}
```
#BI WEEKLY CO2

```{r, warning=FALSE}

df <- df %>%
  arrange(TIMESTAMP) %>%
  mutate(
    biweek = as.numeric(floor((as.numeric(TIMESTAMP) - min(as.numeric(TIMESTAMP))) / (14*24*3600))) + 1
  )

# Sort unique biweek periods
biweeks <- sort(unique(df$biweek))

# Loop: print separate plot for each bi-week window
for (b in biweeks) {
  
  df_bw <- df %>% filter(biweek == b)
  
  p <- ggplot(data = df_bw) +
    geom_hline(yintercept = 0) +
    
    geom_point(
      data = subset(df_bw, !is.na(co2_flux.flag)),
      aes(TIMESTAMP, co2_flux, color = co2_flux.flag),
      alpha = 0.7
    ) +
    
    geom_point(
      aes(TIMESTAMP, co2_flux.c),
      color = 'black',
      alpha = 0.7
    ) +
    
    scale_y_continuous(limits = c(-18, 18)) +
    scale_x_datetime(
      date_breaks = "1 day",
      date_labels = "%d-%b"
    ) +
    scale_color_manual(values = color_map, name = "Cleaning Flag") +
    
    labs(
      title = bquote(CO[2]~"Flux — Bi-Week"~~.(b)),
      x = "Day",
      y = expression(paste(CO[2], " Flux (µmol m"^-2," s"^-1,")"))
    ) +
    
    theme_bw() +
    theme(
      axis.text.x = element_text(angle = 45, hjust = 1)
    )
  
  print(p)
}


```


#### ANNUAL CH4
```{r, warning=FALSE, echo=FALSE}

# Flag = 0, 1, 2 : EP Flag
# Flag = 3 : Absolute Limits Filter
# Flag = 4 : Rolling MAD Filter
# Flag = 5 : Diagnostic filter

ch4_plot_ytd <- ggplot(data = df) +
  geom_hline(yintercept = 0) +
  
  # QC flagged points
  geom_point(
    data = subset(df, !is.na(ch4_flux.flag)),
    aes(TIMESTAMP, ch4_flux, color = ch4_flux.flag),
    alpha = 0.7
  ) +
  
  # Corrected CH4 points
  geom_point(aes(TIMESTAMP, ch4_flux.c), col = 'black', alpha = 0.7) +
  
  # Y-axis limits
  scale_y_continuous(limits = c(-0.1, 0.33)) +
  
  # X-axis monthly ticks
  scale_x_datetime(
    date_breaks = "1 month",
    date_labels = "%b"
  ) +
  
  # QC color mapping
  scale_color_manual(values = color_map, name = "QC CH4 Flux") +
  
  # Labels
  labs(
    title = "Toolik",
    x = "Month",
    y = bquote(CH[4]~"Flux ("*mu*"mol m"^-2~"s"^-1*")")
  ) +
  
  theme_bw() +
  theme(
    plot.title = element_text(hjust = 0.5),
    axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "right"
  )

ch4_plot_ytd


```

#CH4 MONTHLY

```{r, warning=FALSE}

# Add month column if not already present
if(!"month" %in% names(df)) {
  df <- df %>% mutate(month = as.numeric(format(TIMESTAMP, "%m")))
}

# List unique months
months <- sort(unique(df$month))

for (m in months) {
  
  df_month <- df %>% filter(month == m)
  
  p <- ggplot(data = df_month) +
    geom_hline(yintercept = 0) +
    geom_point(
      data = subset(df_month, !is.na(ch4_flux.flag)),
      aes(TIMESTAMP, ch4_flux, color = ch4_flux.flag),
      alpha = 0.7
    ) +
    geom_point(
      aes(TIMESTAMP, ch4_flux.c),
      color = "black",
      alpha = 0.7
    ) +
   # scale_y_continuous(limits = c(-0.1, 0.1)) +
    scale_color_manual(values = color_map, name = "QC CH4 Flux") +
    labs(
      title = bquote(CH[4]~"Flux — Month"~~.(m)),
      x = "Time",
      y = expression(paste(CH[4], " Flux (µmol m"^-2," s"^-1,")"))
    ) +
    theme_bw() +
    theme(
      axis.text.x = element_text(angle = 45, hjust = 1)
    )
  
  print(p)
}


```

#BI WEEKLY CH4
```{r, warning=FALSE}

df <- df %>%
  arrange(TIMESTAMP) %>%
  mutate(
    biweek = as.numeric(floor((as.numeric(TIMESTAMP) - min(as.numeric(TIMESTAMP))) / (14*24*3600))) + 1
  )

# Sort unique biweek periods
biweeks <- sort(unique(df$biweek))

# Loop: print separate plot for each bi-week window
for (b in biweeks) {
  
  df_bw <- df %>% filter(biweek == b)
  
  p <- ggplot(data = df_bw) +
    geom_hline(yintercept = 0) +
    
    geom_point(
      data = subset(df_bw, !is.na(ch4_flux.flag)),
      aes(TIMESTAMP, ch4_flux, color = ch4_flux.flag),
      alpha = 0.7
    ) +
    
    geom_point(
      aes(TIMESTAMP, ch4_flux.c),
      color = "black",
      alpha = 0.7
    ) +
    
    # Daily x-axis ticks
    scale_x_datetime(
      date_breaks = "1 day",
      date_labels = "%d-%b"
    ) +
    
    scale_color_manual(values = color_map, name = "QC CH₄ Flux") +
    
    labs(
      title = bquote(CH[4]~"Flux — Bi-Week"~~.(b)),
      x = "Time",
      y = expression( paste(CH[4], " Flux (µmol m"^-2," s"^-1,")"))
    ) +
    
    theme_bw() +
    theme(
      axis.text.x = element_text(angle = 45, hjust = 1)
    )
  
  print(p)
}


```


# ANNUAL EB 
```{r, warning=FALSE}


```

```{r}

# -------------------------------
# Compute net radiation safely
# -------------------------------
df$Rn <- df$LWIN_6_14_1_1_1.c + df$SWIN_6_10_1_1_1.c -
         df$LWOUT_6_15_1_1_1.c - df$SWOUT_6_11_1_1_1.c

# -------------------------------
# Compute SHF safely with fallback
# -------------------------------
# Vectorized row-wise handling
df$shf_avg = rowMeans(
  df[, c("SHF_6_37_1_1_1.c", "SHF_6_37_2_1_1.c")],
  na.rm = TRUE
)

# Replace rows where both SHF were missing
both_missing <- is.na(df$SHF_6_37_1_1_1.c) & is.na(df$SHF_6_37_2_1_1.c)
df$shf_avg[both_missing] = 0  # or df$Rn[both_missing] if you want met = 0 when missing

# -------------------------------
# Compute energy balance
# -------------------------------
df$met <- df$Rn - df$shf_avg
df$flux <- df$H.c + df$LE.c

# -------------------------------
# Fit linear model
# -------------------------------
mod <- lm(flux ~ met, data = df)
summary_mod <- summary(mod)

slope <- coef(mod)["met"]
r2 <- summary_mod$r.squared

cat("Slope:", round(slope,3), "\nR²:", round(r2,3), "\n")

# -------------------------------
# Plot
# -------------------------------
x_lim <- c(-200, 500)
y_lim <- c(-200, 500)

eb_ytd <- ggplot(df, aes(x = met, y = flux)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", color = "blue", se = FALSE) +
  geom_abline(slope = 1, intercept = 0, linetype = "dashed", color = "red") +
  geom_hline(yintercept = 0, linetype = "solid", color = "black") +
  geom_vline(xintercept = 0, linetype = "solid", color = "black") +
  coord_fixed(ratio = 1, xlim = x_lim, ylim = y_lim) +
  labs(
    x = expression("Rn - G  (W m"^-2*")"),
    y = expression("H + LE  (W m"^-2*")"),
    title = "Toolik Full Year Energy Balance"
  ) +
  annotate(
    "text",
    x = max(x_lim), y = min(y_lim),
    label = paste0("Slope = ", round(slope, 3), "\nR² = ", round(r2, 3)),
    hjust = 1.1, vjust = -0.5, size = 4
  ) +
  theme_bw()

# Print plot
eb_ytd


```
# MONTHLY EB

```{r, warning=FALSE}

# Add month column if not already present
if(!"month" %in% names(df)) {
  df <- df %>% mutate(month = as.numeric(format(TIMESTAMP, "%m")))
}

# Filter out NAs
df_plot <- df %>% filter(!is.na(month) & !is.na(flux) & !is.na(met))

# Fit linear model for full year
mod <- lm(flux ~ met, data = df_plot)
summary_mod <- summary(mod)
slope <- coef(mod)["met"]
r2 <- summary_mod$r.squared

cat("Slope:", slope, "\nR²:", r2, "\n")

# Axis limits
x_lim <- c(-200, 500)
y_lim <- c(-200, 500)

# Plot with month coloring
eb_ytd_month <- ggplot(df_plot, aes(x = met, y = flux, color = factor(month))) +
  geom_point(alpha = 0.7) +
  geom_smooth(method = "lm", color = "blue", se = FALSE) +
  geom_abline(slope = 1, intercept = 0, linetype = "dashed", color = "red") +
  geom_hline(yintercept = 0, linetype = "solid", color = "black") +
  geom_vline(xintercept = 0, linetype = "solid", color = "black") +
  coord_fixed(ratio = 1, xlim = x_lim, ylim = y_lim) +
  scale_color_viridis_d(name = "Month") +
  labs(
    x = expression("Rn - G  (W m"^-2*")"),
    y = expression("H + LE  (W m"^-2*")"),
    title = "Toolik Full Year Energy Balance"
  ) +
  annotate(
    "text",
    x = max(x_lim), y = min(y_lim),
    label = paste0("Slope = ", round(slope, 3), "\nR² = ", round(r2, 3)),
    hjust = 1.1, vjust = -0.5, size = 4
  ) +
  theme_bw()

# Print
eb_ytd_month


```
# ANNUAL ENERGY FLUX (ATMOSPHERIC)

```{r, warning=FALSE}

# -------------------------------
# Full-year H & LE plot with smoothing
# -------------------------------
p_flux_full <- ggplot(df) +
  theme_bw() +
  geom_hline(yintercept = 0, linetype = "dashed", color = "black") +

  # Raw lines (slightly transparent)
geom_line(aes(x = TIMESTAMP, y = H.c, color = "H"), linewidth = 0.8, alpha = 0.5) +
geom_line(aes(x = TIMESTAMP, y = LE.c, color = "LE"), linewidth = 0.8, alpha = 0.5) +

# Smoothed lines (fully opaque)
geom_smooth(aes(x = TIMESTAMP, y = H.c, color = "H"), method = "loess",
            span = 0.02, linewidth = 1, se = FALSE, alpha = 1) +
geom_smooth(aes(x = TIMESTAMP, y = LE.c, color = "LE"), method = "loess",
            span = 0.02, linewidth = 1, se = FALSE, alpha = 1)+


  # Colors
  scale_color_manual(
    name = "Flux",
    values = c("H" = "firebrick", "LE" = "dodgerblue3")
  ) +

  # X-axis formatting
  scale_x_datetime(
    date_breaks = "1 month",
    date_labels = "%b"
  ) +

  # Labels
  labs(
    x = "Month",
    y = expression(Flux~"(W/m"^2*")"),
    title = "H & LE — Full Year"
  ) +

  # Theme
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  )

# Print
p_flux_full


```

# ANNUAL LONGWAVE IN/OUT

```{r, warning=FALSE}
# -------------------------------
# Longwave Radiation Plot with Smoothing
# -------------------------------
df_lw <- df %>%
  select(TIMESTAMP, LWIN_6_14_1_1_1.c, LWOUT_6_15_1_1_1.c) %>%
  pivot_longer(
    cols = c(LWIN_6_14_1_1_1.c, LWOUT_6_15_1_1_1.c),
    names_to = "variable",
    values_to = "value"
  )

p_lw <- ggplot(df_lw, aes(x = TIMESTAMP, y = value, color = variable)) +
  geom_line(linewidth = 0.8, alpha = 0.6) +           # raw data
  geom_smooth(
    method = "loess",
    span = 0.02,                                      # small span for sensitive smoothing
    linewidth = 1,
    se = FALSE
  ) +
  scale_color_manual(
    values = c("LWIN_6_14_1_1_1.c" = "firebrick", "LWOUT_6_15_1_1_1.c" = "dodgerblue"),
    labels = c("Incoming LW", "Outgoing LW"),
    name = NULL
  ) +
 scale_y_continuous(
  name = expression(Longwave~Radiation~"(W/m"^2*")"),
  breaks = scales::pretty_breaks(n = 8)
  ) +
  scale_x_datetime(
    date_breaks = "1 month",
    date_labels = "%b"
  ) +
  labs(
    x = "Month",
    title = "Longwave Radiation In/Out"
  ) +
  theme_minimal() +
  theme(
    legend.position = "top",
    axis.text.x = element_text(angle = 45, hjust = 1)
  )

p_lw



```
#ANNUAL SHORTWAVE IN/OUT

```{r, warning=FALSE}
# -------------------------------
# Shortwave Radiation Plot with Smoothing
# -------------------------------
df_sw <- df %>%
  select(TIMESTAMP, SWIN_6_10_1_1_1.c, SWOUT_6_11_1_1_1.c) %>%
  pivot_longer(
    cols = c(SWIN_6_10_1_1_1.c, SWOUT_6_11_1_1_1.c),
    names_to = "variable",
    values_to = "value"
  )

p_sw <- ggplot(df_sw, aes(x = TIMESTAMP, y = value, color = variable)) +
  geom_line(linewidth = 0.8, alpha = 0.6) +           # raw data
  geom_smooth(
    method = "loess",
    span = 0.02,                                      # sensitive smoothing
    linewidth = 1,
    se = FALSE
  ) +
  scale_color_manual(
    values = c("SWIN_6_10_1_1_1.c" = "pink4", "SWOUT_6_11_1_1_1.c" = "dodgerblue4"),
    labels = c("Incoming SW", "Outgoing SW"),
    name = NULL
  ) +
  scale_y_continuous(
    name = expression(Shortwave~Radiation~"(W/m"^2*")"),
    breaks = scales::pretty_breaks(n = 8)
  ) +
  scale_x_datetime(
    date_breaks = "1 month",
    date_labels = "%b"
  ) +
  labs(
    x = "Month",
    title = "Shortwave Radiation In/Out"
  ) +
  theme_minimal() +
  theme(
    legend.position = "top",
    axis.text.x = element_text(angle = 45, hjust = 1)
  )

p_sw


```
# ANNUAL PAR

```{r, warning=FALSE}

# -------------------------------
# 1. Prepare cleaned PAR data
# -------------------------------
df_par_IN  <- df %>% filter(!is.na(PPFD_7_21_1_1_1.c))
df_par_OUT <- df %>% filter(!is.na(PPFDR_7_23_1_1_1.c))

# -------------------------------
# 2. Annual PAR plots with monthly ticks
# -------------------------------

# Incoming PAR
p_par_IN <- ggplot(df_par_IN, aes(x = TIMESTAMP, y = PPFD_7_21_1_1_1.c)) +
  geom_line(alpha = 0.6, color = "forestgreen") +
  geom_smooth(method = "loess", span = 0.01, color = "black", linewidth = 0.7, se = FALSE) +
  scale_y_continuous(
    name = expression(PAR~"(µmol m"^-2~" s"^-1*")"),
    expand = expansion(mult = 0.05)
  ) +
  scale_x_datetime(
    date_breaks = "1 month",
    date_labels = "%b"
  ) +
  labs(
    x = "",
    title = "Annual PAR — In"
  ) +
  theme_minimal() +
  theme(
    axis.title.y = element_text(color = "black"),
    axis.text.x = element_text(angle = 45, hjust = 1)
  )

# Outgoing PAR
p_par_OUT <- ggplot(df_par_OUT, aes(x = TIMESTAMP, y = PPFDR_7_23_1_1_1.c)) +
  geom_line(alpha = 0.6, color = "forestgreen") +
  geom_smooth(method = "loess", span = 0.01, color = "black", linewidth = 0.7, se = FALSE) +
  scale_y_continuous(
    name = expression(PAR~"(µmol m"^-2~" s"^-1*")"),
    expand = expansion(mult = 0.05)
  ) +
  scale_x_datetime(
    date_breaks = "1 month",
    date_labels = "%b"
  ) +
  labs(
    x = "",
    title = "Annual PAR — Out"
  ) +
  theme_minimal() +
  theme(
    axis.title.y = element_text(color = "black"),
    axis.text.x = element_text(angle = 45, hjust = 1)
  )

# -------------------------------
# 3. Display stacked plots
# -------------------------------
p_par_IN / p_par_OUT



```

# ANNUAL GROUND HEAT FLUX 

```{r, warning=FALSE}

df$G = (df$SHF_6_37_1_1_1.c + df$SHF_6_37_2_1_1.c)/2


# -------------------------------
# 4. Plot G (Soil Heat Flux)
# -------------------------------
p2 <- ggplot(df, aes(x = TIMESTAMP)) +
  geom_line(aes(y = G, color = "Soil Heat Flux"), linewidth = 0.7) +
  scale_y_continuous(
    name = expression(Soil~Heat~Flux~(W/m^2)),
    breaks = scales::pretty_breaks(n = 8),
    expand = expansion(mult = 0.05)
  ) +
  scale_color_manual(
    values = c("Soil Heat Flux" = "blue"),
    labels = c("Soil Heat Flux"),
    name = NULL
  ) +
  scale_x_datetime(
    date_breaks = "1 month",
    date_labels = "%b"
  ) +
  labs(
    x = "",
    title = "Soil Heat Flux — Full Year"
  ) +
  theme_minimal() +
  theme(
    axis.title.y = element_text(color = "blue"),
    axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "top"
  )

p2 

```

#ANNUAL AIR T VS SOIL T

```{r, warning=FALSE}

# -------------------------------
# Soil Temperature Plot
# -------------------------------
p_soil <- ggplot(data = df) +
  theme_bw() +
  geom_hline(yintercept = 0, linetype = "dashed", color = "black") +
  geom_line(aes(x = TIMESTAMP, y = TS_2_38_1_1_1.c, color = "8 cm"), linewidth = 0.8) +
  geom_line(aes(x = TIMESTAMP, y = TS_2_38_2_1_1.c, color = "18 cm"), linewidth = 0.8) +
  geom_line(aes(x = TIMESTAMP, y = TS_2_38_23_1_1.c, color = "28 cm"), linewidth = 0.8) +
  scale_color_manual(
    values = c("8 cm" = "blue", "18 cm" = "green", "28 cm" = "gold3"),
    breaks = c("8 cm", "18 cm", "28 cm"),  # enforce order in legend
    name = NULL
  ) +
  scale_x_datetime(
    date_breaks = "1 month",
    date_labels = "%b"
  ) +
  labs(
    x = "",
    y = expression("Temperature ("*degree*C*")"),
    title = "Soil Temperatures"
  ) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "top"
  )

# -------------------------------
# Air Temperature Plot
# -------------------------------
p_air <- ggplot(data = df) +
  theme_bw() +
  geom_hline(yintercept = 0, linetype = "dashed", color = "black") +
  geom_line(aes(x = TIMESTAMP, y = TA_2_1_1_1_1.c), color = "red", linewidth = 0.8) +
  scale_x_datetime(
    date_breaks = "1 month",
    date_labels = "%b"
  ) +
  labs(
    x = "",
    y = expression("Temperature ("*degree*C*")"),
    title = "Air Temperature"
  ) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  )

# -------------------------------
# Stack plots
# -------------------------------
p_soil / p_air



```

#MONTHLY AIR T VS SOIL T

```{r, warning=FALSE}


plot_monthly_soil_air <- function(df, tz = "UTC") {

  months <- sort(unique(df$month))

  for (m in months) {

    df_month <- df %>% filter(month == m)
    if (nrow(df_month) == 0) next

    # -------------------------------
    # Soil Temperature Plot
    # -------------------------------
    p_soil <- ggplot(df_month) +
      theme_bw() +
      geom_hline(yintercept = 0, linetype = "dashed", color = "black") +

      geom_line(
        aes(x = TIMESTAMP, y = TS_2_38_1_1_1.c, color = "8 cm"),
        linewidth = 0.8,
        na.rm = FALSE
      ) +
      geom_line(
        aes(x = TIMESTAMP, y = TS_2_38_2_1_1.c, color = "18 cm"),
        linewidth = 0.8,
        na.rm = FALSE
      ) +
      geom_line(
        aes(x = TIMESTAMP, y = TS_2_38_23_1_1.c, color = "28 cm"),
        linewidth = 0.8,
        na.rm = FALSE
      ) +

      scale_color_manual(
        values = c("8 cm" = "blue", "18 cm" = "green", "28 cm" = "gold3"),
        breaks = c("8 cm", "18 cm", "28 cm"),
        name = NULL
      ) +

      labs(
        x = "",
        y = expression("Temperature ("*degree*C*")"),
        title = paste0("Soil Temperatures — Month ", m)
      ) +
      theme(legend.position = "top")

    # -------------------------------
    # Air Temperature Plot
    # -------------------------------
    p_air <- ggplot(df_month) +
      theme_bw() +
      geom_hline(yintercept = 0, linetype = "dashed", color = "black") +

      geom_line(
        aes(x = TIMESTAMP, y = TA_2_1_1_1_1.c),
        color = "red",
        linewidth = 0.8,
        na.rm = FALSE
      ) +

      labs(
        x = "",
        y = expression("Temperature ("*degree*C*")"),
        title = paste0("Air Temperature — Month ", m)
      )

    # -------------------------------
    # Stack and print
    # -------------------------------
    print(p_soil / p_air)
  }
}

plot_monthly_soil_air(df)


```
# BI WEEKLY AIR T VS SOIL T

```{r, warning=FALSE}

# -------------------------------
# Loop over biweeks
# -------------------------------
for (b in biweeks) {

  df_bw <- df %>% filter(biweek == b)

  # Skip empty biweeks
  if (nrow(df_bw) == 0) next

  # -------------------------------
  # Soil Temperature Plot
  # -------------------------------
  p_soil <- ggplot(df_bw) +
    theme_bw() +
    geom_hline(yintercept = 0, linetype = "dashed", color = "black") +

    geom_line(
      aes(x = TIMESTAMP, y = TS_2_38_1_1_1.c, color = "8 cm"),
      linewidth = 0.8,
      na.rm = FALSE
    ) +
    geom_line(
      aes(x = TIMESTAMP, y = TS_2_38_2_1_1.c, color = "18 cm"),
      linewidth = 0.8,
      na.rm = FALSE
    ) +
    geom_line(
      aes(x = TIMESTAMP, y = TS_2_38_23_1_1.c, color = "28 cm"),
      linewidth = 0.8,
      na.rm = FALSE
    ) +

    scale_color_manual(
      values = c("8 cm" = "blue", "18 cm" = "green", "28 cm" = "gold3"),
      breaks = c("8 cm", "18 cm", "28 cm"),
      name = NULL
    ) +

    scale_x_datetime(
      date_breaks = "1 day",
      date_labels = "%d-%b"
    ) +

    labs(
      x = "",
      y = expression("Temperature ("*degree*C*")"),
      title = paste0("Soil Temperatures — Bi-Week ", b)
    ) +

    theme(
      legend.position = "top",
      axis.text.x = element_text(angle = 45, hjust = 1)
    )

  # -------------------------------
  # Air Temperature Plot
  # -------------------------------
  p_air <- ggplot(df_bw) +
    theme_bw() +
    geom_hline(yintercept = 0, linetype = "dashed", color = "black") +

    geom_line(
      aes(x = TIMESTAMP, y = TA_2_1_1_1_1.c),
      color = "red",
      linewidth = 0.8,
      na.rm = FALSE
    ) +

    scale_x_datetime(
      date_breaks = "1 day",
      date_labels = "%d-%b"
    ) +

    labs(
      x = "",
      y = expression("Temperature ("*degree*C*")"),
      title = paste0("Air Temperature — Bi-Week ", b)
    ) +

    theme(
      axis.text.x = element_text(angle = 45, hjust = 1)
    )

  # -------------------------------
  # Stack and print
  # -------------------------------
  print(p_soil / p_air)
}


```
#SOIL WATER CONTENT

```{r, warning=FALSE}

p_swc <- ggplot(df) +
  geom_line(aes(TIMESTAMP, SWC_12_36_1_1_1.c * 100, 
                color = "8 cm", linetype = "8 cm"), linewidth = 0.8) +
  geom_line(aes(TIMESTAMP, SWC_12_36_2_1_1.c * 100, 
                color = "18 cm", linetype = "18 cm"), linewidth = 0.8) +
  geom_line(aes(TIMESTAMP, SWC_12_36_3_1_1.c * 100, 
                color = "28 cm", linetype = "28 cm"), linewidth = 0.8) +
  scale_y_continuous(
    name = "% VWC", 
    breaks = scales::pretty_breaks(n = 8)   # dynamic axis
  ) +
  scale_color_manual(
    values = c("8 cm" = "darkblue", "18 cm" = "steelblue", "28 cm" = "skyblue"),
    breaks = c("8 cm","18 cm","28 cm"),
    name = NULL  # removes legend title
  ) +
  scale_linetype_manual(
    values = c("8 cm" = "solid", "18 cm" = "solid", "28 cm" = "solid"),
    breaks = c("8 cm","18 cm","28 cm"),
    name = NULL  # removes legend title
  ) +
  scale_x_datetime(
    date_breaks = "1 month",
    date_labels = "%b"  # shows Jan, Feb, Mar, etc.
  ) +
  labs(
    x = "",
    title = "Soil Water Content"
  ) +
  theme_minimal() +
  theme(
    legend.position = "top",
    axis.text.x = element_text(angle = 45, hjust = 1)
  )

p_swc


```


# ANNUAL RELATIVE HUMIDITY

```{r, warning=FALSE}

# -------------------------------
# Relative Humidity Plot with Smoothing
# -------------------------------
p_rh <- ggplot(df, aes(x = TIMESTAMP, y = RH.c)) +
  geom_line(alpha = 0.5, color = "steelblue", linewidth = 0.7) +  # raw line
  geom_smooth(
    method = "loess", 
    span = 0.05,         # smaller span = more sensitive smoothing
    color = "blue", 
    linewidth = 1, 
    se = FALSE
  ) +
  scale_y_continuous(
    name = "Relative Humidity (%)",
    limits = c(0, 100),
    breaks = seq(0, 100, 10)
  ) +
  scale_x_datetime(
    date_breaks = "1 month",
    date_labels = "%b"
  ) +
  labs(
    x = "",
    title = "Relative Humidity"
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  )

p_rh


```


# ANNUAL BAROMETRIC PRESSURE (uncleaned from sonic)


```{r, warning=FALSE}

# -------------------------------
# Air Pressure (Pa -> kPa) plot
# -------------------------------
df_pres <- df %>%
  filter(!is.na(air_pressure)) %>%
  mutate(air_pressure_kpa = air_pressure / 1000)

p_pres <- ggplot(df_pres, aes(x = TIMESTAMP, y = air_pressure_kpa)) +
  geom_line(color = "gray40", alpha = 0.6, linewidth = 0.6) +   # raw data
  geom_smooth(
    method = "loess",
    span = 0.05,
    se = FALSE,
    color = "black",
    linewidth = 1
  ) +
  scale_y_continuous(
    name = "Air Pressure (kPa)",
    breaks = scales::pretty_breaks(n = 8)
  ) +
   scale_x_datetime(
    date_breaks = "1 month",
    date_labels = "%b"
  ) +
  labs(
    x = "",
    title = "Air Pressure"
  ) +
  theme_minimal()

p_pres


```


# ANNUAL AIR TEMP CHECK (HMP VS SONIC)

```{r, warning=FALSE}

# Annual Temperature Plot with Monthly Ticks (no superscripts)
p_annual <- ggplot(df, aes(x = TIMESTAMP)) +
  geom_line(aes(y = TA_2_1_1_1_1.c, color = "Air Temp"), linewidth = 0.8) +
  geom_line(aes(y = sonic_temperature - 273.15, color = "Sonic Temp"), linewidth = 0.8) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "black") +
  scale_color_manual(values = c("Air Temp" = "red", "Sonic Temp" = "blue")) +
  scale_x_datetime(
    date_breaks = "1 month",
    date_labels = "%b"
  ) +
  labs(
    x = "",
    y = expression("Temperature ("*degree*C*")"),
    color = "Sensor",
    title = "Annual Temperature Comparison"
  ) +
  theme_bw() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  )

print(p_annual)

```

# MONTHLY AIR TEMP CHECK (HMP VS SONIC)

```{r, warning=FALSE}
# Ensure month column exists
if(!"month" %in% names(df)) {
  df <- df %>% mutate(month = as.numeric(format(TIMESTAMP, "%m")))
}

# List unique months
months <- sort(unique(df$month))

# Loop: print separate plot for each month
for (m in months) {
  
  df_month <- df %>% filter(month == m)
  
  # Skip empty months
  if (nrow(df_month) == 0) next
  
  p_month <- ggplot(df_month, aes(x = TIMESTAMP)) +
    geom_line(aes(y = TA_2_1_1_1_1.c, color = "Air Temp"), linewidth = 0.8) +
    geom_line(aes(y = sonic_temperature - 273.15, color = "Sonic Temp"), linewidth = 0.8) +
    geom_hline(yintercept = 0, linetype = "dashed", color = "black") +
    scale_color_manual(values = c("Air Temp" = "red", "Sonic Temp" = "blue")) +
    labs(
      x = "",
      y = expression("Temperature ("*degree*C*")"),
      color = "Sensor",
      title = paste0("Temperature Comparison — Month ", m)
    ) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1))
  
  print(p_month)
}

```

# BI WEEKLY AIR TEMP CHECK (HMP VS SONIC)

```{r, warning=FALSE}

df <- df %>%
  arrange(TIMESTAMP) %>%
  mutate(biweek = as.numeric(floor((as.numeric(TIMESTAMP) - min(as.numeric(TIMESTAMP))) / (14*24*3600))) + 1)

biweeks <- sort(unique(df$biweek))
plots <- list()

for (b in biweeks) {
  df_bw <- df %>% filter(biweek == b)
  
  p <- ggplot(df_bw, aes(x = TIMESTAMP)) +
    geom_line(aes(y = TA_2_1_1_1_1.c, color = "Air Temp"), linewidth = 0.8) +
    geom_line(aes(y = sonic_temperature - 273.15, color = "Sonic Temp"), linewidth = 0.8) +
    geom_hline(yintercept = 0, linetype = "dashed", color = "black") +
    scale_color_manual(values = c("Air Temp" = "red", "Sonic Temp" = "blue")) +
    labs(
      x = "",
      y = expression("Temperature ("*degree*C*")"),
      color = "Sensor",
      title = paste(" Bi-Weekly Period:", b)
    ) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1))

  plots[[paste0("temp_biweek_", b)]] <- p
}

# print all biweek plots
for (name in names(plots)) {
  print(plots[[name]])
}


```
# ANNUAL ALBEDO

```{r, warning=FALSE}


# -------------------------------
# 1. Filter cleaned Albedo data
# -------------------------------
df_alb_clean <- df %>% 
  filter(!is.na(ALB_1_1_1.c))  # remove NAs

# -------------------------------
# 2. Annual Albedo plot
# -------------------------------
p_albedo <- ggplot(df_alb_clean, aes(x = TIMESTAMP, y = ALB_1_1_1.c)) +
  geom_line(alpha = 0.6, color = "darkgreen") +  # raw line
  geom_smooth(method = "loess", span = 0.05, color = "black", linewidth = 1.0, se = FALSE) +
  scale_y_continuous(
    name = "Albedo",
    limits = c(0, 1),
    expand = expansion(mult = 0.05)
  ) +
   scale_x_datetime(
    date_breaks = "1 month",
    date_labels = "%b"
  ) +
  labs(
    x = "",
    title = "Annual Albedo"
  ) +
  theme_minimal() +
  theme(
    axis.title.y = element_text(color = "darkgreen")
  )

p_albedo


```
# ANNUAL SNOW DEPTH

```{r, warning=FALSE}
# -------------------------------
# Prepare snow depth
# -------------------------------
df_sd <- df %>%
  filter(!is.na(SD_10_99_1_1_1)) %>%
  mutate(
    SD_cm = (SD_10_99_1_1_1 - (-2.06)) * 10  # adjust and convert to cm
  )

# -------------------------------
# Annual plot of snow depth
# -------------------------------
p_sd_annual <- ggplot(df_sd, aes(x = TIMESTAMP, y = SD_cm)) +
  geom_point(alpha = 0.4, color = "gray") +  # raw data
  geom_smooth(method = "loess", span = 0.051, color = "darkblue", se = FALSE) +  # smooth trend
  scale_y_continuous(name = "Snow Depth (cm)") +
  labs(
    x = "",
    title = "Snow Depth — Annual"
  ) +
   scale_x_datetime(
    date_breaks = "1 month",
    date_labels = "%b"
  ) +
  theme_minimal() +
  theme(
    axis.title.y = element_text(color = "black")
  )

p_sd_annual


```


```{r, warning=FALSE}


```

# ANNUAL WIND

```{r, warning=FALSE}
df_wind_openair <- df %>%
  filter(!is.na(wind_dir) & !is.na(WS_16_33_1_1_1)) %>%
  rename(
    wd = wind_dir,
    ws = WS_16_33_1_1_1
  )

windRose(df_wind_openair,
         ws = "ws",
         wd = "wd",
         paddle = FALSE,
         key = TRUE,
         main = "Toolik")

```

#MONTHLY WIND
```{r, warning=FALSE}

# Prepare wind data
df_wind_openair <- df %>%
  filter(!is.na(wind_dir) & !is.na(WS_16_33_1_1_1)) %>%
  rename(
    wd = wind_dir,
    ws = WS_16_33_1_1_1
  ) %>%
  mutate(month = as.numeric(format(TIMESTAMP, "%m")))

# Unique months
months <- sort(unique(df_wind_openair$month))

# Loop over months and print wind roses
for (m in months) {
  df_month <- df_wind_openair %>% filter(month == m)
  
  windRose(df_month,
           ws = "ws",
           wd = "wd",
           paddle = FALSE,
           key = TRUE,
           main = paste(" Month", m))
}

```

#POTENTIAL RADIATION VS SWIN - TIME ALIGNMENT CHECK
#making monthly diel graphs
```{r, warning=F, echo=FALSE}

df$TIMESTAMP <- as.POSIXct(df$TIMESTAMP, tz = "UTC")

df$year  <- as.numeric(format(df$TIMESTAMP, "%Y"))
df$month <- as.numeric(format(df$TIMESTAMP, "%m"))
df$hour  <- as.numeric(format(df$TIMESTAMP, "%H"))

diel_rad <- df %>%
  group_by(year, month, hour) %>%
  summarise(
    rad_mean  = mean(SWIN_6_10_1_1_1, na.rm = TRUE),
    rad_sd    = sd(SWIN_6_10_1_1_1, na.rm = TRUE),
    rpot_mean = mean(rpot, na.rm = TRUE),
    .groups = "drop"
  )

month_list <- diel_rad %>%
  distinct(year, month) %>%
  arrange(year, month)

for(i in 1:nrow(month_list)) {
  
  y <- month_list$year[i]
  m <- month_list$month[i]
  
  dfm <- diel_rad %>%
    filter(year == y, month == m)
  
  p <- ggplot(dfm) +
    
    # rpot line (like original blue line)
    geom_line(aes(hour, rpot_mean),
              color = "blue",
              linewidth = 0.8) +
    
    # measured radiation mean
    geom_line(aes(hour, rad_mean),
              linetype = 2) +
    
    # variability ribbon
    geom_ribbon(aes(
      x = hour,
      ymin = rad_mean - rad_sd,
      ymax = rad_mean + rad_sd
    ),
    alpha = 0.3) +
    
    scale_x_continuous(breaks = seq(0, 23, by = 3)) +
    
    labs(
      title = format(as.Date(paste(y, m, 1, sep = "-")), "%B %Y"),
      x = "Hour of Day",
      y = "Radiation (W m⁻²)"
    ) +
    
    theme_minimal()
  
  print(p)
}


```


