---
title: "Toolik annual qc check"
author: "Kaj"
date: "2026-01-26"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(error =  TRUE)
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_knit$set(root.dir = 'C:/Users/klynoe/Documents/toolik/R_outputs/flux_met_c/') #use this to set your directory
```


This file generates plots for the annual data checks


```{r, include=FALSE}
# Load packages, cleaned data 

rm(list = ls())

library(data.table)
library(ggplot2)
library(cowplot)
library(openair)
library(plotrix)
library(signal)
library(svMisc)
library(zoo)
library(stringr)
library(plyr)
library(dplyr)
library(patchwork) # formats plots
library(bigleaf) # for radiation check
library(scales)
library(lubridate)
library(tidyr)
library(RColorBrewer)
```

#DATA LOADER AND FLAGS
```{r, include = FALSE}

df <- fread('./toolik_flux_c_met_c_tms_2025_2026.csv')

#df$ts <- df$ts-9*3600 #adjust timezone from UTC to CST
#df$TIMESTAMP <- df$TIMESTAMP-9*3600 #adjust timezone from UTC to CST

df$TIMESTAMP <- as.POSIXct( paste(df$TIMESTAMP, "00:00"), format = "%Y-%m-%d %H:%M", tz = "UTC")


# data formatting for flag plots
# Ensure flags are character first
df$co2_flux.flag <- as.character(df$co2_flux.flag)
df$ch4_flux.flag <- as.character(df$ch4_flux.flag)

# Then assign factor with explicit levels
df$co2_flux.flag <- factor(df$co2_flux.flag, levels = c("0","1","2","3","4","5"))
df$ch4_flux.flag <- factor(df$ch4_flux.flag, levels = c("0","1","2","3","4","5"))

#df$co2_flux.flag <- as.factor(df$co2_flux.flag)
#df$ch4_flux.flag <- as.factor(df$ch4_flux.flag)

color_map = c("0" = "yellow3", "1" = "darkblue" , "2" =  "red4", "3" = "orange", "4" = "green4", "5" = "purple")

```


# Timeseries Plots

Flag = 0, 1, 2 : EP Flag
Flag = 3 : Absolute Limits Filter
Flag = 4 : Rolling MAD Filter
Flag = 5 : Diagnostic filter

# ANNUAL PLOT CO2
```{r, warning=FALSE}
# Flag = 0, 1, 2 : EP Flag
# Flag = 3 : Absolute Limits Filter
# Flag = 4 : Rolling MAD Filter
# Flag = 5 : Diagnostic filter

# -------------------------------
# NEE Plot with Monthly Ticks
# -------------------------------
nee_plot_ytd <- ggplot(data = df) +
  geom_hline(yintercept = 0) +
  geom_point(
    data = subset(df, !is.na(co2_flux.flag)),
    aes(TIMESTAMP, co2_flux, color = co2_flux.flag)
  ) +
  geom_point(aes(TIMESTAMP, co2_flux.c), col = 'black') +
  scale_y_continuous(limits = c(-30, 30)) +
  scale_x_datetime(
    date_breaks = "1 month",
    date_labels = "%b"
  ) +
  labs(
    title = "Toolik",
    x = "Month",
    y = bquote(CO[2]~"Flux ("*mu*"mol m"^-2~"s"^-1*")")
  ) +
  scale_color_manual(values = color_map, name = "Cleaning Flag") +
  theme_bw() +
  theme(
    plot.title = element_text(hjust = 0.5),
    axis.text.x = element_text(angle = 45, hjust = 1)
  )

nee_plot_ytd


```
# MONTHLY CO2

```{r}

# 1. Extract both month and year from TIMESTAMP
df <- df %>% 
  mutate(
    month = as.numeric(format(TIMESTAMP, "%m")),
    year  = as.numeric(format(TIMESTAMP, "%Y"))
  )

# 2. Get unique combinations of year and month, sorted chronologically
time_blocks <- df %>% 
  distinct(year, month) %>% 
  arrange(year, month)

# 3. Loop through each specific year and month combination
for (i in 1:nrow(time_blocks)) {
  current_year  <- time_blocks$year[i]
  current_month <- time_blocks$month[i]
  
  # Filter data for the specific year and month
  df_month <- df %>% 
    filter(year == current_year & month == current_month)
  
  # CRITICAL UPDATE: Skip if column doesn't exist, is empty, or contains ONLY NA values
  if (!"co2_flux.c" %in% names(df_month) || nrow(df_month) == 0 || all(is.na(df_month$co2_flux.c))) {
    next
  }
  
  # Generate the plot
  p <- ggplot(data = df_month) + 
    geom_hline(yintercept = 0) + 
    geom_point(
      data = subset(df_month, !is.na(co2_flux.flag)), 
      aes(TIMESTAMP, co2_flux, color = co2_flux.flag), 
      alpha = 0.7
    ) + 
    geom_point(
      aes(TIMESTAMP, co2_flux.c), 
      color = 'black', 
      alpha = 0.7
    ) + 
    scale_y_continuous(limits = c(-30, 30)) + 
    scale_color_manual(values = color_map, name = "Cleaning Flag") + 
    labs(
      # Updated title to dynamically show both Month and Year
      title = bquote(CO[2]~"Flux — " * .(current_month) * "/" * .(current_year)), 
      x = "Time", 
      y = expression(paste(CO[2], " Flux (µmol m"^-2," s"^-1,")"))
    ) + 
    theme_bw() + 
    theme(
      axis.text.x = element_text(angle = 45, hjust = 1)
    )
  
  print(p)
}

```
#BI WEEKLY CO2

```{r, warning=FALSE}


# 1. Arrange data, extract year, and calculate biweek relative to EACH year's start
df <- df %>% 
  arrange(TIMESTAMP) %>% 
  mutate(year = as.numeric(format(TIMESTAMP, "%Y"))) %>% 
  group_by(year) %>% 
  mutate(
    biweek = as.numeric(floor((as.numeric(TIMESTAMP) - min(as.numeric(TIMESTAMP))) / (14 * 24 * 3600))) + 1
  ) %>% 
  ungroup()

# 2. Get unique combinations of year and biweek, sorted chronologically
time_blocks <- df %>% 
  distinct(year, biweek) %>% 
  arrange(year, biweek)

# 3. Loop: print separate plot for each year and bi-week window
for (i in 1:nrow(time_blocks)) {
  current_year   <- time_blocks$year[i]
  current_biweek <- time_blocks$biweek[i]
  
  # Filter data for this specific year and biweek
  df_bw <- df %>% 
    filter(year == current_year & biweek == current_biweek)
  
  #  Skip if column doesn't exist, is empty, or contains ONLY NA values
  if (!"co2_flux.c" %in% names(df_bw) || nrow(df_bw) == 0 || all(is.na(df_bw$co2_flux.c))) {
    next
  }
  
  p <- ggplot(data = df_bw) + 
    geom_hline(yintercept = 0) + 
    geom_point(
      data = subset(df_bw, !is.na(co2_flux.flag)), 
      aes(TIMESTAMP, co2_flux, color = co2_flux.flag), 
      alpha = 0.7
    ) + 
    geom_point(
      aes(TIMESTAMP, co2_flux.c), 
      color = 'black', 
      alpha = 0.7
    ) + 
    scale_y_continuous(limits = c(-18, 18)) + 
    scale_x_datetime(
      date_breaks = "1 day", 
      date_labels = "%d-%b"
    ) + 
    scale_color_manual(values = color_map, name = "Cleaning Flag") + 
    labs(
      title = bquote(CO[2]~"Flux — " * .(current_year) * " Bi-Week " * .(current_biweek)), 
      x = "Day", 
      y = expression(paste(CO[2], " Flux (µmol m"^-2," s"^-1,")"))
    ) + 
    theme_bw() + 
    theme(
      axis.text.x = element_text(angle = 45, hjust = 1)
    )
  
  print(p)
}



```


#### ANNUAL CH4
```{r, warning=FALSE, echo=FALSE}

# Flag = 0, 1, 2 : EP Flag
# Flag = 3 : Absolute Limits Filter
# Flag = 4 : Rolling MAD Filter
# Flag = 5 : Diagnostic filter

ch4_plot_ytd <- ggplot(data = df) +
  geom_hline(yintercept = 0) +
  
  # QC flagged points
  geom_point(
    data = subset(df, !is.na(ch4_flux.flag)),
    aes(TIMESTAMP, ch4_flux, color = ch4_flux.flag),
    alpha = 0.7
  ) +
  
  # Corrected CH4 points
  geom_point(aes(TIMESTAMP, ch4_flux.c), col = 'black', alpha = 0.7) +
  
  # Y-axis limits
  scale_y_continuous(limits = c(-0.1, 0.33)) +
  
  # X-axis monthly ticks
  scale_x_datetime(
    date_breaks = "1 month",
    date_labels = "%b"
  ) +
  
  # QC color mapping
  scale_color_manual(values = color_map, name = "QC CH4 Flux") +
  
  # Labels
  labs(
    title = "Toolik",
    x = "Month",
    y = bquote(CH[4]~"Flux ("*mu*"mol m"^-2~"s"^-1*")")
  ) +
  
  theme_bw() +
  theme(
    plot.title = element_text(hjust = 0.5),
    axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "right"
  )

ch4_plot_ytd


```

#CH4 MONTHLY

```{r, warning=FALSE}

# 1. Add month and year columns if they are not already present
if (!"month" %in% names(df)) {
  df <- df %>% mutate(month = as.numeric(format(TIMESTAMP, "%m")))
}
if (!"year" %in% names(df)) {
  df <- df %>% mutate(year = as.numeric(format(TIMESTAMP, "%Y")))
}

# 2. Get unique combinations of year and month, sorted chronologically
time_blocks <- df %>% 
  distinct(year, month) %>% 
  arrange(year, month)

# 3. Loop: print separate plot for each year and month combination
for (i in 1:nrow(time_blocks)) {
  current_year  <- time_blocks$year[i]
  current_month <- time_blocks$month[i]
  
  # Filter data for this specific year and month
  df_month <- df %>% 
    filter(year == current_year & month == current_month)
  
  # CRITICAL UPDATE: Skip if column doesn't exist, is empty, or contains ONLY NA values
  if (!"ch4_flux.c" %in% names(df_month) || nrow(df_month) == 0 || all(is.na(df_month$ch4_flux.c))) {
    next
  }
  
  p <- ggplot(data = df_month) + 
    geom_hline(yintercept = 0) + 
    geom_point(
      data = subset(df_month, !is.na(ch4_flux.flag)), 
      aes(TIMESTAMP, ch4_flux, color = ch4_flux.flag), 
      alpha = 0.7
    ) + 
    geom_point(
      aes(TIMESTAMP, ch4_flux.c), 
      color = "black", 
      alpha = 0.7
    ) + 
    # scale_y_continuous(limits = c(-0.1, 0.1)) + 
    scale_color_manual(values = color_map, name = "QC CH4 Flux") + 
    labs(
      # Updated title to explicitly display both Month and Year
      title = bquote(CH[4]~"Flux — " * .(current_month) * "/" * .(current_year)), 
      x = "Time", 
      y = expression(paste(CH[4], " Flux (µmol m"^-2," s"^-1,")"))
    ) + 
    theme_bw() + 
    theme(
      axis.text.x = element_text(angle = 45, hjust = 1)
    )
  
  print(p)
}



```

#BI WEEKLY CH4
```{r, warning=FALSE}

# 1. Arrange data, extract year, and calculate biweek relative to EACH year's start
df <- df %>% 
  arrange(TIMESTAMP) %>% 
  mutate(year = as.numeric(format(TIMESTAMP, "%Y"))) %>% 
  group_by(year) %>% 
  mutate(
    biweek = as.numeric(floor((as.numeric(TIMESTAMP) - min(as.numeric(TIMESTAMP))) / (14 * 24 * 3600))) + 1
  ) %>% 
  ungroup()

# 2. Get unique combinations of year and biweek, sorted chronologically
time_blocks <- df %>% 
  distinct(year, biweek) %>% 
  arrange(year, biweek)

# 3. Loop: print separate plot for each year and bi-week window
for (i in 1:nrow(time_blocks)) {
  current_year   <- time_blocks$year[i]
  current_biweek <- time_blocks$biweek[i]
  
  # Filter data for this specific year and biweek
  df_bw <- df %>% 
    filter(year == current_year & biweek == current_biweek)
  
  # CRITICAL UPDATE: Skip if column doesn't exist, is empty, or contains ONLY NA values
  if (!"ch4_flux.c" %in% names(df_bw) || nrow(df_bw) == 0 || all(is.na(df_bw$ch4_flux.c))) {
    next
  }
  
  p <- ggplot(data = df_bw) + 
    geom_hline(yintercept = 0) + 
    geom_point(
      data = subset(df_bw, !is.na(ch4_flux.flag)), 
      aes(TIMESTAMP, ch4_flux, color = ch4_flux.flag), 
      alpha = 0.7
    ) + 
    geom_point(
      aes(TIMESTAMP, ch4_flux.c), 
      color = "black", 
      alpha = 0.7
    ) + 
    # Daily x-axis ticks
    scale_x_datetime(
      date_breaks = "1 day", 
      date_labels = "%d-%b"
    ) + 
    scale_color_manual(values = color_map, name = "QC CH4 Flux") + 
    labs(
      # Updated title to explicitly display both Year and Bi-Week index
      title = bquote(CH[4]~"Flux — " * .(current_year) * " Bi-Week " * .(current_biweek)), 
      x = "Time", 
      y = expression(paste(CH, " Flux (µmol m"^-2," s"^-1,")"))
    ) + 
    theme_bw() + 
    theme(
      axis.text.x = element_text(angle = 45, hjust = 1)
    )
  
  print(p)
}



```


# ANNUAL EB 
```{r, warning=FALSE}


```

```{r}
# -------------------------------
# Compute net radiation safely
# -------------------------------
df$Rn <- df$LWIN_6_14_1_1_1.c + df$SWIN_6_10_1_1_1.c -
         df$LWOUT_6_15_1_1_1.c - df$SWOUT_6_11_1_1_1.c

# -------------------------------
# Compute SHF safely with fallback
# -------------------------------
# Vectorized row-wise handling
df$shf_avg = rowMeans(
  df[, c("SHF_6_37_1_1_1.c", "SHF_6_37_2_1_1.c")],
  na.rm = TRUE
)

# Replace rows where both SHF were missing
both_missing <- is.na(df$SHF_6_37_1_1_1.c) & is.na(df$SHF_6_37_2_1_1.c)
df$shf_avg[both_missing] = 0  # or df$Rn[both_missing] if you want met = 0 when missing

# -------------------------------
# Compute energy balance
# -------------------------------
df$met <- df$Rn - df$shf_avg
df$flux <- df$H.c + df$LE.c

# -------------------------------
# Fit linear model
# -------------------------------
mod <- lm(flux ~ met, data = df)
summary_mod <- summary(mod)

slope <- coef(mod)["met"]
r2 <- summary_mod$r.squared

cat("Slope:", round(slope,3), "\nR²:", round(r2,3), "\n")

# -------------------------------
# Plot
# -------------------------------
x_lim <- c(-200, 500)
y_lim <- c(-200, 500)

eb_ytd <- ggplot(df, aes(x = met, y = flux)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", color = "blue", se = FALSE) +
  geom_abline(slope = 1, intercept = 0, linetype = "dashed", color = "red") +
  geom_hline(yintercept = 0, linetype = "solid", color = "black") +
  geom_vline(xintercept = 0, linetype = "solid", color = "black") +
  coord_fixed(ratio = 1, xlim = x_lim, ylim = y_lim) +
  labs(
    x = expression("Rn - G  (W m"^-2*")"),
    y = expression("H + LE  (W m"^-2*")"),
    title = "Toolik Full Year Energy Balance"
  ) +
  annotate(
    "text",
    x = max(x_lim), y = min(y_lim),
    label = paste0("Slope = ", round(slope, 3), "\nR² = ", round(r2, 3)),
    hjust = 1.1, vjust = -0.5, size = 4
  ) +
  theme_bw()

# Print plot
eb_ytd

 

```
# MONTHLY EB

```{r, warning=FALSE}

# Add month column if not already present
if (!"month" %in% names(df)) {
  df <- df %>% mutate(month = as.numeric(format(TIMESTAMP, "%m")))
}

# Add year column if not already present
if (!"year" %in% names(df)) {
  df <- df %>% mutate(year = as.numeric(format(TIMESTAMP, "%Y")))
}

# Filter out NAs
df_plot <- df %>% filter(!is.na(month) & !is.na(flux) & !is.na(met) & !is.na(year))

# Get unique years, sorted chronologically
unique_years <- sort(unique(df_plot$year))

# Axis limits
x_lim <- c(-200, 500)
y_lim <- c(-200, 500)

# Loop through each year
for (y in unique_years) {
  
  # Filter data for the specific year
  df_year <- df_plot %>% filter(year == y)
  
  # Skip this year if there are fewer than 3 data points to fit a line
  if (nrow(df_year) < 3) {
    next
  }
  
  # Fit linear model for the specific year
  mod         <- lm(flux ~ met, data = df_year)
  summary_mod <- summary(mod)
  slope       <- coef(mod)["met"]
  r2          <- summary_mod$r.squared
  
  # Print metrics to the console for this year
  cat("\n--- Year:", y, "---", "\nSlope:", slope, "\nR²:", r2, "\n")
  
  # Create plot for this specific year
  eb_ytd_month <- ggplot(df_year, aes(x = met, y = flux, color = factor(month))) + 
    geom_point(alpha = 0.7) + 
    geom_smooth(method = "lm", color = "blue", se = FALSE) + 
    geom_abline(slope = 1, intercept = 0, linetype = "dashed", color = "red") + 
    geom_hline(yintercept = 0, linetype = "solid", color = "black") + 
    geom_vline(xintercept = 0, linetype = "solid", color = "black") + 
    coord_fixed(ratio = 1, xlim = x_lim, ylim = y_lim) + 
    scale_color_viridis_d(name = "Month", drop = FALSE) + # drop = FALSE keeps all calendar months in the legend scale
    labs(
      x = expression("Rn - G (W m"^-2*")"), 
      y = expression("H + LE (W m"^-2*")"), 
      title = paste("Toolik", y, "Energy Balance") # Dynamic year title
    ) + 
    annotate(
      "text", 
      x = max(x_lim), 
      y = min(y_lim), 
      label = paste0("Slope = ", round(slope, 3), "\nR² = ", round(r2, 3)), 
      hjust = 1.1, 
      vjust = -0.5, 
      size = 4
    ) + 
    theme_bw()
  
  # Print the plot for this/each year
  print(eb_ytd_month)
}


```
# ANNUAL ENERGY FLUX (ATMOSPHERIC)

```{r, warning=FALSE}


# 1. Ensure time columns and normalized day-of-year axis exist
df <- df %>%
  arrange(TIMESTAMP) %>% 
  mutate(
    year = as.numeric(format(TIMESTAMP, "%Y")),
    doy_time = as.POSIXct(format(TIMESTAMP, "2000-%m-%d %H:%M:%S"), tz = "UTC")
  )

# 2. Corrected parameter syntax for zoo::rollapply
df <- df %>%
  group_by(year) %>%
  mutate(
    # Changed k to width, and v to FUN
    H.smoothed  = zoo::rollapply(H.c,  width = 48, FUN = mean, na.rm = TRUE, fill = NA, partial = FALSE),
    LE.smoothed = zoo::rollapply(LE.c, width = 48, FUN = mean, na.rm = TRUE, fill = NA, partial = FALSE)
  ) %>%
  ungroup()

# ==============================================================================
# TYPE 1: ONE SEPARATE PLOT PER YEAR
# ==============================================================================
for (y in unique_years) {
  df_year <- df %>% filter(year == y)
  
  if (nrow(df_year %>% filter(!is.na(H.c) | !is.na(LE.c))) < 10) next
  
  p_year <- ggplot(df_year) +
    theme_bw() +
    geom_hline(yintercept = 0, linetype = "dashed", color = "black") +
    # Raw data lines (slightly transparent)
    geom_line(aes(x = TIMESTAMP, y = H.c, color = "H"), linewidth = 0.8, alpha = 0.3) +
    geom_line(aes(x = TIMESTAMP, y = LE.c, color = "LE"), linewidth = 0.8, alpha = 0.3) +
    # Pre-calculated smoothed lines (will naturally break at large NA blocks)
    geom_line(aes(x = TIMESTAMP, y = H.smoothed, color = "H"), linewidth = 1, na.rm = FALSE) +
    geom_line(aes(x = TIMESTAMP, y = LE.smoothed, color = "LE"), linewidth = 1, na.rm = FALSE) +
    scale_color_manual(
      name = "Flux",
      values = c("H" = "firebrick", "LE" = "dodgerblue3")
    ) +
    scale_x_datetime(date_breaks = "1 month", date_labels = "%b") +
    labs(
      x = "Month",
      y = expression(Flux~"(W/m"^2*")"),
      title = paste("H & LE Flux — Year", y)
    ) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1))
  
  print(p_year)
}


# 1. Dynamically build a custom color map for any number of years
# The 'Paired' palette gives us matching pairs (e.g., Light Blue/Dark Blue, Light Green/Dark Green, etc.)
unique_years <- sort(unique(df$year))
num_years    <- length(unique_years)
base_colors  <- brewer.pal(max(3, num_years * 2), "Paired")

# Map each year to a specific pair of colors
custom_colors <- c()
for (idx in 1:num_years) {
  y <- unique_years[idx]
  # Assign the light color to H and the dark color to LE for that year
  custom_colors[paste0(y, "_H")]  <- base_colors[(idx * 2) - 1]
  custom_colors[paste0(y, "_LE")] <- base_colors[idx * 2]
}

# ==============================================================================
# TYPE 2: ALL YEARS COMPARED TOGETHER (REVISED COLOR MAPPING WITH ALPHA)
# ==============================================================================
p_compare_years <- ggplot(df) +
  theme_bw() +
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey50") +
  
  # Added alpha = 0.6 to make the overlapping lines semi-transparent
  geom_line(
    aes(x = doy_time, y = H.smoothed, color = interaction(year, "H", sep = "_")), 
    linewidth = 1, alpha = 0.6, na.rm = FALSE
  ) +
  geom_line(
    aes(x = doy_time, y = LE.smoothed, color = interaction(year, "LE", sep = "_")), 
    linewidth = 1, alpha = 0.6, na.rm = FALSE
  ) +
  
  # Assign our custom pairs palette directly
  scale_color_manual(
    name = "Year & Flux Type",
    values = custom_colors,
    # Clean up legend labels from "2025_H" to "2025 H"
    labels = function(x) gsub("_", " ", x) 
  ) +
  
  # Clean X-axis monthly tracking
  scale_x_datetime(
    date_breaks = "1 month", 
    date_labels = "%b"
  ) +
  labs(
    x = "Month",
    y = expression(Flux~"(W/m"^2*")"),
    title = "H & LE Flux Multi-Year Comparison"
  ) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    legend.key.width = unit(1.2, "cm") # Makes legend easier to distinguish
  )

print(p_compare_years)




```

# ANNUAL LONGWAVE IN/OUT

```{r, warning=FALSE}

# 1. Extract year and calculate rolling averages per column before pivoting
# This ensures that gaps are preserved and smoothing does not bleed across years
df_lw_smooth <- df %>%
  arrange(TIMESTAMP) %>%
  mutate(year = as.numeric(format(TIMESTAMP, "%Y"))) %>%
  group_by(year) %>%
  mutate(
    # width = 48 corresponds to a 24-hour window if data is 30-minute intervals
    LWIN_smooth  = zoo::rollapply(LWIN_6_14_1_1_1.c,  width = 48, FUN = mean, na.rm = TRUE, fill = NA, partial = FALSE),
    LWOUT_smooth = zoo::rollapply(LWOUT_6_15_1_1_1.c, width = 48, FUN = mean, na.rm = TRUE, fill = NA, partial = FALSE)
  ) %>%
  ungroup() %>%
  select(TIMESTAMP, LWIN_6_14_1_1_1.c, LWOUT_6_15_1_1_1.c, LWIN_smooth, LWOUT_smooth)

# 2. Pivot the raw data
df_raw_long <- df_lw_smooth %>%
  select(TIMESTAMP, LWIN_6_14_1_1_1.c, LWOUT_6_15_1_1_1.c) %>%
  pivot_longer(
    cols = c(LWIN_6_14_1_1_1.c, LWOUT_6_15_1_1_1.c),
    names_to = "variable",
    values_to = "value"
  )

# 3. Pivot the smoothed data separately so they can be merged cleanly
df_smooth_long <- df_lw_smooth %>%
  select(TIMESTAMP, LWIN_smooth, LWOUT_smooth) %>%
  pivot_longer(
    cols = c(LWIN_smooth, LWOUT_smooth),
    names_to = "variable",
    values_to = "smoothed_value"
  ) %>%
  # Rename variables to match the raw data for seamless coloring
  mutate(variable = case_when(
    variable == "LWIN_smooth"  ~ "LWIN_6_14_1_1_1.c",
    variable == "LWOUT_smooth" ~ "LWOUT_6_15_1_1_1.c"
  ))

# 4. Join the long dataframes together
df_lw_final <- left_join(df_raw_long, df_smooth_long, by = c("TIMESTAMP", "variable"))

# 5. Plot using geom_line with na.rm = FALSE to force breaks at data gaps
p_lw <- ggplot(df_lw_final, aes(x = TIMESTAMP, color = variable)) +
  theme_minimal() +
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey50") +
  
  # Raw data lines (slightly transparent)
  geom_line(aes(y = value), linewidth = 0.8, alpha = 0.3) + 
  
  # UPDATED: Smooth lines that automatically cut off during data gaps
  geom_line(aes(y = smoothed_value), linewidth = 1, na.rm = FALSE) + 
  
  scale_color_manual(
    values = c("LWIN_6_14_1_1_1.c" = "firebrick", "LWOUT_6_15_1_1_1.c" = "dodgerblue"),
    labels = c("Incoming LW", "Outgoing LW"),
    name = NULL
  ) +
  scale_y_continuous(
    name = expression(Longwave~Radiation~"(W/m"^2*")"),
    breaks = scales::pretty_breaks(n = 8)
  ) +
  scale_x_datetime(
    date_breaks = "1 month",
    date_labels = "%b"
  ) +
  labs(
    x = "Month",
    title = "Longwave Radiation In/Out"
  ) +
  theme(
    legend.position = "top",
    axis.text.x = element_text(angle = 45, hjust = 1)
  )

print(p_lw)



```
#ANNUAL SHORTWAVE IN/OUT

```{r, warning=FALSE}
# 1. Extract year and calculate rolling averages per column before pivoting
df_sw_smooth <- df %>%
  arrange(TIMESTAMP) %>%
  mutate(year = as.numeric(format(TIMESTAMP, "%Y"))) %>%
  group_by(year) %>%
  mutate(
    # width = 48 corresponds to a 24-hour window if data is 30-minute intervals
    # partial = FALSE ensures gaps are preserved with NAs instead of bleeding through
    SWIN_smooth = zoo::rollapply(SWIN_6_10_1_1_1.c, width = 48, FUN = mean, na.rm = TRUE, fill = NA, partial = FALSE),
    SWOUT_smooth = zoo::rollapply(SWOUT_6_11_1_1_1.c, width = 48, FUN = mean, na.rm = TRUE, fill = NA, partial = FALSE)
  ) %>%
  ungroup() %>%
  select(TIMESTAMP, SWIN_6_10_1_1_1.c, SWOUT_6_11_1_1_1.c, SWIN_smooth, SWOUT_smooth)

# 2. Pivot the raw data
df_raw_long_sw <- df_sw_smooth %>%
  select(TIMESTAMP, SWIN_6_10_1_1_1.c, SWOUT_6_11_1_1_1.c) %>%
  pivot_longer(
    cols = c(SWIN_6_10_1_1_1.c, SWOUT_6_11_1_1_1.c),
    names_to = "variable",
    values_to = "value"
  )

# 3. Pivot the smoothed data separately so they can be merged cleanly
df_smooth_long_sw <- df_sw_smooth %>%
  select(TIMESTAMP, SWIN_smooth, SWOUT_smooth) %>%
  pivot_longer(
    cols = c(SWIN_smooth, SWOUT_smooth),
    names_to = "variable",
    values_to = "smoothed_value"
  ) %>%
  # Rename variables to match the raw data for seamless coloring
  mutate(variable = case_when(
    variable == "SWIN_smooth" ~ "SWIN_6_10_1_1_1.c",
    variable == "SWOUT_smooth" ~ "SWOUT_6_11_1_1_1.c"
  ))

# 4. Join the long dataframes together
df_sw_final <- left_join(df_raw_long_sw, df_smooth_long_sw, by = c("TIMESTAMP", "variable"))

# 5. Plot using geom_line with na.rm = FALSE to force breaks at data gaps
p_sw <- ggplot(df_sw_final, aes(x = TIMESTAMP, color = variable)) +
  theme_minimal() +
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey50") +
  
  # Raw data lines (slightly transparent)
  geom_line(aes(y = value), linewidth = 0.8, alpha = 0.3) +
  
  # Smooth lines that automatically cut off during data gaps
  geom_line(aes(y = smoothed_value), linewidth = 1, na.rm = FALSE) +
  
  scale_color_manual(
    values = c("SWIN_6_10_1_1_1.c" = "pink4", "SWOUT_6_11_1_1_1.c" = "dodgerblue4"),
    labels = c("Incoming SW", "Outgoing SW"),
    name = NULL
  ) +
  scale_y_continuous(
    name = expression(Shortwave~Radiation~"(W/m"^2*")"),
    breaks = scales::pretty_breaks(n = 8)
  ) +
  # UPDATED: Added %Y to track year changes chronologically along the axis
  scale_x_datetime(
    date_breaks = "1 month",
    date_labels = "%b %Y"
  ) +
  labs(
    x = "Timeline",
    title = "Shortwave Radiation In/Out"
  ) +
  theme(
    legend.position = "top",
    axis.text.x = element_text(angle = 45, hjust = 1)
  )

print(p_sw)


```
# ANNUAL PAR

```{r, warning=FALSE}

#### =========================================================================

### 1. Extract year and calculate rolling averages per column before pivoting

### =========================================================================

df_par_smooth <- df %>%
arrange(TIMESTAMP) %>%
mutate(year = as.numeric(format(TIMESTAMP, "%Y"))) %>%
group_by(year) %>%
mutate(

### width = 48 corresponds to a 24-hour window if data is 30-minute intervals

### partial = FALSE ensures gaps are preserved with NAs instead of bleeding through

PAR_IN_smooth  = zoo::rollapply(PPFD_7_21_1_1_1.c, width = 48, FUN = mean, na.rm = TRUE, fill = NA, partial = FALSE),
PAR_OUT_smooth = zoo::rollapply(PPFDR_7_23_1_1_1.c, width = 48, FUN = mean, na.rm = TRUE, fill = NA, partial = FALSE)
) %>%
ungroup() %>%
select(TIMESTAMP, PPFD_7_21_1_1_1.c, PPFDR_7_23_1_1_1.c, PAR_IN_smooth, PAR_OUT_smooth)
### =========================================================================

### 2. Pivot the raw data

### =========================================================================

df_raw_long_par <- df_par_smooth %>%
select(TIMESTAMP, PPFD_7_21_1_1_1.c, PPFDR_7_23_1_1_1.c) %>%
pivot_longer(
cols = c(PPFD_7_21_1_1_1.c, PPFDR_7_23_1_1_1.c),
names_to = "variable",
values_to = "value"
)

### =========================================================================

### 3. Pivot the smoothed data separately so they can be merged cleanly

### =========================================================================

df_smooth_long_par <- df_par_smooth %>%
select(TIMESTAMP, PAR_IN_smooth, PAR_OUT_smooth) %>%
pivot_longer(
cols = c(PAR_IN_smooth, PAR_OUT_smooth),
names_to = "variable",
values_to = "smoothed_value"
) %>%

### Rename variables to match the raw data for seamless coloring

mutate(variable = case_when(
variable == "PAR_IN_smooth"  ~ "PPFD_7_21_1_1_1.c",
variable == "PAR_OUT_smooth" ~ "PPFDR_7_23_1_1_1.c"
))

### =========================================================================

### 4. Join the long dataframes together

### =========================================================================

df_par_final <- left_join(df_raw_long_par, df_smooth_long_par, by = c("TIMESTAMP", "variable"))

### =========================================================================

### 5. Plot using geom_line with na.rm = FALSE to force breaks at data gaps

### =========================================================================

p_par <- ggplot(df_par_final, aes(x = TIMESTAMP, color = variable)) +
theme_minimal() +
geom_hline(yintercept = 0, linetype = "dashed", color = "grey50") +

### Raw data lines (slightly transparent)

geom_line(aes(y = value), linewidth = 0.8, alpha = 0.3) +

### Smooth lines that automatically cut off during data gaps

geom_line(aes(y = smoothed_value), linewidth = 1, na.rm = FALSE) +
scale_color_manual(
values = c("PPFD_7_21_1_1_1.c" = "forestgreen", "PPFDR_7_23_1_1_1.c" = "darkorange2"),
labels = c("Incoming PAR", "Outgoing PAR"),
name = NULL
) +
scale_y_continuous(
name = expression(PAR~"(µmol m"^-2~" s"^-1*")"),
breaks = scales::pretty_breaks(n = 8)
) +
scale_x_datetime(
date_breaks = "1 month",
date_labels = "%b %Y"
) +
labs(
x = "Date",
title = " PAR In/Out"
) +
theme(
legend.position = "top",
axis.text.x = element_text(angle = 45, hjust = 1)
)

print(p_par)


```

# ANNUAL GROUND HEAT FLUX 

```{r, warning=FALSE}

### =========================================================================

### 1. Filter Data and Calculate G (Soil Heat Flux) from July 2, 2025 Onward

### =========================================================================

df_filtered <- df %>%

### Trims out all rows prior to July 1, 2025

filter(TIMESTAMP >= as.POSIXct("2025-07-02", tz = "UTC")) %>%
mutate(G = (SHF_6_37_1_1_1.c + SHF_6_37_2_1_1.c) / 2)

### =========================================================================

### 2. Plot G (Soil Heat Flux)

### =========================================================================

p2 <- ggplot(df_filtered, aes(x = TIMESTAMP)) +
geom_line(aes(y = G, color = "Soil Heat Flux"), linewidth = 0.7) +
scale_y_continuous(
name = expression(Soil~Heat~Flux~(W/m^2)),
breaks = scales::pretty_breaks(n = 8),
expand = expansion(mult = 0.05)
) +
scale_color_manual(
values = c("Soil Heat Flux" = "blue"),
labels = c("Soil Heat Flux"),
name = NULL
) +

### Updated date_labels to include %Y since it's no longer a full generic calendar year

scale_x_datetime(
date_breaks = "1 month",
date_labels = "%b %Y"
) +
labs(
x = "",
title = "Soil Heat Flux — Post-Installation"
) +
theme_minimal() +
theme(
axis.title.y = element_text(color = "black"),
axis.text.x = element_text(angle = 45, hjust = 1),
legend.position = "top"
)

p2


```

#ANNUAL AIR T VS SOIL T

```{r, warning=FALSE}

# -------------------------------
# Soil Temperature Plot
# -------------------------------
p_soil <- ggplot(data = df) +
  theme_bw() +
  geom_hline(yintercept = 0, linetype = "dashed", color = "black") +
  geom_line(aes(x = TIMESTAMP, y = TS_2_38_1_1_1.c, color = "8 cm"), linewidth = 0.8) +
  geom_line(aes(x = TIMESTAMP, y = TS_2_38_2_1_1.c, color = "18 cm"), linewidth = 0.8) +
  geom_line(aes(x = TIMESTAMP, y = TS_2_38_2_2_1.c, color = "28 cm"), linewidth = 0.8) +
  scale_color_manual(
    values = c("8 cm" = "blue", "18 cm" = "green", "28 cm" = "gold3"),
    breaks = c("8 cm", "18 cm", "28 cm"),  # enforce order in legend
    name = NULL
  ) +
  scale_x_datetime(
    date_breaks = "1 month",
    date_labels = "%b"
  ) +
  labs(
    x = "",
    y = expression("Temperature ("*degree*C*")"),
    title = "Soil Temperatures"
  ) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "top"
  )

# -------------------------------
# Air Temperature Plot
# -------------------------------
p_air <- ggplot(data = df) +
  theme_bw() +
  geom_hline(yintercept = 0, linetype = "dashed", color = "black") +
  geom_line(aes(x = TIMESTAMP, y = TA_2_1_1_1_1.c), color = "red", linewidth = 0.8) +
  scale_x_datetime(
    date_breaks = "1 month",
    date_labels = "%b"
  ) +
  labs(
    x = "",
    y = expression("Temperature ("*degree*C*")"),
    title = "Air Temperature"
  ) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  )

# -------------------------------
# Stack plots
# -------------------------------
p_soil / p_air



```

#MONTHLY AIR T VS SOIL T

```{r, warning=FALSE}


plot_monthly_soil_air <- function(df, tz = "UTC") {
  
  # 1. Handle sensor name change / historical merge before plotting
  cutoff_date <- as.POSIXct("2026-05-01 00:00:00", tz = tz)
  
  # Ensure the new destination column exists in df, fill with NA if missing
  if (!"TS_2_38_2_2_1" %in% names(df)) {
    df$TS_2_38_2_2_1 <- NA
  }
  
  # Merge data: Use old name before cutoff, new name after cutoff
  # Using if_else handles POSIXct/numeric classes more strictly than ifelse
  df <- df %>%
    mutate(
      TS_2_38_2_2_1 = if_else(TIMESTAMP <= cutoff_date, TS_2_38_23_1_1, TS_2_38_2_2_1)
    )
  
  # 2. Add month and year columns if they are not already present
  if (!"month" %in% names(df)) {
    df <- df %>% mutate(month = as.numeric(format(TIMESTAMP, "%m")))
  }
  if (!"year" %in% names(df)) {
    df <- df %>% mutate(year = as.numeric(format(TIMESTAMP, "%Y")))
  }
  
  # 3. Get unique combinations of year and month, sorted chronologically
  time_blocks <- df %>% 
    distinct(year, month) %>% 
    arrange(year, month)
  
  # 4. Loop through each specific year and month combination
  for (i in 1:nrow(time_blocks)) {
    current_year  <- time_blocks$year[i]
    current_month <- time_blocks$month[i]
    
    # Filter data for this specific year and month
    df_month <- df %>% 
      filter(year == current_year & month == current_month)
    
    # Check if ALL soil and air temperature columns are entirely NA in this block
    # (Updated to check the newly merged TS_2_38_2_2_1 column)
    temp_cols <- c("TS_2_38_1_1_1.c", "TS_2_38_2_1_1.c", "TS_2_38_2_2_1", "TA_2_1_1_1_1.c")
    valid_cols <- intersect(temp_cols, names(df_month))
    
    if (nrow(df_month) == 0 || (length(valid_cols) > 0 && all(sapply(df_month[valid_cols], function(x) all(is.na(x)))))) {
      next
    }
    
    # ------------------------------- 
    # Soil Temperature Plot 
    # ------------------------------- 
    p_soil <- ggplot(df_month) + 
      theme_bw() + 
      geom_hline(yintercept = 0, linetype = "dashed", color = "black") + 
      geom_line(
        aes(x = TIMESTAMP, y = TS_2_38_1_1_1.c, color = "8 cm"), 
        linewidth = 0.8, na.rm = FALSE
      ) + 
      geom_line(
        aes(x = TIMESTAMP, y = TS_2_38_2_1_1.c, color = "18 cm"), 
        linewidth = 0.8, na.rm = FALSE
      ) + 
      # UPDATED: Now plotting the newly consolidated 28 cm column
      geom_line(
        aes(x = TIMESTAMP, y = TS_2_38_2_2_1, color = "28 cm"), 
        linewidth = 0.8, na.rm = FALSE
      ) + 
      scale_color_manual(
        values = c("8 cm" = "blue", "18 cm" = "green", "28 cm" = "gold3"), 
        breaks = c("8 cm", "18 cm", "28 cm"), 
        name = NULL
      ) + 
      labs(
        x = "", 
        y = expression("Temperature ("*degree*C*")"), 
        title = paste0("Soil Temperatures — ", current_month, "/", current_year)
      ) + 
      theme(legend.position = "top")
    
    # ------------------------------- 
    # Air Temperature Plot 
    # ------------------------------- 
    p_air <- ggplot(df_month) + 
      theme_bw() + 
      geom_hline(yintercept = 0, linetype = "dashed", color = "black") + 
      geom_line(
        aes(x = TIMESTAMP, y = TA_2_1_1_1_1.c), 
        color = "red", linewidth = 0.8, na.rm = FALSE
      ) + 
      labs(
        x = "", 
        y = expression("Temperature ("*degree*C*")"), 
        title = paste0("Air Temperature — ", current_month, "/", current_year)
      )
    
    # ------------------------------- 
    # Stack and print 
    # ------------------------------- 
    print(p_soil / p_air)
  }
}


plot_monthly_soil_air(df)



```
# BI WEEKLY AIR T VS SOIL T

```{r, warning=FALSE}

# 1. Handle sensor name change / historical merge before loop
cutoff_date <- as.POSIXct("2026-05-01 00:00:00", tz = "UTC")

if (!"TS_2_38_2_2_1" %in% names(df)) {
  df$TS_2_38_2_2_1 <- NA
}

df <- df %>%
  mutate(
    TS_2_38_2_2_1 = if_else(TIMESTAMP <= cutoff_date, TS_2_38_23_1_1, TS_2_38_2_2_1)
  )

# 2. Arrange data, extract year, and calculate biweek relative to EACH year's start
df <- df %>% 
  arrange(TIMESTAMP) %>% 
  mutate(year = as.numeric(format(TIMESTAMP, "%Y"))) %>% 
  group_by(year) %>% 
  mutate(
    biweek = as.numeric(floor((as.numeric(TIMESTAMP) - min(as.numeric(TIMESTAMP))) / (14 * 24 * 3600))) + 1
  ) %>% 
  ungroup()

# 3. Get unique combinations of year and biweek, sorted chronologically
time_blocks <- df %>% 
  distinct(year, biweek) %>% 
  arrange(year, biweek)

# 4. Loop: print separate stacked plot for each year and bi-week window
for (i in 1:nrow(time_blocks)) {
  current_year   <- time_blocks$year[i]
  current_biweek <- time_blocks$biweek[i]
  
  # Filter data for this specific year and biweek
  df_bw <- df %>% 
    filter(year == current_year & biweek == current_biweek)
  
  # Check if ALL soil and air temperature columns are entirely NA in this block
  temp_cols <- c("TS_2_38_1_1_1.c", "TS_2_38_2_1_1.c", "TS_2_38_2_2_1.c", "TA_2_1_1_1_1.c")
  valid_cols <- intersect(temp_cols, names(df_bw))
  
  if (nrow(df_bw) == 0 || (length(valid_cols) > 0 && all(sapply(df_bw[valid_cols], function(x) all(is.na(x)))))) {
    next
  }
  
  # ------------------------------- 
  # Soil Temperature Plot 
  # ------------------------------- 
  p_soil <- ggplot(df_bw) + 
    theme_bw() + 
    geom_hline(yintercept = 0, linetype = "dashed", color = "black") + 
    geom_line(
      aes(x = TIMESTAMP, y = TS_2_38_1_1_1.c, color = "8 cm"), 
      linewidth = 0.8, na.rm = FALSE
    ) + 
    geom_line(
      aes(x = TIMESTAMP, y = TS_2_38_2_1_1.c, color = "18 cm"), 
      linewidth = 0.8, na.rm = FALSE
    ) + 
    # UPDATED: Now plotting the newly consolidated 28 cm column
    geom_line(
      aes(x = TIMESTAMP, y = TS_2_38_2_2_1, color = "28 cm"), 
      linewidth = 0.8, na.rm = FALSE
    ) + 
    scale_color_manual(
      values = c("8 cm" = "blue", "18 cm" = "green", "28 cm" = "gold3"), 
      breaks = c("8 cm", "18 cm", "28 cm"), 
      name = NULL
    ) + 
    scale_x_datetime(
      date_breaks = "1 day", 
      date_labels = "%d-%b"
    ) + 
    labs(
      x = "", 
      y = expression("Temperature ("*degree*C*")"), 
      title = paste0("Soil Temperatures — ", current_year, " Bi-Week ", current_biweek)
    ) + 
    theme(
      legend.position = "top", 
      axis.text.x = element_text(angle = 45, hjust = 1)
    )
  
  # ------------------------------- 
  # Air Temperature Plot 
  # ------------------------------- 
  p_air <- ggplot(df_bw) + 
    theme_bw() + 
    geom_hline(yintercept = 0, linetype = "dashed", color = "black") + 
    geom_line(
      aes(x = TIMESTAMP, y = TA_2_1_1_1_1.c), 
      color = "red", linewidth = 0.8, na.rm = FALSE
    ) + 
    scale_x_datetime(
      date_breaks = "1 day", 
      date_labels = "%d-%b"
    ) + 
    labs(
      x = "", 
      y = expression("Temperature ("*degree*C*")"), 
      title = paste0("Air Temperature — ", current_year, " Bi-Week ", current_biweek)
    ) + 
    theme(
      axis.text.x = element_text(angle = 45, hjust = 1)
    )
  
  # ------------------------------- 
  # Stack and print 
  # ------------------------------- 
  print(p_soil / p_air)
}



```
#SOIL WATER CONTENT

```{r, warning=FALSE}



# 2. Build the continuous time-series plot
p_swc_timeseries <- ggplot(df) + 
  theme_minimal() +
  
  # Plot all depths over the true, continuous chronological TIMESTAMP axis
  geom_line(aes(x = TIMESTAMP, y = SWC_12_36_1_1_1.c * 100, color = "8 cm"), linewidth = 0.8, na.rm = FALSE) + 
  geom_line(aes(x = TIMESTAMP, y = SWC_12_36_2_1_1.c * 100, color = "18 cm"), linewidth = 0.8, na.rm = FALSE) + 
  geom_line(aes(x = TIMESTAMP, y = SWC_12_36_3_1_1.c * 100, color = "28 cm"), linewidth = 0.8, na.rm = FALSE) + 
  
  # Map colors cleanly to soil depths
  scale_color_manual(
    values = c("8 cm" = "darkblue", "18 cm" = "steelblue", "28 cm" = "skyblue"),
    breaks = c("8 cm", "18 cm", "28 cm"),
    name = NULL # Removes legend title
  ) + 
  
  scale_y_continuous(
    name = "% VWC",
    breaks = scales::pretty_breaks(n = 8)
  ) + 
  
  # Format x-axis to dynamically show month and year over the full timeline
  scale_x_datetime(
    date_breaks = "1 month",
    date_labels = "%b-%Y" # Shows format like 'Jan-2025', 'Mar-2025'
  ) + 
  
  labs(
    x = "Date",
    title = "Soil Water Content"
  ) + 
  theme(
    legend.position = "top",
    axis.text.x = element_text(angle = 45, hjust = 1)
  )

print(p_swc_timeseries)




```


# ANNUAL RELATIVE HUMIDITY

```{r, warning=FALSE}

# 1. Pad timeline across the ENTIRE dataset to prevent artificial year-end breaks
df_rh_smooth <- df %>%
  arrange(TIMESTAMP) %>%
  # Fill timeline gaps seamlessly across all years
  complete(TIMESTAMP = seq(min(TIMESTAMP), max(TIMESTAMP), by = "30 min")) %>%
  mutate(
    # Rolling calculation over the continuous timeline (no group_by)
    RH_smooth = zoo::rollapply(
      RH.c, 
      width = 240,     # 5-day window
      FUN = mean, 
      na.rm = FALSE,   # Breaks smoothing line if actual data gaps exist
      fill = NA, 
      partial = FALSE  
    )
  )

# 2. Relative Humidity Plot with continuous multi-year x-axis
p_rh <- ggplot(df_rh_smooth, aes(x = TIMESTAMP)) + 
  geom_line(aes(y = RH.c), alpha = 0.5, color = "steelblue", linewidth = 0.7) + 
  geom_line(aes(y = RH_smooth), color = "blue", linewidth = 1) + 
  scale_y_continuous(
    name = "Relative Humidity (%)", 
    limits = c(0, 100), 
    breaks = seq(0, 100, 10)
  ) + 
  # Dynamic x-axis formatting for continuous multi-year tracking
  scale_x_datetime(
    date_breaks = "1 month", 
    date_labels = "%b-%Y"  # Formats as 'Jan-2025', 'Feb-2025', etc.
  ) + 
  labs(
    x = "", 
    title = "Relative Humidity"
  ) + 
  theme_minimal() + 
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  )

p_rh




```


# ANNUAL BAROMETRIC PRESSURE 


```{r, warning=FALSE}

# 0. Define the cutoff threshold date
cutoff_date <- as.POSIXct("2026-05-01 00:00:00", tz = "UTC")

# =========================================================================
# 1. Merge Sensors Chronologically and Calculate Deep Rolling Smooth
# =========================================================================
df_pres_smooth <- df %>%
  arrange(TIMESTAMP) %>%
  mutate(
    combined_pressure = ifelse(TIMESTAMP < cutoff_date, air_p_mean.c, PA_4_2_1_1_1.c),
    year = as.numeric(format(TIMESTAMP, "%Y"))
  ) %>%
  group_by(year) %>%
  mutate(
    # UPDATED: width = 336 corresponds to a 7-day window for 30-minute data.
    # Increase this number further if you want an even smoother line (e.g., 672 for 14 days)
    pres_smooth = zoo::rollapply(combined_pressure, width = 336, FUN = mean, na.rm = TRUE, fill = NA, partial = FALSE)
  ) %>%
  ungroup()

# =========================================================================
# 2. Plotting with Gaps Forced (na.rm = FALSE)
# =========================================================================
p_pres <- ggplot(df_pres_smooth, aes(x = TIMESTAMP)) +
  theme_minimal() +
  
  # Raw merged data line (slightly transparent, gray)
  geom_line(aes(y = combined_pressure), color = "gray40", alpha = 0.6, linewidth = 0.6, na.rm = FALSE) +
  
  # Highly smoothed trend line that still drops off during gaps
  geom_line(aes(y = pres_smooth), color = "black", linewidth = 0.8, na.rm = FALSE) +
  
  scale_y_continuous(
    name = "Air Pressure (kPa)",
    breaks = scales::pretty_breaks(n = 8)
  ) +
  scale_x_datetime(
    date_breaks = "1 month",
    date_labels = "%b %Y"
  ) +
  labs(
    x = "",
    title = "Air Pressure"
  ) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  )

print(p_pres)

```


# ANNUAL AIR TEMP CHECK (HMP VS SONIC)

```{r, warning=FALSE}


# Annual Temperature Plot with Monthly Ticks (including Year)
p_annual <- ggplot(df, aes(x = TIMESTAMP)) + 
  geom_line(aes(y = TA_2_1_1_1_1.c, color = "Air Temp"), linewidth = 0.8) + 
  geom_line(aes(y = sonic_temperature - 273.15, color = "Sonic Temp"), linewidth = 0.8) + 
  geom_hline(yintercept = 0, linetype = "dashed", color = "black") + 
  scale_color_manual(values = c("Air Temp" = "red", "Sonic Temp" = "blue")) + 
  # UPDATED: Tracks year changes explicitly across multi-year intervals
  scale_x_datetime(
    date_breaks = "1 month", 
    date_labels = "%b %Y"
  ) + 
  labs(
    x = "", 
    y = expression("Temperature ("*degree*C*")"), 
    color = "Sensor", 
    title = "Annual Temperature Comparison"
  ) + 
  theme_bw() + 
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  )

print(p_annual)


```

# MONTHLY AIR TEMP CHECK (HMP VS SONIC)

```{r, warning=FALSE}

# 1. Ensure clean time extraction columns exist with string names
df <- df %>%
  mutate(
    month      = as.numeric(format(TIMESTAMP, "%m")),
    year       = as.numeric(format(TIMESTAMP, "%Y")),
    month_name = factor(month, levels = 1:12, labels = month.abb)
  )

# 2. Extract a unique list of sequential year-month combinations present in the data
timeline_blocks <- df %>%
  distinct(year, month_name) %>%
  arrange(year, month_name) %>%
  filter(!is.na(month_name))

# 3. Loop: print separate plot for each distinct month-year window
for (i in 1:nrow(timeline_blocks)) {
  current_year  <- timeline_blocks$year[i]
  current_month <- timeline_blocks$month_name[i]
  
  # Filter data for this specific chronological block
  df_month <- df %>% 
    filter(year == current_year, month_name == current_month)
  
  # Skip completely empty months or chunks filled only with NAs
  if (nrow(df_month) == 0 || (all(is.na(df_month$TA_2_1_1_1_1.c)) && all(is.na(df_month$sonic_temperature)))) {
    next
  }
  
  # Create plot
  p_month <- ggplot(df_month, aes(x = TIMESTAMP)) +
    geom_line(aes(y = TA_2_1_1_1_1.c, color = "Air Temp"), linewidth = 0.8) +
    geom_line(aes(y = sonic_temperature - 273.15, color = "Sonic Temp"), linewidth = 0.8) +
    geom_hline(yintercept = 0, linetype = "dashed", color = "black") +
    scale_color_manual(values = c("Air Temp" = "red", "Sonic Temp" = "blue")) +
    # Force the isolated x-axis labels to match the current month-year format
    scale_x_datetime(
      date_breaks = "1 week",
      date_labels = "%b %d, %Y"
    ) +
    labs(
      x = "",
      y = expression("Temperature ("*degree*C*")"),
      color = "Sensor",
      title = paste0("Temperature Comparison — ", current_month, " ", current_year)
    ) +
    theme_bw() +
    theme(
      axis.text.x = element_text(angle = 45, hjust = 1),
      legend.position = "top"
    )
  
  print(p_month)
}


```

# BI WEEKLY AIR TEMP CHECK (HMP VS SONIC)

```{r, warning=FALSE}

# 1. Arrange chronologically and calculate 14-day grouping blocks
df <- df %>% 
  arrange(TIMESTAMP) %>% 
  mutate(biweek = as.numeric(floor((as.numeric(TIMESTAMP) - min(as.numeric(TIMESTAMP))) / (14 * 24 * 3600))) + 1)

biweeks <- sort(unique(df$biweek))
plots <- list()

# 2. Loop through each 14-day window block
for (b in biweeks) {
  df_bw <- df %>% filter(biweek == b)
  
  # Skip completely empty time segments or segments filled only with NAs
  if (nrow(df_bw) == 0 || (all(is.na(df_bw$TA_2_1_1_1_1.c)) && all(is.na(df_bw$sonic_temperature)))) {
    next
  }
  
  # Extract the calendar dates for the start and end of this specific bi-weekly window
  start_date_str <- format(min(df_bw$TIMESTAMP), "%b %d, %Y")
  end_date_str   <- format(max(df_bw$TIMESTAMP), "%b %d, %Y")
  
  # Create a descriptive title showing the actual time span
  window_title <- paste0("Temperature Comparison: ", start_date_str, " — ", end_date_str)
  
  # Build the isolated plot
  p <- ggplot(df_bw, aes(x = TIMESTAMP)) + 
    geom_line(aes(y = TA_2_1_1_1_1.c, color = "Air Temp"), linewidth = 0.8) + 
    geom_line(aes(y = sonic_temperature - 273.15, color = "Sonic Temp"), linewidth = 0.8) + 
    geom_hline(yintercept = 0, linetype = "dashed", color = "black") + 
    scale_color_manual(values = c("Air Temp" = "red", "Sonic Temp" = "blue")) + 
    # High-resolution time axis tailored for 2-week spans
    scale_x_datetime(
      date_breaks = "2 days",
      date_labels = "%b %d"
    ) +
    labs(
      x = "", 
      y = expression("Temperature ("*degree*C*")"), 
      color = "Sensor", 
      title = window_title,
      subtitle = paste("Bi-Weekly Window Period Index:", b)
    ) + 
    theme_bw() + 
    theme(
      axis.text.x = element_text(angle = 45, hjust = 1),
      legend.position = "top"
    )
  
  # Save the plot object into the tracking array environment
  plots[[paste0("temp_biweek_", b)]] <- p
}

# =========================================================================
# 3. Print Validated Plots
# =========================================================================
for (name in names(plots)) {
  print(plots[[name]])
}



```
# ANNUAL ALBEDO

```{r, warning=FALSE}


# =========================================================================
# 1. Prepare Data and Calculate Rolling Smooth Within Years
# =========================================================================
df_alb_smooth <- df %>%
  arrange(TIMESTAMP) %>%
  mutate(year = as.numeric(format(TIMESTAMP, "%Y"))) %>%
  group_by(year) %>%
  mutate(
    # width = 48 corresponds to a 24-hour window if data is 30-minute intervals
    # partial = FALSE ensures gaps are preserved with NAs instead of bleeding through
    alb_smooth = zoo::rollapply(ALB_1_1_1.c, width = 336, FUN = mean, na.rm = TRUE, fill = NA, partial = FALSE)
  ) %>%
  ungroup()

# =========================================================================
# 2. Annual Albedo Plot with Visual Breaks For Missing Blocks
# =========================================================================
p_albedo <- ggplot(df_alb_smooth, aes(x = TIMESTAMP)) +
  theme_minimal() +
  
  # Raw data line (slightly transparent, darkgreen, breaks at gaps)
  geom_line(aes(y = ALB_1_1_1.c), alpha = 0.6, color = "darkgreen", na.rm = FALSE) +
  
  # Smoothed trend line (black, breaks at gaps)
  geom_line(aes(y = alb_smooth), color = "black", linewidth = 0.8, na.rm = FALSE) +
  
  scale_y_continuous(
    name = "Albedo",
    limits = c(0, 1),
    expand = expansion(mult = 0.05)
  ) +
  # UPDATED: Tracks year changes explicitly across multi-year intervals
  scale_x_datetime(
    date_breaks = "1 month",
    date_labels = "%b %Y"
  ) +
  labs(
    x = "",
    title = "Annual Albedo"
  ) +
  theme(
    axis.title.y = element_text(color = "darkgreen"),
    axis.text.x = element_text(angle = 45, hjust = 1)
  )

print(p_albedo)


```
# ANNUAL SNOW DEPTH

```{r, warning=FALSE, include=FALSE}
# -------------------------------
# Prepare snow depth
# -------------------------------
df_sd <- df %>%
  filter(!is.na(SD_10_99_1_1_1)) %>%
  mutate(
    SD_cm = (SD_10_99_1_1_1 - (-2.06)) * 10  # adjust and convert to cm
  )

# -------------------------------
# Annual plot of snow depth
# -------------------------------
p_sd_annual <- ggplot(df_sd, aes(x = TIMESTAMP, y = SD_cm)) +
  geom_point(alpha = 0.4, color = "gray") +  # raw data
  geom_smooth(method = "loess", span = 0.051, color = "darkblue", se = FALSE) +  # smooth trend
  scale_y_continuous(name = "Snow Depth (cm)") +
  labs(
    x = "",
    title = "Snow Depth — Annual"
  ) +
   scale_x_datetime(
    date_breaks = "1 month",
    date_labels = "%b"
  ) +
  theme_minimal() +
  theme(
    axis.title.y = element_text(color = "black")
  )

p_sd_annual


```


```{r, warning=FALSE}


```

# ANNUAL WIND

```{r, warning=FALSE}

## 1. Prepare wind data safely by overwriting the existing 'date' column
df_wind_openair <- df %>% 
  filter(!is.na(wind_dir) & !is.na(WS_16_33_1_1_1)) %>% 
  # Overwrite 'date' column with TIMESTAMP so openair can use it for year grouping
  mutate(date = TIMESTAMP) %>% 
  rename(
    wd = wind_dir, 
    ws = WS_16_33_1_1_1
  )

# 2. Generate wind rose panel broken down by individual years
windRose(
  df_wind_openair, 
  ws = "ws", 
  wd = "wd", 
  type = "year",    # Automatically splits and charts wind roses by year
  paddle = FALSE, 
  key = TRUE, 
  main = "Toolik"
)



```

#MONTHLY WIND
```{r, warning=FALSE}

## 1. Prepare wind data safely by updating the 'date' tracker vector
df_wind_openair <- df %>% 
  filter(!is.na(wind_dir) & !is.na(WS_16_33_1_1_1)) %>% 
  mutate(
    date = TIMESTAMP, # Overwrites old date column safely to avoid rename crashes
    month = as.numeric(format(TIMESTAMP, "%m")),
    year = as.numeric(format(TIMESTAMP, "%Y")),
    month_name = factor(month, levels = 1:12, labels = month.abb)
  ) %>% 
  rename(
    wd = wind_dir, 
    ws = WS_16_33_1_1_1
  )

# 2. Extract a unique list of sequential year-month blocks
wind_blocks <- df_wind_openair %>%
  distinct(year, month_name) %>%
  arrange(year, month_name) %>%
  filter(!is.na(month_name))

# 3. Loop over blocks and generate separate, year-specific monthly wind roses
for (i in 1:nrow(wind_blocks)) {
  current_year  <- wind_blocks$year[i]
  current_month <- wind_blocks$month_name[i]
  
  # Filter data for this specific chronological block
  df_month <- df_wind_openair %>% 
    filter(year == current_year, month_name == current_month)
  
  # Skip months with no rows or insufficient data rows
  if (nrow(df_month) < 2) next
  
  # Print the individualized chart
  windRose(
    df_month, 
    ws = "ws", 
    wd = "wd", 
    paddle = FALSE, 
    key = TRUE, 
    main = paste0("Toolik Wind Rose — ", current_month, " ", current_year)
  )
}

```

#SONIC VS. YOUNG
```{r, warning=F, echo=FALSE}


# Filter out missing rows and calculate the absolute difference between the two wind variables
df_wind_clean <- df %>% 
  filter(!is.na(WS_16_33_1_1_1) & !is.na(wind_speed)) %>%
  mutate(
    # Dynamic metric combining both variables into a unique color value per point
    wind_difference = abs(WS_16_33_1_1_1 - wind_speed),
    year = as.numeric(format(TIMESTAMP, "%Y")),
    month = as.numeric(format(TIMESTAMP, "%m")),
    month_name = factor(month, levels = 1:12, labels = month.abb)
  )

# Plot 1: Grand 1:1 Comparison colored by variable divergence
p_overall <- ggplot(df_wind_clean, aes(x = wind_speed, y = WS_16_33_1_1_1, color = wind_difference)) +
  geom_point(alpha = 0.5) +
  geom_abline(intercept = 0, slope = 1, linetype = "dashed", color = "black", linewidth = 1) +
  # Gradient scale: dark blue when they match perfectly, shifting to bright red as they diverge
  scale_color_viridis_c(option = "plasma", name = "Absolute\nDifference (m/s)") +
  labs(
    title = "Overall Wind Speed 1:1 Comparison",
    subtitle = paste("n =", nrow(df_wind_clean), "observations"),
    x = "wind_speed (m/s)",
    y = "WS_16_33_1_1_1 (m/s)"
  ) +
  theme_bw() +
  coord_equal() +
  theme(legend.position = "right")

print(p_overall)

years_list <- sort(unique(df_wind_clean$year))

# Loop: Print separate 1:1 plot for each year
for (yr in years_list) {
  df_year <- df_wind_clean %>% filter(year == yr)
  
  if (nrow(df_year) == 0) next
  
  p_year <- ggplot(df_year, aes(x = wind_speed, y = WS_16_33_1_1_1, color = wind_difference)) +
    geom_point(alpha = 0.6) +
    geom_abline(intercept = 0, slope = 1, linetype = "dashed", color = "black", linewidth = 1) +
    scale_color_viridis_c(option = "plasma", name = "Difference (m/s)") +
    labs(
      title = paste("Wind Speed 1:1 Comparison — Year:", yr),
      subtitle = paste("n =", nrow(df_year)),
      x = "wind_speed (m/s)",
      y = "WS_16_33_1_1_1 (m/s)"
    ) +
    theme_bw() +
    coord_equal()
  
  print(p_year)
}

# Get unique chronological blocks
ym_blocks <- df_wind_clean %>%
  distinct(year, month_name) %>%
  arrange(year, month_name)

# Loop: Print separate 1:1 plot for each month/year block
for (i in 1:nrow(ym_blocks)) {
  current_year  <- ym_blocks$year[i]
  current_month <- ym_blocks$month_name[i]
  
  df_month <- df_wind_clean %>% 
    filter(year == current_year, month_name == current_month)
  
  # Skip if there's fewer than 2 points to plot
  if (nrow(df_month) < 2) next
  
  p_month <- ggplot(df_month, aes(x = wind_speed, y = WS_16_33_1_1_1, color = wind_difference)) +
    geom_point(alpha = 0.7) +
    geom_abline(intercept = 0, slope = 1, linetype = "dashed", color = "black", linewidth = 1) +
    scale_color_viridis_c(option = "plasma", name = "Difference (m/s)") +
    labs(
      title = paste("Wind Speed 1:1 —", current_month, current_year),
      subtitle = paste("n =", nrow(df_month)),
      x = "wind_speed (m/s)",
      y = "WS_16_33_1_1_1 (m/s)"
    ) +
    theme_bw() +
    coord_equal()
  
  print(p_month)
}


```
#POTENTIAL RADIATION VS SWIN - TIME ALIGNMENT CHECK
#making monthly diel graphs
```{r, warning=F, echo=FALSE}

df$TIMESTAMP <- as.POSIXct(df$TIMESTAMP, tz = "UTC")

df$year  <- as.numeric(format(df$TIMESTAMP, "%Y"))
df$month <- as.numeric(format(df$TIMESTAMP, "%m"))
df$hour  <- as.numeric(format(df$TIMESTAMP, "%H"))

diel_rad <- df %>%
  group_by(year, month, hour) %>%
  summarise(
    rad_mean  = mean(SWIN_6_10_1_1_1, na.rm = TRUE),
    rad_sd    = sd(SWIN_6_10_1_1_1, na.rm = TRUE),
    rpot_mean = mean(rpot, na.rm = TRUE),
    .groups = "drop"
  )

month_list <- diel_rad %>%
  distinct(year, month) %>%
  arrange(year, month)

for(i in 1:nrow(month_list)) {
  
  y <- month_list$year[i]
  m <- month_list$month[i]
  
  dfm <- diel_rad %>%
    filter(year == y, month == m)
  
  p <- ggplot(dfm) +
    
    # rpot line (like original blue line)
    geom_line(aes(hour, rpot_mean),
              color = "blue",
              linewidth = 0.8) +
    
    # measured radiation mean
    geom_line(aes(hour, rad_mean),
              linetype = 2) +
    
    # variability ribbon
    geom_ribbon(aes(
      x = hour,
      ymin = rad_mean - rad_sd,
      ymax = rad_mean + rad_sd
    ),
    alpha = 0.3) +
    
    scale_x_continuous(breaks = seq(0, 23, by = 3)) +
    
    labs(
      title = format(as.Date(paste(y, m, 1, sep = "-")), "%B %Y"),
      x = "Hour of Day",
      y = "Radiation (W m⁻²)"
    ) +
    
    theme_minimal()
  
  print(p)
}


```

#TOMST ANNUAL

```{r, warning=F, echo=FALSE}


# 1. Parse timestamps safely
cutoff   <- as.POSIXct("2025-08-04 00:00:00", tz = "UTC")
end_date <- as.POSIXct("2026-08-11 23:59:59", tz = "UTC")

df_filtered <- df %>%
  mutate(TIMESTAMP_true = as.POSIXct(TIMESTAMP, tz = "UTC")) %>%
  filter(TIMESTAMP_true >= cutoff & TIMESTAMP_true <= end_date)

# Common styling variables
lbl_y_temp <- expression("Temperature ("*degree*C*")")
lbl_y_vwc  <- expression("Soil Moisture VWC (m"^3*"/m"^3*")")
color_map  <- c(
  "Center" = "black", 
  "East"   = "firebrick", 
  "West"   = "dodgerblue4", 
  "North"  = "forestgreen", 
  "South"  = "gold3"
)

# =========================================================================
# PLOT 1: +15cm Air Temperature Horizon
# =========================================================================
# Filter out rows where all loggers are NA for this specific depth
df_p1 <- df_filtered %>% 
  filter(!is.na(TMS_C_T_1) | !is.na(TMS_E_T_1) | !is.na(TMS_W_T_1) | !is.na(TMS_N_T_1) | !is.na(TMS_S_T_1))

p1 <- ggplot(df_p1, aes(x = TIMESTAMP_true)) +
  theme_minimal() +
  geom_hline(yintercept = 0, color = "black", linewidth = 0.8, linetype = "dashed") +
  geom_line(aes(y = TMS_C_T_1, color = "Center"), linewidth = 0.7, na.rm = FALSE) +
  geom_line(aes(y = TMS_E_T_1, color = "East"),   linewidth = 0.7, na.rm = FALSE) +
  geom_line(aes(y = TMS_W_T_1, color = "West"),   linewidth = 0.7, na.rm = FALSE) +
  geom_line(aes(y = TMS_N_T_1, color = "North"),  linewidth = 0.7, na.rm = FALSE) +
  geom_line(aes(y = TMS_S_T_1, color = "South"),  linewidth = 0.7, na.rm = FALSE) +
  scale_color_manual(values = color_map, name = "Logger Station") +
  scale_x_datetime(limits = c(cutoff, end_date), date_breaks = "1 month", date_labels = "%b %Y") +
  labs(x = "Timeline", y = lbl_y_temp, title = "TMS Network Profile Comparison: +15cm Air Horizon") +
  theme(legend.position = "bottom", axis.text.x = element_text(angle = 45, hjust = 1), title = element_text(face = "bold"))

print(p1)

# =========================================================================
# PLOT 2: 0cm Ground Surface Temperature Horizon
# =========================================================================
df_p2 <- df_filtered %>% 
  filter(!is.na(TMS_C_T_2) | !is.na(TMS_E_T_2) | !is.na(TMS_W_T_2) | !is.na(TMS_N_T_2) | !is.na(TMS_S_T_2))

p2 <- ggplot(df_p2, aes(x = TIMESTAMP_true)) +
  theme_minimal() +
  geom_hline(yintercept = 0, color = "black", linewidth = 0.8, linetype = "dashed") +
  geom_line(aes(y = TMS_C_T_2, color = "Center"), linewidth = 0.7, na.rm = FALSE) +
  geom_line(aes(y = TMS_E_T_2, color = "East"),   linewidth = 0.7, na.rm = FALSE) +
  geom_line(aes(y = TMS_W_T_2, color = "West"),   linewidth = 0.7, na.rm = FALSE) +
  geom_line(aes(y = TMS_N_T_2, color = "North"),  linewidth = 0.7, na.rm = FALSE) +
  geom_line(aes(y = TMS_S_T_2, color = "South"),  linewidth = 0.7, na.rm = FALSE) +
  scale_color_manual(values = color_map, name = "Logger Station") +
  scale_x_datetime(limits = c(cutoff, end_date), date_breaks = "1 month", date_labels = "%b %Y") +
  labs(x = "Timeline", y = lbl_y_temp, title = "TMS Network Profile Comparison: 0cm Ground Surface Horizon") +
  theme(legend.position = "bottom", axis.text.x = element_text(angle = 45, hjust = 1), title = element_text(face = "bold"))

print(p2)

# =========================================================================
# PLOT 3: -10cm Soil Temperature Horizon
# =========================================================================
df_p3 <- df_filtered %>% 
  filter(!is.na(TMS_C_T_3) | !is.na(TMS_E_T_3) | !is.na(TMS_W_T_3) | !is.na(TMS_N_T_3) | !is.na(TMS_S_T_3))

p3 <- ggplot(df_p3, aes(x = TIMESTAMP_true)) +
  theme_minimal() +
  geom_hline(yintercept = 0, color = "black", linewidth = 0.8, linetype = "dashed") +
  geom_line(aes(y = TMS_C_T_3, color = "Center"), linewidth = 0.7, na.rm = FALSE) +
  geom_line(aes(y = TMS_E_T_3, color = "East"),   linewidth = 0.7, na.rm = FALSE) +
  geom_line(aes(y = TMS_W_T_3, color = "West"),   linewidth = 0.7, na.rm = FALSE) +
  geom_line(aes(y = TMS_N_T_3, color = "North"),  linewidth = 0.7, na.rm = FALSE) +
  geom_line(aes(y = TMS_S_T_3, color = "South"),  linewidth = 0.7, na.rm = FALSE) +
  scale_color_manual(values = color_map, name = "Logger Station") +
  scale_x_datetime(limits = c(cutoff, end_date), date_breaks = "1 month", date_labels = "%b %Y") +
  labs(x = "Timeline", y = lbl_y_temp, title = "TMS Network Profile Comparison: -10cm Soil Temperature Horizon") +
  theme(legend.position = "bottom", axis.text.x = element_text(angle = 45, hjust = 1), title = element_text(face = "bold"))

print(p3)

# =========================================================================
# PLOT 4: -10cm Soil Moisture Horizon (VWC)
# =========================================================================
df_p4 <- df_filtered %>% 
  filter(!is.na(TMS_C_VWC) | !is.na(TMS_E_VWC) | !is.na(TMS_W_VWC) | !is.na(TMS_N_VWC) | !is.na(TMS_S_VWC))

p4 <- ggplot(df_p4, aes(x = TIMESTAMP_true)) +
  theme_minimal() +
  geom_line(aes(y = TMS_C_VWC, color = "Center"), linewidth = 0.7, na.rm = FALSE) +
  geom_line(aes(y = TMS_E_VWC, color = "East"),   linewidth = 0.7, na.rm = FALSE) +
  geom_line(aes(y = TMS_W_VWC, color = "West"),   linewidth = 0.7, na.rm = FALSE) +
  geom_line(aes(y = TMS_N_VWC, color = "North"),  linewidth = 0.7, na.rm = FALSE) +
  geom_line(aes(y = TMS_S_VWC, color = "South"),  linewidth = 0.7, na.rm = FALSE) +
  scale_color_manual(values = color_map, name = "Logger Station") +
  scale_x_datetime(limits = c(cutoff, end_date), date_breaks = "1 month", date_labels = "%b %Y") +
  labs(x = "Timeline", y = lbl_y_vwc, title = "TMS Network Profile Comparison: -10cm Soil Moisture Horizon (VWC)") +
  theme(legend.position = "bottom", axis.text.x = element_text(angle = 45, hjust = 1), title = element_text(face = "bold"))

print(p4)


```

#TOMST MONTHLY

```{r, warning=F, echo=FALSE}

# 1. Parse timestamps safely and extract chronological blocks
df_time <- df %>%
  mutate(
    TIMESTAMP_true = as.POSIXct(TIMESTAMP, tz = "UTC"),
    year = as.numeric(format(TIMESTAMP_true, "%Y")),
    month = as.numeric(format(TIMESTAMP_true, "%m")),
    month_name = factor(month, levels = 1:12, labels = month.abb)
  )

# Get unique year-month blocks present across your entire dataframe
timeline_blocks <- df_time %>%
  distinct(year, month_name) %>%
  arrange(year, month_name) %>%
  filter(!is.na(month_name))

# Common styling variables
lbl_y_temp <- expression("Temperature ("*degree*C*")")
lbl_y_vwc  <- expression("Soil Moisture VWC (m"^3*"/m"^3*")")
color_map  <- c(
  "Center" = "black", 
  "East"   = "firebrick", 
  "West"   = "dodgerblue4", 
  "North"  = "forestgreen", 
  "South"  = "gold3"
)

# =========================================================================
# LOOP THROUGH EACH YEAR & MONTH BLOCK INDIVIDUALLY
# =========================================================================
for (i in 1:nrow(timeline_blocks)) {
  current_year  <- timeline_blocks$year[i]
  current_month <- timeline_blocks$month_name[i]
  
  # Filter master dataset down to the single month block
  df_month <- df_time %>% 
    filter(year == current_year, month_name == current_month)
  
  # -------------------------------------------------------------------------
  # HORIZON 1: +15cm Air Temperature
  # -------------------------------------------------------------------------
  df_p1 <- df_month %>% 
    filter(!is.na(TMS_C_T_1) | !is.na(TMS_E_T_1) | !is.na(TMS_W_T_1) | !is.na(TMS_N_T_1) | !is.na(TMS_S_T_1))
  
  # SAFEGUARD: Skip plotting completely if the month contains no row records
  if (nrow(df_p1) >= 2) {
    p1 <- ggplot(df_p1, aes(x = TIMESTAMP_true)) +
      theme_minimal() +
      geom_hline(yintercept = 0, color = "black", linewidth = 0.8, linetype = "dashed") +
      geom_line(aes(y = TMS_C_T_1, color = "Center"), linewidth = 0.7, na.rm = FALSE) +
      geom_line(aes(y = TMS_E_T_1, color = "East"),   linewidth = 0.7, na.rm = FALSE) +
      geom_line(aes(y = TMS_W_T_1, color = "West"),   linewidth = 0.7, na.rm = FALSE) +
      geom_line(aes(y = TMS_N_T_1, color = "North"),  linewidth = 0.7, na.rm = FALSE) +
      geom_line(aes(y = TMS_S_T_1, color = "South"),  linewidth = 0.7, na.rm = FALSE) +
      scale_color_manual(values = color_map, name = "Logger Station") +
      scale_x_datetime(date_breaks = "1 week", date_labels = "%b %d, %Y") +
      labs(x = "", y = lbl_y_temp, title = paste("TMS Network: +15cm Air Horizon —", current_month, current_year)) +
      theme(legend.position = "bottom", axis.text.x = element_text(angle = 45, hjust = 1), title = element_text(face = "bold"))
    
    print(p1)
  }

  # -------------------------------------------------------------------------
  # HORIZON 2: 0cm Ground Surface Temperature
  # -------------------------------------------------------------------------
  df_p2 <- df_month %>% 
    filter(!is.na(TMS_C_T_2) | !is.na(TMS_E_T_2) | !is.na(TMS_W_T_2) | !is.na(TMS_N_T_2) | !is.na(TMS_S_T_2))
  
  if (nrow(df_p2) >= 2) {
    p2 <- ggplot(df_p2, aes(x = TIMESTAMP_true)) +
      theme_minimal() +
      geom_hline(yintercept = 0, color = "black", linewidth = 0.8, linetype = "dashed") +
      geom_line(aes(y = TMS_C_T_2, color = "Center"), linewidth = 0.7, na.rm = FALSE) +
      geom_line(aes(y = TMS_E_T_2, color = "East"),   linewidth = 0.7, na.rm = FALSE) +
      geom_line(aes(y = TMS_W_T_2, color = "West"),   linewidth = 0.7, na.rm = FALSE) +
      geom_line(aes(y = TMS_N_T_2, color = "North"),  linewidth = 0.7, na.rm = FALSE) +
      geom_line(aes(y = TMS_S_T_2, color = "South"),  linewidth = 0.7, na.rm = FALSE) +
      scale_color_manual(values = color_map, name = "Logger Station") +
      scale_x_datetime(date_breaks = "1 week", date_labels = "%b %d, %Y") +
      labs(x = "", y = lbl_y_temp, title = paste("TMS Network: 0cm Surface Horizon —", current_month, current_year)) +
      theme(legend.position = "bottom", axis.text.x = element_text(angle = 45, hjust = 1), title = element_text(face = "bold"))
    
    print(p2)
  }

  # -------------------------------------------------------------------------
  # HORIZON 3: -10cm Soil Temperature
  # -------------------------------------------------------------------------
  df_p3 <- df_month %>% 
    filter(!is.na(TMS_C_T_3) | !is.na(TMS_E_T_3) | !is.na(TMS_W_T_3) | !is.na(TMS_N_T_3) | !is.na(TMS_S_T_3))
  
  if (nrow(df_p3) >= 2) {
    p3 <- ggplot(df_p3, aes(x = TIMESTAMP_true)) +
      theme_minimal() +
      geom_hline(yintercept = 0, color = "black", linewidth = 0.8, linetype = "dashed") +
      geom_line(aes(y = TMS_C_T_3, color = "Center"), linewidth = 0.7, na.rm = FALSE) +
      geom_line(aes(y = TMS_E_T_3, color = "East"),   linewidth = 0.7, na.rm = FALSE) +
      geom_line(aes(y = TMS_W_T_3, color = "West"),   linewidth = 0.7, na.rm = FALSE) +
      geom_line(aes(y = TMS_N_T_3, color = "North"),  linewidth = 0.7, na.rm = FALSE) +
      geom_line(aes(y = TMS_S_T_3, color = "South"),  linewidth = 0.7, na.rm = FALSE) +
      scale_color_manual(values = color_map, name = "Logger Station") +
      scale_x_datetime(date_breaks = "1 week", date_labels = "%b %d, %Y") +
      labs(x = "", y = lbl_y_temp, title = paste("TMS Network: -10cm Soil Temp Horizon —", current_month, current_year)) +
      theme(legend.position = "bottom", axis.text.x = element_text(angle = 45, hjust = 1), title = element_text(face = "bold"))
    
    print(p3)
  }

  # -------------------------------------------------------------------------
  # HORIZON 4: -10cm Soil Moisture (VWC)
  # -------------------------------------------------------------------------
  df_p4 <- df_month %>% 
    filter(!is.na(TMS_C_VWC) | !is.na(TMS_E_VWC) | !is.na(TMS_W_VWC) | !is.na(TMS_N_VWC) | !is.na(TMS_S_VWC))
  
  if (nrow(df_p4) >= 2) {
    p4 <- ggplot(df_p4, aes(x = TIMESTAMP_true)) +
      theme_minimal() +
      geom_line(aes(y = TMS_C_VWC, color = "Center"), linewidth = 0.7, na.rm = FALSE) +
      geom_line(aes(y = TMS_E_VWC, color = "East"),   linewidth = 0.7, na.rm = FALSE) +
      geom_line(aes(y = TMS_W_VWC, color = "West"),   linewidth = 0.7, na.rm = FALSE) +
      geom_line(aes(y = TMS_N_VWC, color = "North"),  linewidth = 0.7, na.rm = FALSE) +
      geom_line(aes(y = TMS_S_VWC, color = "South"),  linewidth = 0.7, na.rm = FALSE) +
      scale_color_manual(values = color_map, name = "Logger Station") +
      scale_x_datetime(date_breaks = "1 week", date_labels = "%b %d, %Y") +
      labs(x = "", y = lbl_y_vwc, title = paste("TMS Network: -10cm Soil Moisture Horizon (VWC) —", current_month, current_year)) +
      theme(legend.position = "bottom", axis.text.x = element_text(angle = 45, hjust = 1), title = element_text(face = "bold"))
    
    print(p4)
  }
}



```