---
title: "monthly_met_qc_TOOLIK"
author: "Kaj"
date: "2026-06-08"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  message = FALSE,
  error = TRUE
)

rm(list = ls())

library(data.table)
library(ggplot2)
library(dplyr)
library(lubridate)
library(zoo)
library(openair)
library(patchwork)
library(scales)
library(tidyr)
library(bigleaf)
```

# Load Data

```{r}
df <- fread(
  "C:/Users/klynoe/Documents/toolik/R_outputs/met/flux_met_c_202605.csv"
)

df$TIMESTAMP <- as.POSIXct(
  paste(df$TIMESTAMP, "00:00"),
  format = "%Y-%m-%d %H:%M",
  tz = "UTC"
)

full_time <- data.frame(
  TIMESTAMP = seq(
    min(df$TIMESTAMP),
    max(df$TIMESTAMP),
    by = "30 mins"
  )
)

df <- merge(
  full_time,
  df,
  by = "TIMESTAMP",
  all.x = TRUE
)
```

# Derived Variables

```{r}
df$G <- (
  df$SHF_6_37_1_1_1.c +
  df$SHF_6_37_2_1_1.c
)/2


df$Rn <-
  df$LWIN_6_14_1_1_1.c +
  df$SWIN_6_10_1_1_1.c -
  df$LWOUT_6_15_1_1_1.c -
  df$SWOUT_6_11_1_1_1.c

df <- df %>%
  mutate(
    across(
      c(
        SWC_12_36_1_1_1.c,
        SWC_12_36_2_1_1.c,
        SWC_12_36_3_1_1.c
      ),
      ~ .x * 100
    )
  )
```

# Monthly Subset

```{r}
month_start <- "2026-05-01"

make_week_index <- function(df){

  start_month <- as.POSIXct(
    format(min(df$TIMESTAMP),
           "%Y-%m-01 00:00"),
    tz = "UTC"
  )

  df$week_in_month <- floor(
    as.numeric(
      difftime(
        df$TIMESTAMP,
        start_month,
        units = "days"
      )
    ) / 7
  ) + 1

  df
}

df_month <- subset(
  df,
  TIMESTAMP >= as.POSIXct(
    month_start,
    tz = "UTC"
  )
)

df_month <- make_week_index(df_month)
```

# Functions

```{r}
break_gaps <- function(
  df,
  ts_col,
  value_col,
  max_gap_minutes = 90
){

  df <- df[order(df[[ts_col]]), ]

  dt <- as.numeric(
    difftime(
      df[[ts_col]],
      dplyr::lag(df[[ts_col]]),
      units = "mins"
    )
  )

  gap <- dt > max_gap_minutes
  gap[is.na(gap)] <- FALSE

  df[[value_col]][gap] <- NA

  df
}
```

```{r}
plot_met_single <- function(
  df,
  variable,
  ylab,
  title,
  color = "blue"
){

  df <- break_gaps(
    df,
    "TIMESTAMP",
    variable
  )

  ggplot(
    df,
    aes(
      TIMESTAMP,
      .data[[variable]]
    )
  ) +
    geom_line(
      color = color
    ) +
    theme_minimal() +
    labs(
      x = "",
      y = ylab,
      title = title
    )
}
```

```{r}
plot_met_long <- function(
  df,
  cols,
  labels,
  colors,
  ylab,
  title
){

  dfl <- pivot_longer(
    df,
    all_of(cols),
    names_to = "variable",
    values_to = "value"
  )

  dfl$variable <- factor(
    dfl$variable,
    levels = cols,
    labels = labels
  )

  ggplot(
    dfl,
    aes(
      TIMESTAMP,
      value,
      color = variable
    )
  ) +
    geom_line() +
    scale_color_manual(
      values = colors
    ) +
    theme_minimal() +
    labs(
      x = "",
      y = ylab,
      title = title,
      color = NULL
    )
}
```

# Air Temperature

## Monthly

```{r}
plot_met_single(
  df_month,
  "TA_2_1_1_1_1.c",
  "Air Temperature (°C)",
  "Monthly Air Temperature",
  "red"
)
```

## Weekly

```{r}
for(w in sort(unique(df_month$week_in_month))){

  p <- plot_met_single(
    subset(
      df_month,
      week_in_month == w
    ),
    "TA_2_1_1_1_1.c",
    "Air Temperature (°C)",
    paste(
      "Week",
      w,
      "Air Temperature"
    ),
    "red"
  )

  print(p)
}
```

# Relative Humidity

```{r}
plot_met_single(
  df_month,
  "RH.c",
  "RH (%)",
  "Relative Humidity",
  "steelblue"
)
```

# Air Pressure

```{r}
plot_met_single(
  df_month,
  "PA_4_2_1_1_1.c",
  "Pressure (kPa)",
  "Air Pressure",
  "black"
)
```

# Shortwave Radiation

```{r}
plot_met_long(
  df_month,
  c(
    "SWIN_6_10_1_1_1.c",
    "SWOUT_6_11_1_1_1.c"
  ),
  c(
    "Incoming",
    "Outgoing"
  ),
  c(
    "orange",
    "blue"
  ),
  expression(W~m^-2),
  "Shortwave Radiation"
)
```

# Longwave Radiation

```{r}
plot_met_long(
  df_month,
  c(
    "LWIN_6_14_1_1_1.c",
    "LWOUT_6_15_1_1_1.c"
  ),
  c(
    "Incoming",
    "Outgoing"
  ),
  c(
    "red",
    "blue"
  ),
  expression(W~m^-2),
  "Longwave Radiation"
)
```

# Net Radiation

```{r}
plot_met_single(
  df_month,
  "Rn",
  expression(Net~Radiation~(W~m^-2)),
  "Net Radiation"
)
```

# PAR

```{r}
plot_met_long(
  df_month,
  c(
    "PPFD_7_21_1_1_1.c",
    "PPFDR_7_23_1_1_1.c"
  ),
  c(
    "Incoming",
    "Reflected"
  ),
  c(
    "darkgreen",
    "green"
  ),
  expression(mu*mol~m^-2~s^-1),
  "PAR"
)
```

# Albedo

```{r}
plot_met_single(
  df_month,
  "ALB_1_1_1.c",
  "Albedo",
  "Albedo",
  "cyan4"
)
```

# Soil Moisture

```{r}
plot_met_long(
  df_month,
  c(
    "SWC_12_36_1_1_1.c",
    "SWC_12_36_2_1_1.c",
    "SWC_12_36_3_1_1.c"
  ),
  c(
    "8 cm",
    "18 cm",
    "28 cm"
  ),
  c(
    "blue",
    "green",
    "gold3"
  ),
  "Soil Moisture (%)",
  "Soil Moisture"
)
```

# Soil Temperature

```{r}
plot_met_long(
  df_month,
  c(
    "TS_2_38_1_1_1.c",
    "TS_2_38_2_1_1.c",
    "TS_2_38_23_1_1.c"
  ),
  c(
    "8 cm",
    "18 cm",
    "28 cm"
  ),
  c(
    "blue",
    "green",
    "gold3"
  ),
  "Soil Temperature (°C)",
  "Soil Temperature"
)
```

# Soil Heat Flux

```{r}
plot_met_long(
  df_month,
  cols = c(
    "G",
    "SHF_6_37_1_1_1.c",
    "SHF_6_37_2_1_1.c"
  ),
  labels = c(
    "G",
    "SHF 1",
    "SHF 2"
  ),
  colors = c(
    "black",
    "blue",
    "red"
  ),
  ylab = expression(Soil~Heat~Flux~(W~m^-2)),
  title = "Soil Heat Flux"
)
```


# Wind Rose

```{r}
df_wind <- df_month

df_wind <- df_wind[
  !is.na(df_wind$WD_20_35_1_1_1) &
  !is.na(df_wind$WS_16_33_1_1_1),
]

names(df_wind)[names(df_wind) == "WD_20_35_1_1_1"] <- "wd"
names(df_wind)[names(df_wind) == "WS_16_33_1_1_1"] <- "ws"

windRose(
  df_wind,
  ws = "ws",
  wd = "wd",
  paddle = FALSE,
  key = TRUE
)
```
Create potential radiation dataset
```{r,error = FALSE}


mindate <- min(df$TIMESTAMP, na.rm = TRUE)
maxdate <- max(df$TIMESTAMP, na.rm = TRUE)

TIMESTAMP <- seq(
  from = mindate,
  to = maxdate,
  by = "30 min"
)

JD <- as.numeric(format(TIMESTAMP, "%j"))
h  <- as.numeric(format(TIMESTAMP, "%H"))
m  <- as.numeric(format(TIMESTAMP, "%M"))

H <- h + ifelse(m == 30, 0.5, 0)

rpot_vals <- potential.radiation(doy = JD,hour = H,latDeg = 68.5272,longDeg = -149.5491,timezone = -9,useSolartime = T)*1.1

rpot_df <- data.frame(
  TIMESTAMP = TIMESTAMP,
  rpot = as.numeric(rpot_vals)
)

df <- merge(
  df,
  rpot_df,
  by = "TIMESTAMP",
  all.x = TRUE
)

stopifnot("rpot" %in% names(df))

```


One to one plot for check
```{r}

df$radflag <- ifelse(df$SWIN_6_10_1_1_1 > df$rpot, 1, 0)
```
# Radiation Timing Check

#POTENTIAL RADIATION VS SWIN - TIME ALIGNMENT CHECK
#making monthly diel graphs


```{r, warning=F, echo=FALSE}


df$year  <- year(df$TIMESTAMP)
df$month <- month(df$TIMESTAMP)
df$hour  <- hour(df$TIMESTAMP)

diel_rad <- df %>%
  dplyr::group_by(year, month, hour) %>%
  dplyr::summarise(
    rad_mean  = mean(SWIN_6_10_1_1_1.c, na.rm = TRUE),
    rad_sd    = sd(SWIN_6_10_1_1_1.c, na.rm = TRUE),
    rpot_mean = mean(rpot, na.rm = TRUE),
    .groups = "drop"
  )

month_list <- diel_rad %>%
  dplyr::distinct(year, month) %>%
  dplyr::arrange(year, month)

for(i in seq_len(nrow(month_list))) {

  y <- month_list$year[i]
  m <- month_list$month[i]

  dfm <- diel_rad %>%
    dplyr::filter(year == y, month == m)

  p <- ggplot(dfm, aes(hour)) +
    geom_ribbon(
      aes(
        ymin = rad_mean - rad_sd,
        ymax = rad_mean + rad_sd
      ),
      alpha = 0.3
    ) +
    geom_line(aes(y = rad_mean), linetype = 2) +
    geom_line(aes(y = rpot_mean), linewidth = 0.8) +
    scale_x_continuous(breaks = seq(0, 23, 3)) +
    labs(
      title = paste(month.name[m], y),
      x = "Hour",
      y = expression(Radiation~(W~m^-2))
    ) +
    theme_minimal()

  print(p)
}

```

