---
title: "Toolik Monthly Flux QC"

output:
  html_document:
    code_folding: hide
    toc: true
    toc_float: true
params:
  year:
    value: 2025  # change year !
  month:
    value: 8  # you need to change the month number !
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(error =  TRUE)
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = 'C:/Users/klynoe/Documents/toolik/R_outputs/met_and_flux') #use this to set your directory
```



```{r, include=FALSE}
# Load packages, cleaned data 

#rm(list = ls())

library(data.table)
library(ggplot2)
library(cowplot)
library(openair)
library(plotrix)
library(signal)
library(svMisc)
library(zoo)
library(stringr)
library(plyr)
library(dplyr)
library(patchwork) # formats plots
library(bigleaf) # for radiation check
library(scales)
library(lubridate)
library(tidyr)
library(openair)
setwd('C:/Users/klynoe/Documents/toolik/R_outputs/met_and_flux')


```


```{r, include = FALSE}

year <- params$year
month <- params$month

month_name <- sprintf("%04d_%02d", year, month)

input_file <- file.path(as.character(year), paste0(sprintf("%04d%02d", year, month), "_C.csv"))

df <- fread(input_file)

df$TIMESTAMP <- as.POSIXct( paste(df$TIMESTAMP, "00:00"), format = "%Y-%m-%d %H:%M", tz = "UTC")

full_time <- data.frame(
  TIMESTAMP = seq(min(df$TIMESTAMP),
                  max(df$TIMESTAMP),
                  by = "30 mins")
)

df <- merge(full_time, df, by = "TIMESTAMP", all.x = TRUE)


# data formatting for flag plots
# Ensure flags are character first
df$co2_flux.flag <- as.character(df$co2_flux.flag)
df$ch4_flux.flag <- as.character(df$ch4_flux.flag)
df$H.flag <- as.character(df$H.flag)
df$LE.flag <- as.character(df$LE.flag)


# Then assign factor with explicit levels
df$co2_flux.flag <- factor(df$co2_flux.flag, levels = c("0","1","2","3","4","5"))
df$ch4_flux.flag <- factor(df$ch4_flux.flag, levels = c("0","1","2","3","4","5"))

df$H.flag <- factor(df$H.flag, levels = c("0","1","2","3","4","5"))
df$LE.flag <- factor(df$LE.flag, levels = c("0","1","2","3","4","5"))

#df$co2_flux.flag <- as.factor(df$co2_flux.flag)
#df$ch4_flux.flag <- as.factor(df$ch4_flux.flag)


```

#ADD SENSOR MAPPER - needs work or skip
```{r, echo=F}

#source("C:/Users/klynoe/Documents/pp github reps/toolik_cleaning_processing/toolik_cleaning/toolik_sensor_mapper.R")

#df <- translate_soil_sensors(df)

```
df <- translate_soil_sensors(df)

# Add any calculations that you want to keep throughout (make sure to adjust accordingly to site)
```{r, warning=FALSE, include=FALSE}

df$G = (df$SHF_6_37_1_1_1.c + df$SHF_6_37_2_1_1.c)/2  # SOIL HEAT FLUX

df <- df %>% mutate(SD_cm = ifelse(is.na(SD_10_99_1_1_1.c),NA,
      (SD_10_99_1_1_1.c ) * 100 ))  # adjust and convert from m to cm - SNOW DEPTH

df <- df %>% mutate(sonic_c = sonic_temperature - 273.15) # - SONIC TEMP

#df <- df %>% filter(!is.na(air_pressure)) %>% mutate(air_pressure_kpa = air_pressure / 1000) # -SONIC PRESSURE


df$Rn <- df$LWIN_6_14_1_1_1.c + df$SWIN_6_10_1_1_1.c -      # Compute net radiation 
         df$LWOUT_6_15_1_1_1.c - df$SWOUT_6_11_1_1_1.c


df$shf_avg = rowMeans(
  df[, c("SHF_6_37_1_1_1.c", "SHF_6_37_2_1_1.c")],     # Compute SHF safely with fallback 
  na.rm = TRUE
)

df <- df %>%
  mutate(across(c(SWC_12_36_1_1_1.c, SWC_12_36_2_1_1.c, SWC_12_36_3_1_1.c), ~ .x * 100))   # convert to %

# Standardize air pressure across sensor change
df$air_pressure <- ifelse(
  df$TIMESTAMP < as.POSIXct("2026-04-28 01:30:00", tz = "UTC"),
  df$air_p_mean.c,
  df$PA_4_2_1_1_1.c
)

```


#WEEK / BIWEEK INDEX

```{R, echo = F}
# ============================================================
# WEEK + BIWEEK INDEX
# ============================================================

make_week_index <- function(df, time_col = "TIMESTAMP") {

  start_month <- as.POSIXct(
    format(
      min(df[[time_col]], na.rm = TRUE),
      "%Y-%m-01 00:00"
    ),
    tz = "UTC"
  )

  df$week_in_month <- floor(
    as.numeric(
      difftime(
        df[[time_col]],
        start_month,
        units = "days"
      )
    ) / 7
  ) + 1

  df
}


make_biweek_index <- function(df, time_col = "TIMESTAMP") {

  start_month <- as.POSIXct(
    format(
      min(df[[time_col]], na.rm = TRUE),
      "%Y-%m-01 00:00"
    ),
    tz = "UTC"
  )

  df$biweek_in_month <- floor(
    as.numeric(
      difftime(
        df[[time_col]],
        start_month,
        units = "days"
      )
    ) / 14
  ) + 1

  df
}


# Apply BOTH indices
df_month <- make_week_index(df)
df_month <- make_biweek_index(df_month)

```

#FLUX PLOTTER

```{r, echo=F}

plot_flux <- function(df, flux_base,
                      y_label,
                      ylims = NULL,
                      title = NULL,
                      site = NULL,
                      focus_90 = FALSE) {

  flux      <- flux_base
  flux_c    <- paste0(flux_base, ".c")
  flux_flag <- paste0(flux_base, ".flag")

  df$.__flux__      <- df[[flux]]
  df$.__flux_c__    <- df[[flux_c]]
  df$.__flux_flag__ <- df[[flux_flag]]

  # ------------------------------------------------------------
  # QC flag colors and labels
  # ------------------------------------------------------------

  color_map <- c(
    "0" = "yellow3",
    "1" = "darkblue",
    "2" = "red4",
    "3" = "orange",
    "4" = "green4",
    "5" = "purple"
  )

  flag_labels <- c(
    "0" = "0 - EP Flag",
    "1" = "1 - EP Flag",
    "2" = "2 - EP Flag",
    "3" = "3 - Absolute Limits Filter",
    "4" = "4 - Rolling MAD Filter",
    "5" = "5 - Diagnostics"
  )

  if (is.null(ylims)) {

  all_values <- c(df$.__flux__, df$.__flux_c__)
  all_values <- all_values[is.finite(all_values)]

  if (length(all_values) > 0) {

    if (focus_90) {

      # Central 90% of the data
      ylims <- quantile(
        all_values,
        probs = c(0.05, 0.95),
        na.rm = TRUE
      )

    } else {

      # Full spread of the data
      ylims <- range(all_values)

    }

    # 5% padding
    y_pad <- diff(ylims) * 0.05

    if (y_pad == 0) {
      y_pad <- max(abs(ylims[1]) * 0.05, 1)
    }

    ylims <- c(
      ylims[1] - y_pad,
      ylims[2] + y_pad
    )
  }
}

  plot_title <- if (!is.null(site) && !is.null(title)) {
    paste(site, "-", title)
  } else if (!is.null(site)) {
    site
  } else {
    title
  }

  ggplot(df) +
    geom_hline(yintercept = 0) +

    geom_point(
      aes(
        TIMESTAMP,
        .__flux__,
        color = .__flux_flag__
      ),
      na.rm = TRUE
    ) +

    geom_point(
      aes(
        TIMESTAMP,
        .__flux_c__
      ),
      color = "black",
      na.rm = TRUE
    ) +

    scale_y_continuous(
      limits = ylims
    ) +

    labs(
      title = plot_title,
      x = NULL,
      y = y_label
    ) +

    scale_color_manual(
      values = color_map,
      labels = flag_labels,
      breaks = names(color_map),
      name = "Cleaning Flag",
      na.translate = FALSE
    ) +

    theme_bw()
}

```

#WEEKLY PLOTTER

```{r, echo=F}

# ============================================================
# WEEKLY FLUX PLOTTER
# ============================================================

plot_week_flux <- function(df, week_num,
                           flux_base,
                           y_label,
                           ylims = NULL,
                           site = "Toolik") {

  flux_col <- flux_base
  flux_c_col <- paste0(flux_base, ".c")

  # Check requested columns exist
  if (!flux_col %in% names(df) &&
      !flux_c_col %in% names(df)) {
    return(NULL)
  }

  dfw <- subset(
    df,
    week_in_month == week_num
  )

  # No rows
  if (nrow(dfw) == 0) {
    return(NULL)
  }

  # Check for actual data
  raw_has_data <- FALSE
  clean_has_data <- FALSE

  if (flux_col %in% names(dfw)) {
    raw_has_data <- any(is.finite(dfw[[flux_col]]))
  }

  if (flux_c_col %in% names(dfw)) {
    clean_has_data <- any(is.finite(dfw[[flux_c_col]]))
  }

  # No actual data -> no plot
  if (!raw_has_data && !clean_has_data) {
    return(NULL)
  }

  plot_flux(
    dfw,
    flux_base,
    y_label = y_label,
    ylims = ylims,
    title = paste("Week", week_num),
    site = site
  )
}

```
#BIWEEK FLUX PLOTTER

```{R, echo = F}
# ============================================================
# BIWEEK FLUX PLOTTER
# ============================================================

plot_biweek_flux <- function(df, biweek_num,
                             flux_base,
                             y_label,
                             ylims = NULL,
                             site = "Toolik") {

  flux_col <- flux_base
  flux_c_col <- paste0(flux_base, ".c")

  if (!flux_col %in% names(df) &&
      !flux_c_col %in% names(df)) {
    return(NULL)
  }

  dfbw <- subset(
    df,
    biweek_in_month == biweek_num
  )

  if (nrow(dfbw) == 0) {
    return(NULL)
  }

  raw_has_data <- FALSE
  clean_has_data <- FALSE

  if (flux_col %in% names(dfbw)) {
    raw_has_data <- any(is.finite(dfbw[[flux_col]]))
  }

  if (flux_c_col %in% names(dfbw)) {
    clean_has_data <- any(is.finite(dfbw[[flux_c_col]]))
  }

  if (!raw_has_data && !clean_has_data) {
    return(NULL)
  }

  plot_flux(
    dfbw,
    flux_base,
    y_label = y_label,
    ylims = ylims,
    title = paste("Biweek", biweek_num),
    site = site
  )
}

```

```{R, echo =F}
# ============================================================
# PLOT BUILDERS
# ============================================================

# Break lines across large timestamp gaps
break_gaps <- function(df, ts_col, value_col, max_gap_minutes = 90) {

  df <- df[order(df[[ts_col]]), ]

  dt <- as.numeric(
    difftime(
      df[[ts_col]],
      dplyr::lag(df[[ts_col]]),
      units = "mins"
    )
  )

  gap <- dt > max_gap_minutes
  gap[is.na(gap)] <- FALSE

  df[[value_col]][gap] <- NA

  df
}


# Dynamic y-axis limits
dynamic_limits <- function(x, pad = 0.05) {

  x <- x[is.finite(x)]

  if (length(x) == 0) {
    return(NULL)
  }

  rng <- range(x)

  # Handle constant values
  if (rng[1] == rng[2]) {
    extra <- max(abs(rng[1]) * 0.05, 1)
    return(c(rng[1] - extra, rng[2] + extra))
  }

  extra <- diff(rng) * pad

  c(rng[1] - extra, rng[2] + extra)
}

```

```{r, echo=F}



```

#MAIN TIMESERIES PLOTTER FUNCTION
#SINGLE VARIABLES

```{r, echo=F}
plot_flux_single <- function(df, ts_col = "TIMESTAMP", flux_col,
                             y_label, title, color = "blue", 
                             date_breaks = "1 month", date_labels = "%b",
                             smooth = FALSE,
                             y_limits = NULL,
                             clip_smooth = NULL,
                             site = NULL){

  df_line   <- break_gaps(df, ts_col, flux_col)
  df_smooth <- df

  # Dynamic limits if none supplied
  if (is.null(y_limits)) {
    y_limits <- dynamic_limits(df_line[[flux_col]])
  }

  if (!is.null(site)) {
    title <- paste(site, "-", title)
  }

  p <- ggplot(df_line, aes(x = .data[[ts_col]])) +
    geom_hline(yintercept = 0, linetype = "dashed", color = "black") +
    geom_line(
      aes(x = .data[[ts_col]], y = .data[[flux_col]]),
      linewidth = 0.8,
      alpha = 0.6,
      color = color
    ) + 
    labs(
      x = "",
      y = y_label,
      title = title
    ) + 
    scale_y_continuous(
      limits = y_limits,
      expand = expansion(mult = 0.05),
      breaks = scales::pretty_breaks(n = 8)
    ) +
    scale_x_datetime(
      date_breaks = date_breaks, 
      date_labels = date_labels
    ) +
    theme_minimal() + 
    theme(
      axis.text.x = element_text(angle = 45, hjust = 1)
    )

  if (smooth) {

    if (flux_col %in% roll_vars) {

      df_roll <- roll_smooth(
        df_smooth,
        ts_col,
        flux_col,
        k = 96
      )

      p <- p + geom_line(
        data = df_roll,
        aes(
          x = .data[[ts_col]],
          y = .data[["roll"]]
        ),
        color = "black",
        linewidth = 0.9
      )

    } else {

      n <- nrow(df_smooth)

      span_auto <- max(
        min((48 * 2) / n, 0.2),
        0.01
      )

      p <- p + geom_smooth(
        data = df_smooth,
        aes(
          x = .data[[ts_col]],
          y = .data[[flux_col]]
        ),
        method = "loess",
        span = span_auto,
        color = "black",
        linewidth = 0.7,
        se = FALSE
      )

      if (!is.null(clip_smooth)) {
        p <- p + coord_cartesian(
          ylim = clip_smooth
        )
      }
    }
  }

  return(p)
}


```

#SINGLE BIWEK PLOTTER

```{r, echo=F}
# ============================================================
# BIWEEK SINGLE PLOTTER
# ============================================================

plot_biweek_single <- function(df, biweek_num,
                               flux_col,
                               y_label,
                               title,
                               color,
                               date_breaks = "2 days",
                               date_labels = "%b %d",
                               y_limits = NULL,
                               clip_smooth = NULL,
                               site = "Toolik") {
  
  dfbw <- subset(
    df,
    biweek_in_month == biweek_num
  )
  
  if (nrow(dfbw) == 0) {
    return(NULL)
  }
  
  if (all(is.na(dfbw[[flux_col]]))) {
    return(NULL)
  }
  
  plot_flux_single(
    dfbw,
    flux_col = flux_col,
    y_label = y_label,
    title = paste(title, "- Biweek", biweek_num),
    color = color,
    date_breaks = date_breaks,
    date_labels = date_labels,
    y_limits = y_limits,
    clip_smooth = clip_smooth,
    site = site
  )
}

```

#MULTIPLE VARIABLES

```{r, echo=F}



plot_flux_long <- function(df, ts_col = "TIMESTAMP", 
                           cols, labels, colors, 
                           y_label, title, 
                           date_breaks = "1 month",
                           date_labels = "%b", 
                           smooth = FALSE,
                           y_limits = NULL,
                           site = NULL) {
  # Do not make a plot if none of the requested variables contain data
has_data <- sapply(
  cols,
  function(v) any(!is.na(df[[v]]))
)

if (!any(has_data)) {
  return(NULL)
}

  raw_list <- lapply(cols, function(v) {
    
    dfv <- df[, c(ts_col, v), drop = FALSE]
    names(dfv) <- c(ts_col, "value")
    dfv$variable <- v
    
    dfv <- break_gaps(dfv, ts_col, "value")
    dfv
  })
  
  df_long <- do.call(rbind, raw_list)
  df_long$variable <- factor(
    df_long$variable,
    levels = cols
  )
  
  # Dynamic limits across all variables
  if (is.null(y_limits)) {
    y_limits <- dynamic_limits(df_long$value)
  }
  
  if (!is.null(site)) {
    title <- paste(site, "-", title)
  }
  
  p <- ggplot(
    df_long,
    aes(
      x = .data[[ts_col]],
      y = value,
      color = variable
    )
  ) +
    geom_line(
      alpha = 0.6,
      linewidth = 0.8
    ) + 
    scale_color_manual(
      values = colors,
      labels = labels,
      name = NULL
    ) + 
    scale_y_continuous(
      limits = y_limits,
      expand = expansion(mult = 0.05),
      breaks = scales::pretty_breaks(n = 8),
      name = y_label
    ) + 
    scale_x_datetime(
      date_breaks = date_breaks, 
      date_labels = date_labels
    ) + 
    labs(
      title = title,
      x = ""
    ) +
    theme_minimal() + 
    theme(
      axis.text.x = element_text(
        angle = 45,
        hjust = 1
      ),
      legend.position = "top"
    )
  
  if (smooth) {
    
    smooth_list <- lapply(cols, function(v) {
      
      dfv <- df[, c(ts_col, v), drop = FALSE]
      names(dfv) <- c(ts_col, "value")
      dfv$variable <- v
      
      if (v %in% roll_vars) {
        
        dfv <- roll_smooth(
          dfv,
          ts_col,
          "value",
          k = 96
        )
        
        dfv$smooth_value <- dfv$roll
        
      } else {
        
        n <- nrow(dfv)
        
        span_auto <- max(
          min((48 * 2) / n, 0.2),
          0.01
        )
        
        lo <- loess(
          value ~ as.numeric(dfv[[ts_col]]),
          data = dfv,
          span = span_auto,
          na.action = na.exclude
        )
        
        dfv$smooth_value <- predict(lo)
      }
      
      dfv
    })
    
    df_smooth <- do.call(rbind, smooth_list)
    
    df_smooth$variable <- factor(
      df_smooth$variable,
      levels = cols
    )
    
    p <- p + geom_line(
      data = df_smooth,
      aes(
        x = .data[[ts_col]],
        y = smooth_value,
        color = variable
      ),
      linewidth = 0.9
    )
  }
  
  return(p)
}
```

#CO2

```{R, echo = F}

co2_plot_month <- plot_flux(
  df_month,
  "co2_flux",
  y_label = expression(
    paste(
      CO[2],
      " Flux (umol m",
      ""^-2,
      " s",
      ""^-1,
      ")"
    )
  ),
  title = "CO2 Flux",
  site = "Toolik"
)


co2_plot_month

```

#CO2 FOCUSED

```{R, echo = F}

co2_plot_month <- plot_flux(
  df_month,
  "co2_flux",
  y_label = expression(
    paste(
      CO[2],
      " Flux (umol m",
      ""^-2,
      " s",
      ""^-1,
      ")"
    )
  ),
  title = "CO2 Flux",
  site = "Toolik",
  focus_90 = TRUE
)


co2_plot_month

```


#CH4

```{r, echo=F}

ch4_plot_month <- plot_flux(
  df_month,
  "ch4_flux",
#  c(-0.031, 0.031),
  expression(paste(~CH[4], ~"Flux (umol m",""^-2,"s",""^-1,")")),
  title = "CH4 Flux",
  site = "Toolik"
)
ch4_plot_month
```
#CH4 MONTH FOCUSED

```{r, echo=F}

ch4_plot_month <- plot_flux(
  df_month,
  "ch4_flux",
#  c(-0.031, 0.031),
  expression(paste(~CH[4], ~"Flux (umol m",""^-2,"s",""^-1,")")),
  title = "CH4 Flux",
  site = "Toolik",
  focus_90 = TRUE
)
ch4_plot_month
```


#### H MONTH
```{r, warning=FALSE, echo=FALSE}
H_plot_ytd <- plot_flux(
  df_month,
  "H", 
 # c(-200, 200),
  expression(paste("H (W/m²)")),
  site = "Toolik"
)

H_plot_ytd

```
#### H MONTH FOCUSED
```{r, warning=FALSE, echo=FALSE}
H_plot_ytd <- plot_flux(
  df_month,
  "H", 
 # c(-200, 200),
  expression(paste("H (W/m²)")),
  site = "Toolik",
 focus_90 = TRUE
)

H_plot_ytd

```

#### LE MONTH
```{r, warning=FALSE, echo=FALSE}

LE_plot_month<- plot_flux(
  df_month,
  "LE", 
 # c(-100, 150),
  expression(paste("LE (W/m²)")),
  site = "Toolik"
)

LE_plot_month

```

#### LE MONTH FOCUSED
```{r, warning=FALSE, echo=FALSE}

LE_plot_month<- plot_flux(
  df_month,
  "LE", 
 # c(-100, 150),
  expression(paste("LE (W/m²)")),
  site = "Toolik",
 focus_90 = T
)

LE_plot_month

```

#DIURNAL FLUXES

```{r, echo=F}

# ============================================================
# DIURNAL FLUXES
# ============================================================

df_month$hour <- as.numeric(
  format(df_month$TIMESTAMP, "%H")
)

df_month$year <- as.numeric(
  format(df_month$TIMESTAMP, "%Y")
)

df_month$month <- as.numeric(
  format(df_month$TIMESTAMP, "%m")
)


make_diel <- function(
    df,
    group_cols = c("year", "month", "hour")
) {

  df %>%
    group_by(across(all_of(group_cols))) %>%
    summarise(

      co2_mean = ifelse(
        all(is.na(co2_flux.c)),
        NA_real_,
        median(co2_flux.c, na.rm = TRUE)
      ),

      co2_sd = ifelse(
        sum(!is.na(co2_flux.c)) < 2,
        NA_real_,
        sd(co2_flux.c, na.rm = TRUE)
      ),


      ch4_mean = ifelse(
        all(is.na(ch4_flux.c)),
        NA_real_,
        median(ch4_flux.c, na.rm = TRUE)
      ),

      ch4_sd = ifelse(
        sum(!is.na(ch4_flux.c)) < 2,
        NA_real_,
        sd(ch4_flux.c, na.rm = TRUE)
      ),


      LE_mean = ifelse(
        all(is.na(LE.c)),
        NA_real_,
        median(LE.c, na.rm = TRUE)
      ),

      LE_sd = ifelse(
        sum(!is.na(LE.c)) < 2,
        NA_real_,
        sd(LE.c, na.rm = TRUE)
      ),


      H_mean = ifelse(
        all(is.na(H.c)),
        NA_real_,
        median(H.c, na.rm = TRUE)
      ),

      H_sd = ifelse(
        sum(!is.na(H.c)) < 2,
        NA_real_,
        sd(H.c, na.rm = TRUE)
      ),


      Rn_mean = ifelse(
        all(is.na(Rn)),
        NA_real_,
        median(Rn, na.rm = TRUE)
      ),

      Rn_sd = ifelse(
        sum(!is.na(Rn)) < 2,
        NA_real_,
        sd(Rn, na.rm = TRUE)
      ),


      ustar_mean = ifelse(
        all(is.na(u.)),
        NA_real_,
        median(u., na.rm = TRUE)
      ),

      ustar_sd = ifelse(
        sum(!is.na(u.)) < 2,
        NA_real_,
        sd(u., na.rm = TRUE)
      ),

      .groups = "drop"
    )
}


# Monthly diel
diel_month <- make_diel(
  df_month,
  group_cols = c(
    "year",
    "month",
    "hour"
  )
)


# Weekly diel
diel_week <- make_diel(
  df_month,
  group_cols = c(
    "year",
    "month",
    "week_in_month",
    "hour"
  )
)


```

#PLOT DIURNALS - MONTHLY

```{r, echo=F}
plot_diel <- function(df, value_col, sd_col,
                      y_label, title,
                      color = "blue",
                      week = NULL,
                      site = "Toolik") {

  if (!is.null(week)) {
    df <- dplyr::filter(
      df,
      week_in_month == week
    )
  }

  title <- paste(site, "-", title)

  if (!is.null(week)) {
    title <- paste(title, "- Week", week)
  }

  ggplot(df) +
    geom_hline(
      yintercept = 0,
      linetype = "dashed"
    ) +
    geom_ribbon(
      aes(
        x = hour,
        ymin = .data[[value_col]] - .data[[sd_col]],
        ymax = .data[[value_col]] + .data[[sd_col]]
      ),
      alpha = 0.2
    ) +
    geom_line(
      aes(
        x = hour,
        y = .data[[value_col]]
      ),
      color = color,
      linewidth = 1
    ) +
    scale_x_continuous(
      breaks = seq(0, 23, by = 3)
    ) +
    labs(
      title = title,
      x = "Hour of Day",
      y = y_label
    ) +
    theme_bw()
}


```

#MONTHLY DIURNALS

```{R, echo = F}

p_diel_co2 <- plot_diel(
  diel_month,
  "co2_mean",
  "co2_sd",
  expression(CO[2]~Flux~(µmol~m^-2~s^-1)),
  "Diurnal CO2 Flux",
  color = "darkgreen"
)

p_diel_ch4 <- plot_diel(
  diel_month,
  "ch4_mean",
  "ch4_sd",
  expression(CH[4]~Flux~(µmol~m^-2~s^-1)),
  "Diurnal CH4 Flux",
  color = "purple"
)

p_diel_LE <- plot_diel(
  diel_month,
  "LE_mean",
  "LE_sd",
  "LE (W/m²)",
  "Diurnal Latent Heat Flux",
  color = "dodgerblue"
)

p_diel_H <- plot_diel(
  diel_month,
  "H_mean",
  "H_sd",
  "H (W/m²)",
  "Diurnal Sensible Heat Flux",
  color = "firebrick"
)

p_diel_Rn <- plot_diel(
  diel_month,
  "Rn_mean",
  "Rn_sd",
  expression(Rn~(W/m^2)),
  "Diurnal Net Radiation",
  color = "black"
)

p_diel_ustar <- plot_diel(
  diel_month,
  "ustar_mean",
  "ustar_sd",
  expression(u^"*"),
  "Diurnal Friction Velocity",
  color = "darkorange"
)



```

```{R, echo = F}

p_diel_co2
p_diel_ch4
p_diel_LE
p_diel_H
p_diel_Rn
p_diel_ustar


```

# TIMESTAMP CHECK WITH RPOT/SWIN

```{r, echo=F}

# WEEKLY DIURNAL RADIATION
df_month$hour <- as.numeric(format(df_month$TIMESTAMP, "%H"))
df_month$year <- as.numeric(format(df_month$TIMESTAMP, "%Y"))
df_month$month <- as.numeric(format(df_month$TIMESTAMP, "%m"))

make_weekly_radiation_diel <- function(df) {

  df %>%
    group_by(year, month, week_in_month, hour) %>%
    summarise(
      SWIN_mean = ifelse(
        all(is.na(SWIN_6_10_1_1_1)),
        NA_real_,
        median(SWIN_6_10_1_1_1, na.rm = TRUE)
      ),
      SWIN_sd = ifelse(
        sum(!is.na(SWIN_6_10_1_1_1)) < 2,
        NA_real_,
        sd(SWIN_6_10_1_1_1, na.rm = TRUE)
      ),
      rpot_mean = ifelse(
        all(is.na(rpot)),
        NA_real_,
        median(rpot, na.rm = TRUE)
      ),
      rpot_sd = ifelse(
        sum(!is.na(rpot)) < 2,
        NA_real_,
        sd(rpot, na.rm = TRUE)
      ),
      .groups = "drop"
    )
}

radiation_diel_week <- make_weekly_radiation_diel(df_month)
```

```{R, echo = F}

for (w in sort(unique(radiation_diel_week$week_in_month))) {

  p <- radiation_diel_week %>%
    dplyr::filter(week_in_month == w) %>%
    ggplot() +

    geom_ribbon(
      aes(
        x = hour,
        ymin = SWIN_mean - SWIN_sd,
        ymax = SWIN_mean + SWIN_sd
      ),
      alpha = 0.2
    ) +

    geom_line(
      aes(x = hour, y = SWIN_mean, color = "SWIN"),
      linewidth = 1
    ) +

    geom_line(
      aes(x = hour, y = rpot_mean, color = "rpot"),
      linewidth = 1
    ) +

    scale_x_continuous(
      breaks = seq(0, 23, by = 3)
    ) +

    labs(
      title = paste("Toolik - Radiation Diel - Week", w),
      x = "Hour of Day",
      y = "Radiation (W/m²)",
      color = NULL
    ) +

    theme_bw()

  print(p)
}
```
###ENERGY BALANCE

```{r, echo=F}

# ============================================================
# ENERGY BALANCE
# ============================================================

both_missing <- is.na(df_month$SHF_6_37_1_1_1.c) &
                is.na(df_month$SHF_6_37_2_1_1_1.c)

df_month$shf_avg[both_missing] <- 0

df_month$met <- df_month$Rn - df_month$shf_avg

df_month$flux <- df_month$H.c + df_month$LE.c


# Only use complete EB observations
eb_data <- df_month %>%
  dplyr::filter(
    !is.na(met),
    !is.na(flux)
  )


# ============================================================
# ENERGY BALANCE PLOT
# ============================================================

if (nrow(eb_data) < 2) {

  eb_month <- ggplot() +
    labs(
      x = expression("Rn - G  (W m"^-2*")"),
      y = expression("H + LE  (W m"^-2*")"),
      title = "Toolik - Monthly Energy Balance"
    ) +
    annotate(
      "text",
      x = 0,
      y = 0,
      label = "No valid energy balance data",
      size = 5
    ) +
    theme_bw()

} else {

  mod <- lm(
    flux ~ met,
    data = eb_data
  )

  slope <- coef(mod)["met"]
  r2 <- summary(mod)$r.squared


  cat(
    "Slope:", slope,
    "\nR²:", r2, "\n"
  )


  # ============================================================
  # DYNAMIC ENERGY BALANCE LIMITS
  # ============================================================

  eb_values <- c(
    eb_data$met,
    eb_data$flux
  )

  eb_values <- eb_values[is.finite(eb_values)]

  if (length(eb_values) > 0) {

    eb_range <- range(eb_values)

    eb_pad <- diff(eb_range) * 0.05

    if (eb_pad == 0) {
      eb_pad <- max(abs(eb_range[1]) * 0.05, 1)
    }

    eb_limits <- c(
      eb_range[1] - eb_pad,
      eb_range[2] + eb_pad
    )

  } else {

    eb_limits <- c(-1, 1)

  }


  eb_month <- ggplot(
    eb_data,
    aes(
      x = met,
      y = flux,
      color = factor(week_in_month)
    )
  ) +

    geom_point(
      alpha = 0.7,
      na.rm = TRUE
    ) +

    geom_smooth(
      method = "lm",
      color = "black",
      se = FALSE,
      na.rm = TRUE
    ) +

    geom_abline(
      slope = 1,
      intercept = 0,
      linetype = "dashed",
      color = "red"
    ) +

    geom_hline(
      yintercept = 0,
      color = "black"
    ) +

    geom_vline(
      xintercept = 0,
      color = "black"
    ) +

    coord_fixed(
      ratio = 1,
      xlim = eb_limits,
      ylim = eb_limits
    ) +

    labs(
      x = expression("Rn - G  (W m"^-2*")"),
      y = expression("H + LE  (W m"^-2*")"),
      color = "Week",
      title = "Toolik - Monthly Energy Balance"
    ) +

    annotate(
      "text",
      x = eb_limits[2],
      y = eb_limits[1],
      label = paste0(
        "Slope = ", round(slope, 3),
        "\nR² = ", round(r2, 3)
      ),
      hjust = 1.1,
      vjust = -0.5,
      size = 4
    ) +

    theme_bw()
}

eb_month

```


#ALL RADIATION

```{r, echo=F}

# ============================================================
# RADIATION
# ============================================================

# Shortwave radiation: Incoming + Outgoing
p_sw <- plot_flux_long(
  df_month,
  cols = c(
    "SWIN_6_10_1_1_1.c",
    "SWOUT_6_11_1_1_1.c"
  ),
  labels = c(
    "Incoming SW",
    "Outgoing SW"
  ),
  colors = c(
    "pink4",
    "dodgerblue4"
  ),
  y_label = expression(Shortwave~Radiation~(W/m^2)),
  title = "Shortwave Radiation In/Out",
  date_breaks = "2 days",
  date_labels = "%b %d",
  site = "Toolik"
)


# Longwave radiation: Incoming + Outgoing
p_lw <- plot_flux_long(
  df_month,
  cols = c(
    "LWIN_6_14_1_1_1.c",
    "LWOUT_6_15_1_1_1.c"
  ),
  labels = c(
    "Incoming LW",
    "Outgoing LW"
  ),
  colors = c(
    "firebrick",
    "dodgerblue"
  ),
  y_label = expression(Longwave~Radiation~(W/m^2)),
  title = "Longwave Radiation In/Out",
  date_breaks = "2 days",
  date_labels = "%b %d",
  site = "Toolik"
)


# PAR: Incoming + Reflected
p_par <- plot_flux_long(
  df_month,
  cols = c(
    "PPFD_7_21_1_1_1.c",
    "PPFDR_7_23_1_1_1.c"
  ),
  labels = c(
    "PPFD",
    "PPFDR"
  ),
  colors = c(
    "darkgreen",
    "purple"
  ),
  y_label = expression(PAR~(µmol~m^-2~s^-1)),
  title = "PAR In/Out",
  date_breaks = "2 days",
  date_labels = "%b %d",
  site = "Toolik"
)


# Albedo
p_albedo <- plot_flux_single(
  df_month,
  flux_col = "ALB_1_1_1.c",
  y_label = "Albedo",
  title = "Albedo",
  color = "cyan4",
  date_breaks = "2 days",
  date_labels = "%b %d",
  y_limits = c(0, 1),
  clip_smooth = c(0, 1),
  site = "Toolik"
)

p_sw 
p_lw
p_par
p_albedo
```

#WIND COMPARISON - SONIC VS. YOUNG

```{r, echo=F}

# ============================================================
# WIND 1:1 COMPARISON PLOTTER
#
# Before 2026-04-26 17:00 UTC:
#   wind_speed       = Sonic
#   WS_16_33_1_1_1   = Sonic
#   max_wind_speed   = Sonic
#   MWS_16_34_1_1_1  = Sonic
#   wind_dir         = Sonic
#   WD_20_35_1_1_1   = Sonic
#
# After 2026-04-26 17:00 UTC:
#   wind_speed       = RMYOUNG
#   WS_16_33_1_1_1   = Sonic
#   max_wind_speed   = RMYOUNG
#   MWS_16_34_1_1_1  = Sonic
#   wind_dir         = RMYOUNG
#   WD_20_35_1_1_1   = Sonic
#
# Therefore, only data AFTER the transition are used for
# the RMYOUNG vs Sonic 1:1 comparisons.
# ============================================================


# ============================================================
# FUNCTION: GET VALID TWO-INSTRUMENT COMPARISON DATA
# Automatically skips months before both instruments are active
# ============================================================

wind_compare_data <- function(df, rmy_col, sonic_col,
                              date = "2026-04-26 17:00:00") {

  transition <- as.POSIXct(date, tz = "UTC")

  # Check that required columns exist
  if (!all(c("TIMESTAMP", rmy_col, sonic_col) %in% names(df))) {
    return(NULL)
  }

  # Keep only the period when RMYOUNG and Sonic are separate
  # instruments AND both measurements are present
  df_plot <- df %>%
    dplyr::filter(
      TIMESTAMP > transition,
      !is.na(.data[[rmy_col]]),
      !is.na(.data[[sonic_col]])
    )

  # Skip if there is no valid comparison period/data
  if (nrow(df_plot) == 0) {
    return(NULL)
  }

  return(df_plot)
}


# ============================================================
# WIND SPEED
# ============================================================

df_wind <- wind_compare_data(
  df_month,
  "wind_speed",
  "WS_16_33_1_1_1"
)

if (!is.null(df_wind)) {

  wind_ws_11 <- ggplot(df_wind) +

    geom_point(
      aes(
        x = wind_speed,
        y = wind_speed,
        color = "RMYOUNG"
      ),
      alpha = 0.5
    ) +

    geom_point(
      aes(
        x = wind_speed,
        y = WS_16_33_1_1_1,
        color = "Sonic"
      ),
      alpha = 0.5
    ) +

    geom_abline(
      intercept = 0,
      slope = 1,
      linetype = "dashed",
      color = "black"
    ) +

    scale_color_manual(
      values = c(
        "RMYOUNG" = "red",
        "Sonic" = "blue"
      )
    ) +

    labs(
      title = "Toolik - Wind Speed Comparison",
      x = "RMYOUNG Wind Speed (m/s)",
      y = "Sonic Wind Speed (m/s)",
      color = "Instrument"
    ) +

    theme_bw()

  wind_ws_11
}


# ============================================================
# MAXIMUM WIND SPEED
# ============================================================

df_mws <- wind_compare_data(
  df_month,
  "max_wind_speed",
  "MWS_16_34_1_1_1"
)

if (!is.null(df_mws)) {

  wind_mws_11 <- ggplot(df_mws) +

    geom_point(
      aes(
        x = max_wind_speed,
        y = max_wind_speed,
        color = "RMYOUNG"
      ),
      alpha = 0.5
    ) +

    geom_point(
      aes(
        x = max_wind_speed,
        y = MWS_16_34_1_1_1,
        color = "Sonic"
      ),
      alpha = 0.5
    ) +

    geom_abline(
      intercept = 0,
      slope = 1,
      linetype = "dashed",
      color = "black"
    ) +

    scale_color_manual(
      values = c(
        "RMYOUNG" = "red",
        "Sonic" = "blue"
      )
    ) +

    labs(
      title = "Toolik - Maximum Wind Speed Comparison",
      x = "RMYOUNG Maximum Wind Speed (m/s)",
      y = "Sonic Maximum Wind Speed (m/s)",
      color = "Instrument"
    ) +

    theme_bw()

  wind_mws_11
}


# ============================================================
# WIND DIRECTION
# ============================================================

df_dir <- wind_compare_data(
  df_month,
  "wind_dir",
  "WD_20_35_1_1_1"
)

if (!is.null(df_dir)) {

  wind_dir_11 <- ggplot(df_dir) +

    geom_point(
      aes(
        x = wind_dir,
        y = wind_dir,
        color = "RMYOUNG"
      ),
      alpha = 0.5
    ) +

    geom_point(
      aes(
        x = wind_dir,
        y = WD_20_35_1_1_1,
        color = "Sonic"
      ),
      alpha = 0.5
    ) +

    geom_abline(
      intercept = 0,
      slope = 1,
      linetype = "dashed",
      color = "black"
    ) +

    scale_color_manual(
      values = c(
        "RMYOUNG" = "red",
        "Sonic" = "blue"
      )
    ) +

    scale_x_continuous(
      limits = c(0, 360),
      breaks = seq(0, 360, by = 45)
    ) +

    scale_y_continuous(
      limits = c(0, 360),
      breaks = seq(0, 360, by = 45)
    ) +

    labs(
      title = "Toolik - Wind Direction Comparison",
      x = "RMYOUNG Wind Direction (°)",
      y = "Sonic Wind Direction (°)",
      color = "Instrument"
    ) +

    theme_bw()

  wind_dir_11
}
```



#WIND ROSES

```{r, echo=F}

# ============================================================
# SONIC ANEMOMETER WIND ROSE
# ============================================================

df_wind_sonic <- df_month %>%
  dplyr::filter(
    !is.na(wind_speed),
    !is.na(wind_dir)
  ) %>%
  dplyr::transmute(
    ws = as.numeric(wind_speed),
    wd = as.numeric(wind_dir)
  ) %>%
  dplyr::filter(
    is.finite(ws),
    is.finite(wd)
  )

if (nrow(df_wind_sonic) == 0) {

  plot.new()
  title("Toolik - Sonic Anemometer Wind Rose")
  text(0.5, 0.5, "No valid sonic wind data")

} else {

  windRose(
    df_wind_sonic,
    ws = "ws",
    wd = "wd",
    paddle = FALSE,
    key = TRUE,
    main = "Toolik - Sonic Anemometer Wind Rose"
  )
}


# ============================================================
# RMY WIND ROSE
# ============================================================

df_wind_rmy <- df_month %>%
  dplyr::filter(
    !is.na(WS_16_33_1_1_1),
    !is.na(WD_20_35_1_1_1)
  ) %>%
  dplyr::transmute(
    ws = as.numeric(WS_16_33_1_1_1),
    wd = as.numeric(WD_20_35_1_1_1)
  ) %>%
  dplyr::filter(
    is.finite(ws),
    is.finite(wd)
  )

if (nrow(df_wind_rmy) == 0) {

  plot.new()
  title("Toolik - RMY Wind Rose")
  text(0.5, 0.5, "No valid RMY wind data")

} else {

  windRose(
    df_wind_rmy,
    ws = "ws",
    wd = "wd",
    paddle = FALSE,
    key = TRUE,
    main = "Toolik - RMY Wind Rose"
  )
}

```

##AIR T COMPARISON - SONIC/HMP

```{r, echo=F}
temp_11 <- ggplot(df_month) +
  geom_point(
    aes(
      x = TA_2_1_1_1_1,
      y = sonic_temperature - 273.15,
      color = TIMESTAMP
    )
  ) +
  geom_abline(
    intercept = 0,
    slope = 1,
    color = "red"
  ) +
  scale_x_continuous(limits = c(-43, 35)) +
  scale_y_continuous(limits = c(-43, 35)) +
  labs(
    title = "Toolik - Air vs Sonic Temperature",
    x = "Air Temperature (°C)",
    y = "Sonic Temperature (°C)"
  ) +
  theme_bw()

temp_11
```

##AIRT
```{R, echo =F}
p_air <- plot_flux_single(
  df_month,
  flux_col = "TA_2_1_1_1_1.c",
  y_label = "Air Temperature (°C)",
  title = "Air Temperature",
  color = "red",
  date_breaks = "2 days",
  date_labels = "%b %d",
  site = "Toolik"
)

p_air
```

#AIR P
```{R, echo =F}
p_pres <- plot_flux_single(
  df,
  flux_col = "air_pressure",
  y_label  = "Air Pressure (kpa)",
  title    = "Air Pressure",
  color    = "black",
  date_breaks = "2 days",
  date_labels = "%b %d",
  site = "Toolik"
)

p_pres

```

#RH
```{R, echo =F}
p_rh <- plot_flux_single(
  df,
  flux_col = "RH.c",
  y_label  = "Relative Humidity (%)",
  title    = "Relative Humidity ",
  color    = "lightblue4",
  date_breaks = "2 days",
  date_labels = "%b %d",
  site = "Toolik"
)

p_rh

```

#SNOWDEPTH
```{R, echo =F}
p_sd <- plot_flux_single(df, flux_col = "SD_cm",
                             y_label = "Snow Depth (cm)",
                             title = "Snow Depth",
                             color = "turquoise2",
                             date_breaks = "2 days",
                             date_labels = "%b %d",
                             site = "Toolik")

p_sd

```

#RAIN
```{R, echo =F}
p_pr <- plot_flux_single(df, flux_col = "P_RAIN_8_19_1_1_1.c",
                             y_label = "Precip. Rain (mm)",
                             title = "Rain (mm)",
                             color = "blue",
                             date_breaks = "2 days",
                             date_labels = "%b %d",
                         site = "Toolik")
                          

p_pr


```


#### SOIL TEMPERATURES 10 -30 cm
```{r, warning=FALSE, echo=FALSE}
P_soilT <- plot_flux_long(
  df_month,
  cols = c("TS_2_38_1_1_1.c",
           "TS_2_38_2_1_1.c",
           "TS_2_38_2_2_1.c"),
  labels = c("08 cm", "18 cm", "28 cm"),
  colors = c("blue", "green", "gold3"),
  y_label = "Soil Temperature (°C)",
  title = "Soil Temperature by Depth",
  site = "Toolik",
  date_breaks = "2 days",
  date_labels = "%b %d")

P_soilT

```

###SOIL MOISTURE

```{R, echo =F}

p_soilM <- plot_flux_long(
  df_month,
  cols = c(
    "SWC_12_36_1_1_1.c",
    "SWC_12_36_2_1_1.c",
    "SWC_12_36_3_1_1.c"
  ),
  labels = c(
    "08 cm",
       "18 cm",
       "28 cm"
  ),
  colors = c(
    "blue",
    "green",
    "gold3"
  ),
  y_label = "Soil Moisture (%)",
  title = "Soil Moisture by Depth",
  site = "Toolik",
  date_breaks = "2 days",
  date_labels = "%b %d"
)

p_soilM

```

###SHF

```{R, echo =F}

p_G <- plot_flux_long(
  df_month,
  cols = c(
    "SHF_6_37_1_1_1.c",
    "SHF_6_37_2_1_1.c"
  ),
  labels = c(
    "SHF 1",
    "SHF 2"
  ),
  colors = c(
    "blue",
    "red"
  ),
  y_label = expression(Soil~Heat~Flux~(W/m^2)),
  title = "Soil Heat Flux",
  site = "Toolik",
  date_breaks = "2 days",
  date_labels = "%b %d"
)

p_G

```
# TOMST SLUMP
```{R, echo=F}
# =========================================================================
# TMS NETWORK MONTHLY QC
# =========================================================================
df_filtered <- df_month


# Common styling
lbl_y_temp <- expression("Temperature ("*degree*C*")")
lbl_y_vwc  <- expression("Soil Moisture VWC (m"^3*"/m"^3*")")

color_map <- c(
  "Center" = "black",
  "East"   = "firebrick",
  "West"   = "dodgerblue4",
  "North"  = "forestgreen",
  "South"  = "gold3"
)


# =========================================================================
# TMS PLOT FUNCTION
# Skip plot if required data are not available
# =========================================================================

plot_tms <- function(df, columns, y_label, title,
                     zero_line = TRUE) {

  # Check that the required columns exist
  missing_cols <- setdiff(columns, names(df))

  if (length(missing_cols) > 0) {
    message("Skipping: ", title,
            " -- missing column(s): ",
            paste(missing_cols, collapse = ", "))
    return(NULL)
  }

  # Keep rows where at least one logger has data
  df_plot <- df %>%
    dplyr::filter(
      rowSums(!is.na(dplyr::select(., dplyr::all_of(columns)))) > 0
    )

  # Skip if there is no data
  if (nrow(df_plot) == 0) {
    message("Skipping: ", title, " -- no data available")
    return(NULL)
  }

  p <- ggplot(df_plot, aes(x = TIMESTAMP)) +

    geom_line(
      aes(y = .data[[columns[1]]], color = "Center"),
      linewidth = 0.7
    ) +

    geom_line(
      aes(y = .data[[columns[2]]], color = "East"),
      linewidth = 0.7
    ) +

    geom_line(
      aes(y = .data[[columns[3]]], color = "West"),
      linewidth = 0.7
    ) +

    geom_line(
      aes(y = .data[[columns[4]]], color = "North"),
      linewidth = 0.7
    ) +

    geom_line(
      aes(y = .data[[columns[5]]], color = "South"),
      linewidth = 0.7
    ) +

    scale_color_manual(
      values = color_map,
      name = "Logger"
    ) +

    labs(
      x = "Timeline",
      y = y_label,
      title = title
    ) +

    theme_minimal() +

    theme(
      legend.position = "bottom",
      axis.text.x = element_text(angle = 45, hjust = 1),
      title = element_text(face = "bold")
    )+
    guides(
  color = guide_legend(
    override.aes = list(linewidth = 2)
  )
)

  if (zero_line) {
    p <- p +
      geom_hline(
        yintercept = 0,
        color = "black",
        linewidth = 0.8,
        linetype = "dashed"
      )
  }

  return(p)
}
```

```{r, echo=F}

# =========================================================================
# PLOT 1: +15 cm AIR TEMPERATURE
# =========================================================================

p1 <- plot_tms(
  df_month,
  c("TMS_C_T_1", "TMS_E_T_1", "TMS_W_T_1",
    "TMS_N_T_1", "TMS_S_T_1"),
  lbl_y_temp,
  "TMS +15cm Air Temperature"
)

if (!is.null(p1)) print(p1)


# =========================================================================
# PLOT 2: 0 cm GROUND SURFACE TEMPERATURE
# =========================================================================

p2 <- plot_tms(
  df_month,
  c("TMS_C_T_2", "TMS_E_T_2", "TMS_W_T_2",
    "TMS_N_T_2", "TMS_S_T_2"),
  lbl_y_temp,
  "TMS +2cm Ground Surface Temperature"
)

if (!is.null(p2)) print(p2)




# =========================================================================
# PLOT 3: -6 cm SOIL TEMPERATURE
# =========================================================================

p3 <- plot_tms(
  df_month,
  c("TMS_C_T_3", "TMS_E_T_3", "TMS_W_T_3",
    "TMS_N_T_3", "TMS_S_T_3"),
  lbl_y_temp,
  "TMS -6cm Soil Temperature"
)

if (!is.null(p3)) print(p3)


# =========================================================================
# PLOT 4: -6 cm SOIL MOISTURE
# =========================================================================

p4 <- plot_tms(
  df_month,
  c("TMS_C_VWC", "TMS_E_VWC", "TMS_W_VWC",
    "TMS_N_VWC", "TMS_S_VWC"),
  lbl_y_vwc,
  "TMS  -6cm Soil Moisture (VWC)",
  zero_line = FALSE
)

if (!is.null(p4)) print(p4)
```
#WEEKLY CO2

```{r, echo=F}

for (w in sort(unique(df_month$week_in_month))) {

  p <- plot_week_flux(
    df_month,
    w,
    "co2_flux",
    expression(
      paste(
        CO[2],
      " Flux (umol m",
      ""^-2,
      " s",
      ""^-1,
      ")"
    )
  ),
  site = "Toolik"
  )

  if (!is.null(p)) {
    print(p)
  }
}
```

#WEEKLY CH4

```{r, warning=FALSE, message=FALSE, echo=FALSE, fig.show='hold'}

for (w in sort(unique(df_month$week_in_month))) {

  p <- plot_week_flux(
    df_month, w,
    "ch4_flux",      
    #c(-0.031, 0.031),    
    expression(paste( ~CH[4], ~"Flux (umol m",""^"-2","s",""^"-1",")")),
    site = "Toolik"
  )

  print(p)
}

```

#### WEEKLY H 
```{r, warning=FALSE, message=FALSE, echo=FALSE, fig.show='hold'}

for (w in sort(unique(df_month$week_in_month))) {

  p <- plot_week_flux(
    df_month,
    w,
    "H",
    "H (W/m²)",
    site = "Toolik"
  )

  if (!is.null(p)) {
    print(p)
  }
}

```

#### WEEKLY LE

```{r, warning=FALSE, message=FALSE, echo=FALSE, fig.show='hold'}

for (w in sort(unique(df_month$week_in_month))) {

p <- plot_week_flux(
  df_month,w,
  "LE", 
 # c(-100, 150),
  expression(paste("LE (W/m²)")),
  site = "Toolik"
)

print(p)
}

```

#BIWEEK RADIATION
```{R, echo = F}
# ============================================================
# RADIATION - BIWEEKLY
# ============================================================

for (w in sort(unique(df_month$biweek_in_month))) {
  
  dfbw <- subset(
    df_month,
    biweek_in_month == w
  )
  
  
  # Shortwave radiation: Incoming + Outgoing
  p_sw <- plot_flux_long(
    dfbw,
    cols = c(
      "SWIN_6_10_1_1_1.c",
      "SWOUT_6_11_1_1_1.c"
    ),
    labels = c(
      "Incoming SW",
      "Outgoing SW"
    ),
    colors = c(
      "pink4",
      "dodgerblue4"
    ),
    y_label = expression(Shortwave~Radiation~(W/m^2)),
    title = paste("Shortwave Radiation In/Out - Biweek", w),
    date_breaks = "2 days",
    date_labels = "%b %d",
    site = "Toolik"
  )
  
  
  # Longwave radiation: Incoming + Outgoing
  p_lw <- plot_flux_long(
    dfbw,
    cols = c(
      "LWIN_6_14_1_1_1.c",
      "LWOUT_6_15_1_1_1.c"
    ),
    labels = c(
      "Incoming LW",
      "Outgoing LW"
    ),
    colors = c(
      "firebrick",
      "dodgerblue"
    ),
    y_label = expression(Longwave~Radiation~(W/m^2)),
    title = paste("Longwave Radiation In/Out - Biweek", w),
    date_breaks = "2 days",
    date_labels = "%b %d",
    site = "Toolik"
  )
  
  
  # PAR: Incoming + Reflected
  p_par <- plot_flux_long(
    dfbw,
    cols = c(
      "PPFD_7_21_1_1_1.c",
      "PPFDR_7_23_1_1_1.c"
    ),
    labels = c(
      "PPFD",
      "PPFDR"
    ),
    colors = c(
      "darkgreen",
      "purple"
    ),
    y_label = expression(PAR~(µmol~m^-2~s^-1)),
    title = paste("PAR In/Out - Biweek", w),
    date_breaks = "2 days",
    date_labels = "%b %d",
    site = "Toolik"
  )
  
  
  # Net radiation
  p_rn <- plot_flux_single(
    dfbw,
    flux_col = "RN_6_5_1_1_1.c",
    y_label = expression(Net~Radiation~(W/m^2)),
    title = paste("Net Radiation - Biweek", w),
    color = "orange",
    date_breaks = "2 days",
    date_labels = "%b %d",
    site = "Toolik"
  )
  
  
  # Print all radiation plots for this biweek
  print(p_sw)
  print(p_lw)
  print(p_par)
  #print(p_rn)
}
```

#BIWEEK AIR T
```{r, echo=FALSE}
# ============================================================
# AIR TEMPERATURE
# ============================================================

for (w in sort(unique(df_month$biweek_in_month))) {
  
  p <- plot_biweek_single(
    df_month,
    w,
    "TA_2_1_1_1_1.c",
    "Air Temperature (°C)",
    "Air Temperature",
    "red",
    site = "Toolik"
  )
  
  print(p)
}
```

#BIWEEK AIR P
```{R, echo =F}
# ============================================================
# AIR PRESSURE
# ============================================================

for (w in sort(unique(df_month$biweek_in_month))) {
  
  p <- plot_biweek_single(
    df_month,
    w,
    "air_pressure",
    "Air Pressure (kPa)",
    "Air Pressure",
    "black",
    site = "Toolik"
  )
  
  print(p)
}

```

# BIWEEK RH
```{R, echo =F}
# ============================================================
# RELATIVE HUMIDITY
# ============================================================

for (w in sort(unique(df_month$biweek_in_month))) {
  
  p <- plot_biweek_single(
    df_month,
    w,
    "RH.c",
    "Relative Humidity (%)",
    "Relative Humidity",
    "lightblue4",
    site = "Toolik"
  )
  
  print(p)
}
```

#BIWEEK SNOWDEPTH
```{R, echo =F}
# ============================================================
# SNOW DEPTH
# ============================================================

for (w in sort(unique(df_month$biweek_in_month))) {
  
  p <- plot_biweek_single(
    df_month,
    w,
    "SD_cm",
    "Snow Depth (cm)",
    "Snow Depth",
    "turquoise2",
    site = "Toolik"
  )
  
  print(p)
}

```

#BIWEEK RAIN
```{R, echo =F}
# ============================================================
# PRECIP
# ============================================================

for (w in sort(unique(df_month$biweek_in_month))) {
  
  p <- plot_biweek_single(
    df_month,
    w,
    "P_RAIN_8_19_1_1_1",
    "Precip. Rain (mm)",
    "Rain",
    "blue",
    site = "Toolik"
  )
  
  print(p)
}

```


# WEEKLY SOIL TEMP 10-30 CM

```{r , echo=F}

for (w in sort(unique(df_month$week_in_month))) {

  dfw <- subset(df_month, week_in_month == w)

  p <- plot_flux_long(
    dfw,
    cols = c("TS_2_38_1_1_1.c",
           "TS_2_38_2_1_1.c",
           "TS_2_38_2_2_1.c"),
    labels = c(
     "08 cm",
       "18 cm",
       "28 cm"
    ),
    colors = c(
      "blue",
      "green",
      "gold3"
    ),
    y_label = "Soil Temperature (°C)",
    title = "Soil Temperature by Depth",
  site = "Toolik",
  date_breaks = "2 days",
  date_labels = "%b %d")

  if (!is.null(p)) {
    print(p)
  }
}

```

#WEEKLY SOIL MOISTURE 10-30 CM

```{r , echo=F}

for (w in sort(unique(df_month$week_in_month))) {

  dfw <- subset(df_month, week_in_month == w)

  p <- plot_flux_long(
    dfw,
    cols = c(
      "SWC_12_36_1_1_1.c",
      "SWC_12_36_2_1_1.c",
      "SWC_12_36_3_1_1.c"
    ),
    labels = c(
       "08 cm",
       "18 cm",
       "28 cm"
    ),
    colors = c(
      "blue",
      "green",
      "gold3"
    ),
    y_label = "Soil Moisture (%)",
    title = paste("Soil Moisture by Depth - Week", w),
    site = "Toolik",
    date_breaks = "1 day",
    date_labels = "%b %d"
  )

  if (!is.null(p)) {
    print(p)
  }
}

```

##WEEKLY SHF 

```{R, echo = F}

for (w in sort(unique(df_month$week_in_month))) {

  dfw <- subset(df_month, week_in_month == w)

  p <- plot_flux_long(
    dfw,
    cols = c(
      "SHF_6_37_1_1_1.c",
      "SHF_6_37_2_1_1.c"
    ),
    labels = c(
      "SHF 1",
      "SHF 2"
    ),
    colors = c(
      "blue",
      "red"
    ),
    y_label = expression(Soil~Heat~Flux~(W/m^2)),
    title = paste("Soil Heat Flux - Week", w),
    site = "Toolik",
    date_breaks = "1 day",
    date_labels = "%b %d"
  )

  if (!is.null(p)) {
    print(p)
  }
}

```



 